### 2016-06-16 Paper/Paper.tex
Some figures updated, first paper draft attempt.
Some figures updated, attempts at new and more consistent colorscheme.
Some figures added to paper draft, trying to get started with the litterature
needed.

%%%============================================================================
%
%   Pandoc template to convert to latex using emulateapj.
%   
%
%   Usage:
%   ------
%
%   pandoc --template=[/Path/To/File/]pandoc-apj.latex
%
%
%
%   Caveats (mostly limitations in pandoc):
%   ---------------------------------------
%
%   + Doesn't do figure* and table* environments, these must be tweaked 
%     manually from standard figure and table environments or inserted as raw
%     LaTeX rather than Markdown figure invironments.
%     UPDATE: This can be accomplished by using Scholdoc rather than Pandoc.
%   + Same goes for equations: pandoc (at the time of writing) only does
%     displaymath, equations must be declared in raw LaTeX
%   + Graphics are not scaled, because the autoscale function provided in the
%     template is using the raw TeX \def function, which is not supported in
%     ApJ. UPDATE: This has been fixed in Pandoc, and Scholdoc even better.
%     Use Scholdoc! 
%
%   Copyright 2014-2016 T. E. Rivera-Thorsen.
%
%%%============================================================================
\documentclass[preprint2]{aastex6}
% \usepackage{lmodern}
% \usepackage{dcolumn}
\usepackage{amssymb,amsmath}
\usepackage[T1]{fontenc}
\usepackage[utf8x]{inputenc}
% \usepackage{natbib}
\bibliographystyle{aasjournal}
\usepackage{listings}
\usepackage{graphicx}
%\ifxetex
%  \usepackage[setpagesize=false, % page size defined by xetex
%              unicode=false, % unicode breaks when used with xetex
%              xetex]{hyperref}
%\else
%\usepackage[unicode=true]{hyperref}
%\fi
\hypersetup{breaklinks=true,
           bookmarks=true,
           pdfauthor={},
           pdftitle={Neutral ISM, Lyman-Alpha and Lyman-continuum in nearby starburst Haro 11},
           colorlinks=true,
           citecolor=blue,
           urlcolor=blue,
           linkcolor=magenta,
           pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
% \setlength{\parindent}{0pt}
% \setlength{\parskip}{6pt plus 2pt minus 1pt}
% \setlength{\emergencystretch}{3em}  % prevent overfull lines
% \setcounter{secnumdepth}{5}

\shorttitle{Neutral ISM, Ly-Alpha and LyC in Haro 11}

\shortauthors{T. E. Rivera-Thorsen et al.}

% % \date{\today}
%

%%%-----------------------------------------------------------------------
%      Macros
%%%-----------------------------------------------------------------------

\begin{document}

\title{Neutral ISM, Lyman-Alpha and Lyman-continuum in nearby starburst Haro 11\footnotemark[1]}
\footnotetext[1]{Based on observations Cosmic Origins Spectrograph on the Hubble Space
Telescope, program XXXXXX, PI YYYYYYYY}

\author{T. Emil Rivera-Thorsen\altaffilmark{2, 3}}

\author{Göran Östlin\altaffilmark{2, 3}}

\altaffiltext{2}{Department of Astronomy, Oskar Klein Centre, Stockholm University,
AlbaNova University Centre, SE-106 91 Stockholm, Sweden}
\altaffiltext{3}{Oscar Klein Centre for Cosmoparticle Physics, Department of Astronomy,
Stockholm University, Stockholm, Sweden}

\begin{abstract}
Something something something.
\end{abstract}

\section{Introduction and
Observations}\label{introduction-and-observations}

About Haro 11: Some of the same stuff as in Rivera-Thorsen et al. (in
prep.) could be mentioned, with a different emphasis. Star formation
rate should be mentioned from \citet{Adamo2010}. Population from same
and from \citet{Micheva2010}. Knots named by \citet{Vader1993}, and also
mentioned by \citet{Kunth2003}. It's an LBA \citep{Hoopes2007}, and an
LAE analog \citep{Hayes2007, Leitet2011}. Knot C a strong Ly$\alpha$
emitter \citep{Hayes2007}, and also a LyC emleaker
{[}\citet{Bergvall2006}; Leitet2011{]}. Kinematics, it's a merger
\citep{Ostlin1999, Ostlin2001, Ostlin2015}. More weight on the
Lyman-$\alpha$ escape thing, and LyC. Mention Ly$\alpha$ escape and the
histrory here, too? References:

\begin{figure*}
\centering
\includegraphics[width=0.600\hsize]{../Figs/Haroslit.pdf}
\caption{Approximate coverage of the COS aperture. The aperture, which
was centered on the supercluster in knot C, has a diameter of 2.5
\arcsec}\label{fig:apmap}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[]{../Figs/FullSpec.pdf}
\caption{Full spectrum in restframe wavelength of Haro 11 C. Redshift
adopted from \citet{Sandberg2013}. Orange lines denote Milky Way
absorption, while blue lines denote absorption internal to the
target.}\label{fig:fullspec}
\end{figure*}

\section{Analysis}\label{analysis}

\begin{figure}
\centering
\includegraphics[width=3.500in]{../Figs/HISLISProfiles.pdf}
\caption{The \ion{Si}{2} (\textbf{upper}) and \ion{Si}{4}
(\textbf{lower}) profiles included in this
study.}\label{fig:SingleLines}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=3.500in]{../Figs/LyACoverfracs.pdf}
\caption{\textbf{Upper panel}: Ly$\alpha$ profile of Haro 11 C, in
approximate units of the surrounding continuum level. Full line is the
measured values smoothed by a 5 px. flat kernel; surrounding shading
encloses the $\pm 1 \sigma$ error band. \textbf{Middle panel}: Black
steps show the averaged, LIS line profile, smoothed by a 5px kernel.
Surrounding gray shading denotes the $\pm 1 \sigma$ confidence band.
\textbf{Lower panel}: Same as middle panel, but for the \ion{Si}{4}
transitions.}\label{fig:HisLisLya}
\end{figure}

Bla bla bla

\section{Discussion and conclusions}\label{discussion-and-conclusions}

Bla bla bla

\bibliography{./main.bib}

\end{document}

### 2016-06-16 Code/DynVel.py

@@ -1,0 +1,289 @@
+#! /usr/bin/env/ python
+# -*- coding: utf-8 -*-
+
+import matplotlib as mpl
+#mpl.rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
+#mpl.rc('font',**{'family':'serif','serif':['Palatino']})
+mpl.rc('text', usetex=True)     # For pretty LaTeX fonts in plots
+import matplotlib.gridspec as grisp
+import matplotlib.pyplot as plt
+import numpy as np
+#import os
+#import pyfits as pf
+import scipy as sp
+#import scipy.constants as const
+import mpl_tricks as mpt
+
+#spedata = pf.getdata('./NormVIS.fits')
+#width = pf.getheader('./NormVIS.fits')
+#errdata = pf.getdata('./NormVIS.err.fits')
+#errhead = pf.getheader('./NormVIS.err.fits')
+#
+#xs = np.arange(errdata.shape[0])
+#wl = xs*width['CD1_1']+width['CRVAL1']
+clickcount = 0
+exes = []
+
+
+def onclick(event):
+    global clickcount
+    global exes
+    print 'button=%d, x=%d, y=%d, xdata=%f, ydata=%f' % (
+        event.button, event.x, event.y,
+        event.xdata, event.ydata)
+    if event.button == 1:
+        exes.append(event.xdata)
+        if((clickcount <= 1) | (clickcount > 3)):
+            linecolor = 'green'
+        else:
+            linecolor = 'red'
+        if(clickcount == 1):
+            plt.title('Click on left border of line')
+        elif(clickcount == 2):
+            plt.title('Click on right border of line')
+        elif(clickcount > 2):
+            plt.title('Click twice on right continuum for calibration')
+        plt.plot([event.xdata, event.xdata], [.9, 1.1],
+                 color=linecolor, linewidth=2)
+        plt.draw()
+        clickcount += 1
+        #print clickcount
+        if((clickcount == 2) | (clickcount == 4) | (clickcount == 6)):
+            #print exes[clickcount-2:clickcount]
+            plt.plot(exes[clickcount - 2:clickcount],
+                     [1, 1], linecolor, linewidth=2)
+            plt.draw()
+        if(clickcount > 6):
+            plt.close()
+
+
+def vel_bin_size(indict):
+    velocities = indict.Velocity
[…]

### 2016-06-16 Code/LARS_branding.py

@@ -1,0 +1,18 @@
+#!/usr/bin/python
+# -*- coding: utf8 -*-
+
+import pandas as pd
+import scipy as sp
+
+colours = [  "k", "c", "m", "orange", "k", "c", "m", "orange", "k", "c", "m", "orange", "k", "c", ]
+symbol  = [  "s", "s", "s", "s", "o", "o", "o", "o", "*", "*", "*", "*", "^", "^", ]
+lstyle  = [  "-", "-", "-", "-", "-", "-", "-", "--", "--", "--", "--", "--", "--", "--", ]
+msize   = [  10., 10., 10., 10., 11., 11., 11., 11., 15., 15., 15., 15., 10., 10., ]
+lnames  = ['LARS {:02d}'.format(i+1) for i in range(14)]
+
+lbrand = pd.DataFrame(index=range(1, 15))
+lbrand['col'] = colours
+lbrand['sym'] = symbol
+lbrand['sty'] = lstyle
+lbrand['siz'] = msize
+

### 2016-06-16 Code/LyaCFfig.py

@@ -1,0 +1,121 @@
+#!/usr/bin/env python
+# encoding: utf-8
+
+import matplotlib as mpl
+mpl.use('qt4agg')
+import matplotlib.pyplot as plt
+import numpy as np
+import scipy as sp
+import pandas as pd
+import cospaper as cosp
+import mpl_tricks as mp
+import wesanderson as wa
+wes = [farve for farve in wa.colors['Darjeeling2']]# if farve != wa.colors['Darjeeling2'][0]]
+cf_color = cosp.paircolors[3]
+cf_color2 = cosp.paircolors[7]
+
+wdata = pd.read_pickle('../Products/dfdict.pickle')[1]
+vdata = pd.read_pickle('../Products/vflis.pickle')[1]
+hdata = pd.read_pickle('../Products/vfhis.pickle')[1]
+z = 0.020434136
+# print wdata.head()
+# print vdata.head()
+#
+fig = plt.figure(figsize=(5.5, 5.5))
+
+cont = plt.subplot(111, frameon=False)
+cont.tick_params(labelleft='off', labelbottom='off')
+
+# ax1 = plt.subplot2grid((3, 1), (0, 0), rowspan=2, )
+# ax2 = plt.subplot2grid((3, 1), (2, 0))
+ax1 = plt.subplot(211)
+ax2 = plt.subplot(413)
+ax3 = plt.subplot(414)
+ax1.tick_params(labelsize=9)
+ax1.label_outer()
+ax2.label_outer()
+ax2.tick_params(labelsize=9)
+ax2.set_yticks([0, .5, 1.])
+ax3.tick_params(labelsize=9)
+ax3.set_yticks([0, .5, 1.])
+ax2.axis((-850, 850, -.2, 1.6))
+dfig, daxes = plt.subplots(2)
+dax1 = daxes[0]
+dax2 = daxes[1]
+cont = fig.add_subplot(111, frameon=False)
+cont.tick_params(labelleft='off', labelbottom='off', length=0)
+cont.set_xlabel(r'$v - v_0$ [km/s]', labelpad=15)
+cont.set_ylabel(r'\rm Relative flux', labelpad=18)
+
+twax = plt.twinx(ax2)
+twax.set_ylim(1.2, -.6)
+twax.set_yticks([0, .5, 1])
+twax.set_ylabel(r'$\mathbf{f_c(v)}$', color=cf_color)
[…]

### 2016-06-16 Code/cospaper.py

@@ -20,7 +20,6 @@ from linelists import COSlines, SDSSlines, MWlines, fikdict, wlsdict, \
 from uncertainties import ufloat as ufl
 from uncertainties import unumpy as unp
 
-
 #================================================================================
 #		Plot details setup.
 #================================================================================
@@ -498,6 +497,7 @@ def make_line_profile_plots(
                  'Si II 1260': 1260.42,
                  'Si II 1304': 1304.37,
                  'Si II 1526': 1526.72,
+                 'Si III 1206': 1206.50,
                  'Si IV 1122': 1122.49,
                  'Si IV 1393': 1393.76,
                  'Si IV 1402': 1402.77}

### 2016-06-16 Code/linelists.py

@@ -1,0 +1,90 @@
+#! /usr/bin/env python
+# -*- coding: utf-8 -*-
+
+import scipy as sp
+
+COSlines = sp.array([['01', 'Si IV', '1122.49'],
+                     ['02', 'Si II', '1190.42'],
+                     ['03', 'Si II', '1193.29'],
+                     ['04', 'Si III', '1206.50'],
+                     ['05', 'Si II', '1260.42'],
+                     ['06', 'O I', '1302.17'],
+                     ['07', 'Si II', '1304.37'],
+                     ['08', 'C II', '1334.53'],
+                     ['09', 'Si IV', '1393.76'],
+                     ['10', 'Si IV', '1402.77'],
+                     ['11', 'Si II', '1526.72']])
+
+SDSSlines = sp.array([['01', '_Hdelta', 4102.892],
+                      ['02', '_Hgamma', 4341.684],
+                      ['03', '_Hbeta' , 4862.683],
+                      ['04', '_Halpha', 6564.61 ],
+                      ['05', '_OI'    , 6302.046],
+                      ['06', '_OII'   , 3727.092],
+                      ['07', '_OII'   , 3729.875],
+                      ['08', '_OIII'  , 4960.295],
+                      ['09', '_OIII'  , 5008.240],
+                      ['11', '_NII'   , 6585.28 ],
+                      ['12', '_NII'   , 6549.85 ],
+                      ['13', '_SII'   , 6718.29 ],
+                      ['14', '_SII'   , 6732.67 ]])
+
+MWlines = {'C I 1157': 1157.1857,
+           'Si IV 1122': 1122.49,
+           'Si II 1190': 1190.42,
+           'Si II 1193': 1193.29,
+           'Si III 1206': 1206.50,
+           'Si II 1260': 1260.42,
+           'O I 1302': 1302.17,
+           'Si II 1304': 1304.37,
+           'C II 1334': 1334.53,
+           'Si IV 1393': 1393.76,
+           'Si IV 1402': 1402.77,
+           'C IV 1548': 1548.204,
+           'C IV 1550': 1550.781, # Doublet
+           'N I 1134': 1134.42,   # Triplet
+           'N I 1199': 1199.5496, # Triplet!
+           'N V 1238': 1238.821,
+           'N V 1242': 1242.804,
[…]

### 2016-06-16 Code/mpl_tricks.py

@@ -1,0 +1,130 @@
+# /usr/bin/env python
+# -*- coding: utf-8 -*-
+
+import matplotlib.pyplot as plt
+from matplotlib.collections import LineCollection
+from matplotlib import rc, rcParams, font_manager, cm
+from matplotlib.colors import colorConverter
+import scipy as sp
+
+pats = 16   # Plot Axis Title Size
+sfont = 14  # Small font for e.g. legends
+csz = 5     # Error bar cap size
+leg_prop = font_manager.FontProperties(size=sfont)
+# Set the ColorBrewer 'Set1' colr set as default colors. Because prettier.
+colorindices = sp.linspace(0, 256, 9)
+# CB_color_cycle = ('#e41a1c', '#377eb8', '#4daf4a',
+#                   '#984ea3', '#ff7f00', '#dede00', # '#ffff33',
+#                   '#a65628', '#f781bf', '#999999')
+CB_color_cycle = ['#377eb8', '#ff7f00', '#4daf4a',
+                  '#f781bf', '#a65628', '#984ea3',
+                  '#999999', '#e41a1c', '#dede00']
+
+CB_cycle2 = ()
+
+CUDcolorD = {}  # From http://python-cudtools.googlecode.com/hg/cudtools.py
+CUDcolorD['Black']          = (0, 0, 0)           #  cool
+CUDcolorD['Vermillion']     = (0.8, 0.4, 0)       # warm
+CUDcolorD['Blue']           = (0, 0.45, 0.7)      #  cool
+CUDcolorD['Orange']         = (0.9, 0.6, 0)       # warm
+CUDcolorD['Bluish Green']   = (0, 0.6, 0.5)       #  cool
+CUDcolorD['Reddish Purple'] = (0.8, 0.6, 0.7)     # warm
+CUDcolorD['Sky Blue']       = (0.35, 0.7, 0.9)    #  cool
+CUDcolorD['Yellow']         = (0.95, 0.9, 0.25)   # warm
+CUDcolorOrderL=['Vermillion', 'Blue',
+                'Orange', 'Bluish Green', 'Reddish Purple',
+                'Sky Blue', 'Yellow', 'Black']
+CUDCycle = ((0.8, 0.4, 0),
+            (0, 0.45, 0.7),
+            (0.9, 0.6, 0),
+            (0, 0.6, 0.5),
+            (0.8, 0.6, 0.7),
+            (0.35, 0.7, 0.9),
[…]

### 2016-06-16 Code/profiles.py

@@ -1,0 +1,93 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+import scipy as sp
+
+def lorentz(x, pos, hwhm, ampl):
+    """ Lorentz-Cauchy function expressed in terms of x0, gamma and height.
+
+    Parameters
+    ----------
+    x : numpy.ndarray
+        Wavelength array
+    pos : float
+        Wavelength of centroid.
+    hwhm : float
+        gamma, or half width half maximum.
+    ampl : float
+        Height of function peak.
+
+    Returns
+    -------
+    lor : numpy.ndarray
+    """
+    lor = ampl * hwhm ** 2 / (4 * (x - pos) ** 2 + hwhm ** 2)
+    lor = ampl * hwhm ** 2. / (( x - pos ) ** 2 + hwhm ** 2)
+    return lor
+
+# Gauss:
+def gauss(x, pos, sig, ampl=1.):
+    """ Gaussian distribution.
+
+    Parameters
+    ----------
+    x : numpy.ndarray
+        Wavelength array.
+    pos : float
+        Wavelength of centroid.
+    sig : float
+        Sigma of distribution.
+    ampl : float
+        Height of function peak.
+
+    Returns
+    -------
+    gau : numpy.ndarray
+    """
+    gau = ampl * sp.e**(-0.5 * ((x - pos) / sig) ** 2)
+    return gau
+
+# Voigt, from Tepper Garcia 2006:
+# FIXME: This whole thing depends on knowledge of resonator strengths and which
+# atom/molecule we are dealing with. Overkill?
+def _get_transition_info(transition='Halpha'):
+    """Still need to figure out if I am going to implement this.
+    If so, as far as possible build the design on that from vpfit...?
+    Call: f, gamma = _get_transition_info(transition)
+    """
+    resstrengths={'Halpha': 0.695800, 'Hbeta': 0.121800, 'Hgamma': 0.044370}
+    gammas = {'Halpha': 6.465e7, 'Hbeta': 2.062e7, 'Hgamma': 9.425e6}
+    f = resstrengths[transition]
+    g = gammas[transition]
+    wl = wavlens[transition]
+    return f, g
+
+
+def _H(a, u):
+    # The H(a, x) function of Tepper Garcia 2006
+    P  = u**2
+    H0 = np.e**(-(u**2))
+    Q  = 1.5/u**2
[…]

### 2016-06-16 Code/wesanderson/__init__.py

@@ -1,0 +1,9 @@
+""" A collection of color palettes inspired by Wes Anderson movies, inspired by
+the Tumblr blog [Wes Anderson Palettes](wesandersonpalettes.tumblr.com).
+
+Usage is very simple for now:
+    import wesanderson as wa
+    mr2 = wa[MoonRise2]
+
+"""
+from colors import colors

### 2016-06-16 Code/wesanderson/colors.py

@@ -1,0 +1,20 @@
+#!/usr/bin/python
+# -*- coding: utf-8 -*-
+
+colors = {
+    'GrandBudapest'  : ["#F1BB7B", "#FD6467", "#5B1A18", "#D67236"],
+    'Moonrise1'      : ["#F3DF6C", "#CEAB07", "#D5D5D3", "#24281A"],
+    'Royal1'         : ["#899DA4", "#C93312", "#FAEFD1", "#DC863B"],
+    'Moonrise2'      : ["#798E87", "#C27D38", "#CCC591", "#29211F"],
+    'Cavalcanti'     : ["#D8B70A", "#02401B", "#A2A475", "#81A88D", "#972D15"],
+    'Royal2'         : ["#9A8822", "#F5CDB4", "#F8AFA8", "#FDDDA0", "#74A089"],
+    'GrandBudapest2' : ["#E6A0C4", "#C6CDF7", "#D8A499", "#7294D4"],
+    'Moonrise3'      : ["#85D4E3", "#F4B5BD", "#9C964A", "#CDC08C", "#FAD77B"],
+    'Chevalier'      : ["#446455", "#FDD262", "#D3DDDC", "#C7B19C"],
+    'Zissou'         : ["#3B9AB2", "#78B7C5", "#EBCC2A", "#E1AF00", "#F21A00"],
+    'FantasticFox'   : ["#DD8D29", "#E2D200", "#46ACC8", "#E58601", "#B40F20"],
+    'Darjeeling'     : ["#FF0000", "#00A08A", "#F2AD00", "#F98400", "#5BBCD6"],
+    'Rushmore'       : ["#E1BD6D", "#EABE94", "#0B775E", "#35274A", "#F2300F"],
+    'BottleRocket'   : ["#A42820", "#5F5647", "#9B110E", "#3F5151", "#4E2A1E", "#550307", "#0C1707"],
+    'Darjeeling2'    : ["#ECCBAE", "#046C9A", "#D69C4E", "#ABDDDE", "#000000"],
+}

### 2016-06-16 Paper/makeaastex6.sh

@@ -1,0 +1,9 @@
+scholdoc Paper.md \
+--template=pandoc-aastex6.latex \
+--natbib \
+-t latex -o Paper.tex
+
+pdflatex Paper.tex
+bibtex Paper
+pdflatex Paper.tex
+

### 2016-08-28 Paper/Paper.tex
Writing writing writing.

@@
 % 
+\usepackage[caption=false]{subfig}
 
@@
 \footnotetext[1]{Based on observations Cosmic Origins Spectrograph on the Hubble Space
-Telescope, program XXXXXX, PI YYYYYYYY}
+Telescope, program GO 13017, PI Timothy Heckman}
 
@@
 \author{Göran Östlin\altaffilmark{2, 3}}
+
+\author{Matthew Hayes\altaffilmark{2, 3}}
 
@@
 \begin{abstract}
-Something something something.
+Star forming galaxies are believed to be the main source of ionizing
+radiation responsible for reionizing the early Universe. Direct
+observations have however been few and with escape fractions far below
+what would be necessary to account for the ionization history of the
+Universe. Especially in the local Universe, only a few handfuls of
+emitters have been observed with typical escape fractions of a few
+percent. It seems the mechanisms regulating this escape need to be ones
+that are strongly evolving with redshift, if galaxies are to be held
+responsible for the reionization. Gas mass, star formation feedback and
+thus star formation activity are among the main suspects, known to both
+regulate neutral gas coverage and evolve with cosmic time. In this
+paper, we present a reanalysis of far-UV HST-COS spectra of the first
+detected Lyman-continuum leaker in the local Universe, Haro 11, in which
+we examine the connections between Lyman-continuum leakage and
+Lyman-$\alpha$ line shape and feedback-influenced neutral ISM properties
+like kinematics, geometry and column density. In particular, we discuss
+the two extremes of an optically thin, density bounded ISM and a
+riddled, optically thick, ionization bounded ISM and how Haro 11 fit
+into the theoretical predictions made from these models. We find that
+the most likely ISM model for Haro 11 knot C is one of clumpy neutral
+medium with a highly ionized interclump medium with a combined covering
+fraction of near-Unity and a with a residual neutral gas column density
+of $XX N_{HI} < XX$, high enough to be optically thick to
+Lyman-$\alpha$, but low enough to be at least partly transparent to
+Lyman-continuum.
 \end{abstract}
@@
 
-About Haro 11: Some of the same stuff as in Rivera-Thorsen et al. (in
-prep.) could be mentioned, with a different emphasis. Star formation
-rate should be mentioned from \citet{Adamo2010}. Population from same
-and from \citet{Micheva2010}. Knots named by \citet{Vader1993}, and also
+\subsection{Background:}\label{background}
+
+\subsection{About Haro 11:}\label{about-haro-11}
+
+Some of the same stuff as in Rivera-Thorsen et al. (in prep.) could be
+mentioned, with a different emphasis. Star formation rate should be
+mentioned from \citet{Adamo2010}. Population from same and from
+\citet{Micheva2010}. Knots named by \citet{Vader1993}, and also
 mentioned by \citet{Kunth2003}. It's an LBA \citep{Hoopes2007}, and an
 LAE analog \citep{Hayes2007, Leitet2011}. Knot C a strong Ly$\alpha$
-emitter \citep{Hayes2007}, and also a LyC emleaker
+emitter \citep{Hayes2007}, and also a LyC leaker
 {[}\citet{Bergvall2006}; Leitet2011{]}. Kinematics, it's a merger
@@
 Lyman-$\alpha$ escape thing, and LyC. Mention Ly$\alpha$ escape and the
-histrory here, too? References:
+history here, too? References:
 
-\begin{figure*}
-\centering
-\includegraphics[width=0.600\hsize]{../Figs/Haroslit.pdf}
-\caption{Approximate coverage of the COS aperture. The aperture, which
-was centered on the supercluster in knot C, has a diameter of 2.5
-\arcsec}\label{fig:apmap}
-\end{figure*}
+This observation is first (?) published in \citet{Alexandroff2015}, and
+also in \citet{Verhamme2015} in which the Ly$\alpha$ profile is dicussed
+as a .
 
-\begin{figure*}
-\centering
-\includegraphics[]{../Figs/FullSpec.pdf}
-\caption{Full spectrum in restframe wavelength of Haro 11 C. Redshift
-adopted from \citet{Sandberg2013}. Orange lines denote Milky Way
-absorption, while blue lines denote absorption internal to the
-target.}\label{fig:fullspec}
-\end{figure*}
+This observation is part of the sample in \citet{Alexandroff2015}, in
+which details about observation and data reduction are described in
+depth; we pint the reader there for further information about these. The
+Ly$\alpha$ profile in this spectrum is discussed in
+\citet{Verhamme2015}. \citet{Heckman2011}, \citet{Heckman2015}.
+\citet{Jaskot2013}, \citet{JaskotOey}. \citet{Bouwens2012}.
+
+In this paper, we analyze HST-COS spectra of knot C in Haro 11. The
+observations were done as part of HST program GO 13017, PI Timothy
+Heckman. The spectrum has first been published by
+\citet{Alexandroff2015}, a sample paper in which an attempt is made of
 
 \section{Analysis}\label{analysis}
+
+\subsection{Individual lines}\label{individual-lines}
+
+Figure~\ref{fig:SingleLines} shows the individual profiles of the
+transitions included in our analysis; the upper panel shows transitions
+of \ion{Si}{2}, lower panel of \ion{Si}{4}. It is plainly visible that
+the ionization fraction is high, with the \ion{Si}{4} curves being
+considerably deeper than the low-ionized lines. Looking at the upper
+panel, \ion{Si}{2} $\lambda \lambda 1304, 1526$ are somewhat shallower
+than \ion{Si}{2} $\lambda 1260$. The former two lines have comparable
+resonator strengths, both about a factor of 10 lower than that of
+$\lambda 1260$. It is thus clear that we do not find ourselves in the
+optically thin regime, in which the latter line should be
+correspondingly around 10 times stronger; on the other hand, it is
+possible that the two weak lines are not completely saturated. In the
+lower panel, the two lines have resonator strengths within a factor of 2
+of each other. They are thus at first glance consistent with a medium
+that is not completely opaque, but not with an optically thin one. The
+stronger absorption in \ion{Si}{4} reveals a high level of ionization of
+the medium covering the central cluster.
 
@@
 \end{figure}
+
+\subsection{$N_{Si}$ and $f_C$}\label{sec:aod}
+
+Following the method described in \citet{RiveraThorsen2015}; we have
+performed fits for column density and covering factor in each velocity
+bin, for both the high- and low-ionization state. The results are shown
+in fig.~\ref{fig:WithColDens}. The upper panels show the pseudo-reduced
+$\chi^2$ as defined in \citet{RiveraThorsen2015} (
+$=\chi^2 / (\mathrm{DOF} + 1)$ ) for each bin, middle panels show the
+inferred column density in each bin, with surrounding shaded columns
+showing the confidence intervals. In the lower panels, the mean LIS line
+profile is shown in black with gray shaded uncertainty intervals. On
+these are overlaid the best-fit values of $f_C$ as colored dots, with
+surrounding shaded bars showing the confidence intervals. We again
+caution that $f_C$ is the covering fraction of HI atoms \emph{within the
+given velocity bin}, and hence only provides a lower limit for the
+total, geometric neutral gas covering fraction, since gas at different
+velocities generally does not occupy the same projected area.
+
+\begin{figure*}
+\centering
+\subfloat[LIS\label{coldenLIS}]{\includegraphics[width=0.400\hsize]{../Figs/Fc_haro11c_LIS.pdf}}
+\subfloat[\ion{Si}{4}\label{coldenHIS}]{\includegraphics[width=0.400\hsize]{../Figs/Fc_haro11c-SiIV.pdf}}
+\caption{\textbf{Upper panels}: Pseudo-reduced $\chi^2$ as described in
+\citet{RiveraThorsen2015}. \textbf{Middle panels}: Best-fit ion column
+density with confidence intervals in shaded gray. \textbf{Lower panels}:
+Mean LIS/\ion{Si}{4} profile shown as black steps, with inferred $f_C$
+shown with yellow dots. Lighter shaded columns show confidence intervals
+for both.}\label{fig:WithColDens}
+\end{figure*}
+
+\section{Discussion and conclusions}\label{discussion-and-conclusions}
+
+\subsection{Lyman-$\alpha$ and neutral absorption
+profiles}\label{sec:LISLya}
 
@@
 
-Bla bla bla
-
-\section{Discussion and conclusions}\label{discussion-and-conclusions}
-
-Bla bla bla
+Bla bla bla Bla bla bla
 

### 2016-08-28 Code/cospaper.py

@@ -1639,7 +1639,7 @@ def draw_coverfrac_axes(veldf, ax1, ax2, ax3, ms=3,
         larsname = veldf.columns.name
         if legend:
             leg = ax3.legend(
-                fancybox=True, shadow=False, loc='best',
+                fancybox=True, shadow=False, loc='lower left',
                 fontsize=8)
             leg.set_title(larsname, prop={'size':7})
             leg.draggable()
@@ -1669,7 +1669,7 @@ def single_coverfrac_plot(
 
     ax1.set_ylim(0, 80)
     ax2.set_ylim(9, 16)
-    ax3.set_xlim(-1050, 1050)  # Yeah, hardcoding. A sane default, though.
+    ax3.set_xlim(-900, 600)  # Yeah, hardcoding. A sane default, though.
     ax3.tick_params(labelsize=8)
     ax4.tick_params(labelsize=8)
     ax3.set_ylim(-.2, 1.6)

### 2016-08-28 Code/helper_functions.py

@@ -14,7 +14,9 @@ import matplotlib.pyplot as plt
 
 def hello_there():
     os.system('notify-send -i ipython "IPython process done! "')
-    os.system('play --no-show-progress --null --channels 1 synth {} sine {}'.format(.6, 550))
+    os.system(
+        'play --no-show-progress --null --channels 1 synth {} sine {}'\
+        .format(.6, 550))
 
 
 def _extract_1d(data, errs, LineLo, LineUp):

### 2016-11-16 Paper/Paper.tex
many minor updates, lost track

--- 2016-06-16 Paper/Paper.tex
@@
 %%%============================================================================
-\documentclass[preprint2]{aastex6}
+\documentclass[twocolumn]{aastex61}
 % \usepackage{lmodern}
@@
 
+%% Command to document which AAS Journal the manuscript was submitted to.
+%% Adds "Submitted to " the arguement.
+
 % % \date{\today}
 % 
+\usepackage[caption=false]{subfig}
 
@@
 %%%-----------------------------------------------------------------------
-
 \begin{document}
 
-\title{Neutral ISM, Lyman-Alpha and Lyman-continuum in nearby starburst Haro 11\footnotemark[1]}
-\footnotetext[1]{Based on observations Cosmic Origins Spectrograph on the Hubble Space
-Telescope, program XXXXXX, PI YYYYYYYY}
+\title{Neutral ISM, Lyman-Alpha and Lyman-continuum in nearby starburst Haro 11}
 
-\author{T. Emil Rivera-Thorsen\altaffilmark{2, 3}}
+\title{Neutral ISM, Lyman-Alpha and Lyman-continuum in nearby starburst Haro 11
+		                    \footnote{Based on observations with HST-COS, program GO 13017, PI Heckman}
+	            }
+%
+\correspondingauthor{T. Emil Rivera-Thorsen}
+\email{trive@astro.su.se}
 
-\author{Göran Östlin\altaffilmark{2, 3}}
-
-\altaffiltext{2}{Department of Astronomy, Oskar Klein Centre, Stockholm University,
-AlbaNova University Centre, SE-106 91 Stockholm, Sweden}
-\altaffiltext{3}{Oscar Klein Centre for Cosmoparticle Physics, Department of Astronomy,
-Stockholm University, Stockholm, Sweden}
+\author{T. Emil Rivera-Thorsen}
+\affil{Department of Astronomy, Stockholm University, AlbaNova University
+Centre, SE-106 91 Stockholm, Sweden}
+\affil{Oscar Klein Centre for Cosmoparticle Physics, Stockholm, Sweden}
+\author{Göran Östlin}
+\affil{Department of Astronomy, Stockholm University, AlbaNova University
+Centre, SE-106 91 Stockholm, Sweden}
+\affil{Oscar Klein Centre for Cosmoparticle Physics, Stockholm, Sweden}
+\author{Matthew Hayes}
+\affil{Department of Astronomy, Stockholm University, AlbaNova University
+Centre, SE-106 91 Stockholm, Sweden}
+\affil{Oscar Klein Centre for Cosmoparticle Physics, Stockholm, Sweden}
+\author{Johannes Puschnig}
+\affil{Department of Astronomy, Stockholm University, AlbaNova University
+Centre, SE-106 91 Stockholm, Sweden}
+\affil{Oscar Klein Centre for Cosmoparticle Physics, Stockholm, Sweden}
 
 \begin{abstract}
-Something something something.
+Star forming galaxies are believed to be the main source of ionizing
+radiation responsible for reionizing the early Universe. Direct
+observations of escaping ionizing radiation have however been few and
+with escape fractions far below what would be necessary to account for
+the ionization history of the Universe. In the local Universe, only a
+few handfuls of emitters have been observed with typical escape
+fractions of a few percent. It seems the mechanisms regulating this
+escape need to be strongly evolving with redshift, if galaxies are to be
+held responsible for reionization. Gas mass, star formation feedback and
+thus star formation activity are among the main suspect parameters,
+known to both regulate neutral gas coverage and evolve with cosmic time.
+In this paper, we present a reanalysis of far-UV HST-COS spectra of the
+first detected Lyman-continuum leaker in the local Universe, Haro 11, in
+which we examine the connections between Lyman-continuum leakage and
+Lyman-$\alpha$ line shape and feedback-influenced neutral ISM properties
+like kinematics, geometry and column density. We discuss the two
+extremes of an optically thin, density bounded ISM and a riddled,
+optically thick, ionization bounded ISM and how Haro 11 fits into the
+theoretical predictions made from these models. We find that the most
+likely ISM model for Haro 11 knot C is one of clumpy neutral medium
+embedded in a highly ionized inter-clump medium with a combined covering
+fraction of unity and a residual neutral gas column density in the
+ionized medium of
+$5 \times 10^{13} \leq N_{\rm HI} \leq 3 \times 10^{16}$; high enough to
+be optically thick to Lyman-$\alpha$, but low enough to be at least
+partly transparent to Lyman-continuum and undetectable in Si\textsc{ii}.
 \end{abstract}
@@
 
-About Haro 11: Some of the same stuff as in Rivera-Thorsen et al. (in
-prep.) could be mentioned, with a different emphasis. Star formation
-rate should be mentioned from \citet{Adamo2010}. Population from same
-and from \citet{Micheva2010}. Knots named by \citet{Vader1993}, and also
-mentioned by \citet{Kunth2003}. It's an LBA \citep{Hoopes2007}, and an
-LAE analog \citep{Hayes2007, Leitet2011}. Knot C a strong Ly$\alpha$
-emitter \citep{Hayes2007}, and also a LyC emleaker
-{[}\citet{Bergvall2006}; Leitet2011{]}. Kinematics, it's a merger
-\citep{Ostlin1999, Ostlin2001, Ostlin2015}. More weight on the
-Lyman-$\alpha$ escape thing, and LyC. Mention Ly$\alpha$ escape and the
-histrory here, too? References:
+Even though star forming galaxies are believed to give rise to the
+majority of radiation reionizing the Universe at early times, it remains
+unknown which physical conditions can facilitate the escape of the
+necessary amounts of radiation from these galaxies, which contain large
+amounts of neutral gas opaque to this radiation at higher column
+densities. Searches for leaking galaxies at redshifts $z \gtrsim 1$ have
+yielded few detections
+\citep[e.g.][]{Iwata2009, Vanzella2010, Vanzella2012, Nestor2013, Cowie2009, Siana2010},
+at escape fractions well below the $\sim 20\%$ needed to account for
+cosmic reionization \citep{Bouwens2011, Robertson2013}. A population of
+lower mass and lower luminosity, star forming galaxies are expected to
+contribute to reionization, too, but high star formation is usually
+coincident with higher neutral gas mass, which would cause a higher
+probability of blocking the ionizing photons
+\citep[e.g.][]{Erb2016, Robertson2013}. In the local Universe, only 9
+leakers have been detected so far
+\citetext{\citealp{Bergvall2006}; \citealp{Leitet2011}; \citealp{Leitet2013}; \citealp{Borthakur2014}; \citealp[Izotov2016Nat;][]{Izotov2016MNRAS}; \citealp{Leitherer2016}},
+at escape fractions ranging typically between 1-8\%, with one as high as
+$f_{\mathrm{esc}} \approx 13\%$ \citep{Izotov2016MNRAS}.
 
-\begin{figure*}
+Models of ISM surrounding a central source and allowing escape of Lyman
+continuum (LyC), span the range of two extremes: In one regime, the
+surrounding gas is optically thin, highly ionized and density-bounded
+\citep[see e.g.][]{Jaskot2013}, allowing unblocked escape for at least a
+fraction of ionizing photons. In the other regime, the central source is
+surrounded by an optically thick, ionization bounded medium with the
+neutral medium surrounding the central Strömgren sphere not completely
+covering all lines of sight to the background source. This is what is
+called the \emph{picket fence model} by \citet{Heckman2011}, or the
+\emph{riddled ionization bounded medium} by \citet{Verhamme2015}. The
+latter paper presents modeling of the imprints of these two extreme
+scenarios on the observed spectral signature of Lyman-$\alpha$ emission
+lines, and suggest how these can help point to candidate LyC leakers.
+The authors compare their theoretical predictions to sample of
+Lyman-$\alpha$ profiles, including a section of the spectrum treated in
+this work.
+
+The present HST-COS observation is part of the sample in
+\citet{Heckman2015} and \citet{Alexandroff2015}, in which details about
+observation and data reduction are described in depth; we point the
+reader there for further information about these. The Ly$\alpha$ profile
+in this spectrum is discussed in \citet{JaskotOey}.
+
+In (Rivera-Thorsen et al., submitted to \apj), we analyzed optical and
+NUV nebular emission lines in slit spectra from ESO VLT/X-Shooter
+\citep[see also][]{Guseva2012}. We find from kinematics modelling that
+both knot B and knot C are associated to a component blueshifted by
+$\sim 50 - 100$ km s\textsuperscript{-1} wrt. the mean nebular velocity.
+This component reaches as far as $\sim 200$ pc. SE of knot B, and
+$\sim 1.5$ kpc S of the midpoint between the two knots. Given the dense
+cloud coverage of knot B and the strong star formation activity in both
+knots, we conclude that this component is not only approaching but also
+found in front of the starburst regions and thus along the LOS to knot
+C.
+
+Recently, the galaxy has been observed in 21 cm H\textsc{i} emission
+with the 100 m. Robert C. Byrd Green Bank Telescope
+\citep{Pardy2016arXiv}. The authors find that Haro 11 has a low gas mass
+and a very low neutral gas to stellar mass fraction, and that it
+contains around twice as much ionized as neutral Hydrogen.
+Interestingly, the authors also find that the bulk of the neutral gas is
+redshifted wrt. the systemic velocity defined from nebular emission from
+the H\textsc{ii} regions surrounding the main starbursts, signifying
+that the majority of the neutral gas reserves are detached from the star
+formation activity, possibly a tidal arm being flung outwards as a part
+of the ongoing merger event.
+
+In this paper, we re-analyze the HST-COS spectrum of Haro 11 C acquired
+as part of HST program GO 13017, PI Timothy Heckman. It was first
+published in \citet{Alexandroff2015} as part of a sample of 22 Lyman
+Break Analog (LBA) galaxies analyzed individually and as a stack. These
+authors mainly focus on three indirect indicators of LyC leakage
+\citep{Overzier2009, Heckman2011}: Residual flux in the trough of
+saturated ISM absorption lines, blueshifted emission in Lyman-$\alpha$,
+and weak optical {[}\ion{S}{2}{]} emission lines.
+
+\begin{figure}
 \centering
-\includegraphics[width=0.600\hsize]{../Figs/Haroslit.pdf}
-\caption{Approximate coverage of the COS aperture. The aperture, which
-was centered on the supercluster in knot C, has a diameter of 2.5
-\arcsec}\label{fig:apmap}
-\end{figure*}
+\includegraphics[width=3.500in]{../Figs/Haroslit.pdf}
+\caption{Approximate position of the COS aperture, shown on HST imaging
+data of \citet{Hayes2009}; \citet{Ostlin2009}, encoding UV continuum in
+green, H$\alpha$ in red, and continuum subtracted Lyman $\alpha$ in
+blue. N is up, E is to the left.}\label{fig:apert}
+\end{figure}
+
+We measure a number of kinematic parameters for both the neutral (LIS)
+and high-ionized (HIS) phase, and apply the apparent optical depth
+method \citep{Savage1991, Pettini2002, Quider2009, Jones2013}, with the
+implementation being as described in \citet{RiveraThorsen2015} (RT15),
+to infer geometric properties of the neutral medium and constrain the
+column density of neutral hydrogen covering the background source under
+the assumption that the LyC photons detected from this galaxy do indeed
+escape from knot C.
 
@@
 \includegraphics[]{../Figs/FullSpec.pdf}
-\caption{Full spectrum in restframe wavelength of Haro 11 C. Redshift
-adopted from \citet{Sandberg2013}. Orange lines denote Milky Way
-absorption, while blue lines denote absorption internal to the
-target.}\label{fig:fullspec}
+\caption{Overview of the relevant regions of the COS spectrum of Haro 11
+C, shown in rest frame wavelengths of the object. Some key spectral
+lines are marked; Milky Way features in orange, features of Haro 11 in
+blue.}\label{fig:fullspec}
 \end{figure*}
 
+Fig.~\ref{fig:fullspec} gives an overview of the COS spectrum of Haro 11
+C treated in this work. Some important features are marked in blue
+(internal to Haro 11) or orange (Milky Way features).
+
+\subsection{Effective resolution}\label{effective-resolution}
+
+For a point source, the resolution of the Cosmic Origins Spectrograph is
+$R=20,000$, which corresponds to six pixels of the extracted spectrum
+per resolution element. We have therefore binned the data by a factor of
+6 to minimize noise while not losing information. The resolution,
+however, is generally lower than this for extended sources; for a
+uniformly filled aperture, it is as low as $R\approx2,000$. For more
+morphologically complex sources, the effective resolution depends on the
+exact shape and angular size of the target.
+
+To estimate the effective resolution for this target, we proceeded as
+follows. We used archival imaging data of Haro 11 in the UV-continuum
+from \citet{Ostlin2009}; \citet{Hayes2009}; since the absorption lines
+treated here have resolution determined by the properties of their
+surrounding continuum. We the extracted a circular image at the same
+position and radius as the COS aperture, which was rotated to match the
+orientation of the COS as given in the spectrum headers. We then
+modelled vignetting in the COS aperture by multiplying each pixel in the
+circular UV-continuum image with an interpolation of the values given in
+the throughput grid in Fig. 7 in \citet{CosImaging}. Finally, the
+aperture cutouts were collapsed along the cross-dispersion direction,
+and the FWHM of the flux distribution along the dispersion direction is
+reported as the effective seeing of this observation. This is converted
+from arc seconds to COS resolution elements by the factor 0.171
+arcsec/resel reported in the COS instrument handbook \citep{CosHandbook}
+
+\begin{figure}
+\centering
+\includegraphics[width=1.000\hsize]{../Figs/EffResol.pdf}
+\caption{Effective resolution estimate. \textbf{Upper left}: Haro 11 in
+UV-continuum, data from \citet{Ostlin2009}; \citet{Hayes2009}. Data is
+shown on a square root scale and cut levels set for best detail. Inset
+in blue tinting is the COS aperture covering the region surrounding knot
+B in the terminology of \citet{Vader1993}. N is up, E is left.
+\textbf{Upper right}: The extracted, throughput-corrected in-aperture
+image, rotated so horizontal corresponds to the dispersion direction of
+the spectrograph. \textbf{Lower panel}: The collapsed flux profile in
+the aperture, with the shaded region showing the width of the effective
+resolution element, which is also given in arc seconds and resolution
+elements/bins.}\label{fig:resol}
+\end{figure}
+
+The procedure is illustrated in Fig.~\ref{fig:resol}. Here, the upper
+left panel shows Haro 11 in UV-continuum using HST imaging data from
+\citet{Ostlin2009}; \citet{Hayes2009}, with the COS aperture coverage
+from this observation overlaid in blue tinting. The upper right panel
+shows the galaxy as the COS saw it, with the region covered by the
+aperture cut out, rotated and vignetting-corrected as described above.
+Finally, the lower panel shows the flux profile in the aperture,
+collapsed along the cross dispersion direction. The FWHM of this
+distribution has been adopted as the effective resolution for this
+observation. We find $R_{\text{eff}} = 0.3 \arcsec = 1.75$ resolution
+elements, which at the wavelength of observed Ly$\alpha$ corresponds to
+31 km s⁻¹.
+
 \section{Analysis}\label{analysis}
+
+\subsection{Individual lines}\label{individual-lines}
+
+Figure~\ref{fig:SingleLines} shows the individual profiles of the
+transitions included in our analysis; the upper panel shows transitions
+of \ion{Si}{2}, lower panel of \ion{Si}{4}. It is plainly visible that
+the ionization fraction is high, with the \ion{Si}{4} curves being
+considerably deeper than the low-ionized lines. Looking at the upper
+panel, \ion{Si}{2} $\lambda \lambda 1304, 1526$ are somewhat shallower
+than \ion{Si}{2} $\lambda 1260$. The former two lines have comparable
+oscillator strengths, both about a factor of 10 lower than that of
+$\lambda 1260$. It is thus clear that we do not find ourselves in the
+optically thin regime, in which the latter line should be
+correspondingly around 10 times stronger; on the other hand, it is
+possible that the two weak lines are not completely saturated. In the
+lower panel, the two \ion{Si}{4} lines have oscillator strengths within
+a factor of 2 of each other. They are thus at first glance consistent
+with a medium that is not completely opaque, but not with an optically
+thin one, and within uncertainties consistent with the optically thick.
+The stronger absorption in \ion{Si}{4} reveals a high level of
+ionization of the medium covering the central cluster.
 
@@
 \includegraphics[width=3.500in]{../Figs/HISLISProfiles.pdf}
-\caption{The \ion{Si}{2} (\textbf{upper}) and \ion{Si}{4}
-(\textbf{lower}) profiles included in this
-study.}\label{fig:SingleLines}
+\caption{The \ion{Si}{2} and other LIS (\textbf{upper}) and \ion{Si}{4}
+(\textbf{lower}) profiles included in this study. Dashes denote data
+points masked out due to foreground contamination. Note the
+high-velocity component in both \ion{Si}{4} lines, extending out to
+$\sim 850$ km s⁻¹.}\label{fig:SingleLines}
 \end{figure}
+
+\input{table1}
+
+\subsection{$N_{\rm Si}$ and $f_C$}\label{sec:aod}
+
+Following the method described in RT15, we have performed fits for
+column density and covering factor in each velocity bin, for both the
+high- and low-ionization state. Here we shall briefly summarize the
+method, but refer to RT15 and references therein for a detailed
+explanation.
+
+In any given velocity bin, the line intensity in terms of the continuum
+intensity is given as
+
+%
+\begin{equation*}
+\frac{I}{I_0} = 1 - f_C (1 - e^{-\tau}), 
+\end{equation*}
+%
+
+with the optical depth $\tau$ given as:
+
+%
+\begin{equation*}
+\tau = f\lambda \frac{\pi e^2}{m_e c} N 
+       = f\lambda \frac{N}{3.768 \times 10^{14}} 
+\end{equation*}
+%
+
+Here, $f$ is the oscillator strength of a given transition, $\lambda$ is
+its rest frame wavelength in Å, $N = N(v)$ is the column density of the
+relevant ion \emph{within the given velocity bin}, and $f_{C}$ is the
+covering fraction of neutral gas \emph{moving at the given velocity}.
+When multiple absorption lines are present which arise from the same
+ground state; the population of this state is the same for all
+transitions, and their relative strengths are governed simply by their
+oscillator strengths, and with two or more such transitions, $f_{C}$ and
+$N$ can be inferred from knowledge of $f \lambda$ and measured values of
+$I/I_0$.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.800\hsize]{../Figs/AOD-details-example.pdf}
+\caption{Illustration of the AOD computations. \textbf{Upper panel}: the
+three \ion{Si}{2} lines in this analysis shown together, with the
+zero-velocity bin marked with a vertical red line. \textbf{Lower panel}:
+From this bin, the three measured relative intensities are plotted
+against $f\lambda$ as black dots, with vertical error bars showing the
+error spectrum from the COS pipeline. Also shown is the best-fit
+function $I/I0 (f \lambda)$ as defined above. Also shown for
+illustration are the two extreme examples of a very high column density
+and unchanged covering fraction, and of a very high covering fraction
+but significantly lower column density.}\label{fig:AOD}
+\end{figure}
+
+The method is illustrated in Fig.~\ref{fig:AOD}: In the upper panel is
+shown the line profiles of the three \ion{Si}{2} transitions included in
+the analysis. The red vertical line marks the zero-velocity bin. From
+this bin, the three relative fluxes are plotted in the lower frame
+against their wavelength scaled oscillator strengths $f\lambda$ on the
+$x$ axis. In magenta is shown the best fit of the function
+$I/I_0 (f\lambda)$ described above. Also shown are two examples of
+different parametrizations of this function, to show how the two
+parameters influence its shape. One, in dotted gray, shows what happens
+to the best-fit function when $N$ is raised strongly, while $f_C$ is
+kept unchanged, while the other in gray dashes shows the curve for a
+$f_C \approx 1$ and $N$ is $~0.5$ dex below the best-fit value. This is
+of interest to the discussion of radiative transfer effects below in
+sect.~\ref{sec:rt}.
+
+The resulting values of $N_{\text{Si\textsc{ii}}}$ and $f_C$ are shown
+in fig.~\ref{fig:WithColDens}. The upper panels show the pseudo-reduced
+$\chi^2$ as defined in RT15 ( $=\chi^2 / (\mathrm{DOF} + 1)$) for each
+bin, middle panels show the inferred column density in each bin, with
+surrounding shaded columns showing the confidence intervals. In the
+lower panels, the mean LIS line profile is shown in black with gray
+shaded uncertainty intervals. On these are overlaid the best-fit values
+of $f_C$ as colored dots, with surrounding shaded bars showing the
+confidence intervals. We again caution that $f_C$ is the covering
+fraction of neutral gas \emph{within the given velocity bin}, and hence
+only provides a lower limit for the total, geometric neutral gas
+covering fraction, since gas at different velocities generally does not
+occupy the same projected area.
+
+\begin{figure*}
+\centering
+\subfloat[LIS\label{coldenLIS}]{\includegraphics[width=0.400\hsize]{../Figs/Fc_haro11c_LIS.pdf}}
+\subfloat[\ion{Si}{4}\label{coldenHIS}]{\includegraphics[width=0.400\hsize]{../Figs/Fc_haro11c-SiIV.pdf}}
+\caption{\textbf{Upper panels}: Pseudo-reduced $\chi^2$ as described in
+RT15. \textbf{Middle panels}: Best-fit ion column density with
+confidence intervals in shaded gray. \textbf{Lower panels}: \ion{Si}{2}
+1260 / mean\ion{Si}{4} profile shown as black steps, with inferred $f_C$
+shown with yellow dots. Lighter shaded columns show confidence intervals
+for both.}\label{fig:WithColDens}
+\end{figure*}
+
+\subsection{\ion{C}{2} $\lambda 1334$
+absorption}\label{lambda-1334-absorption}
+
+Looking back at Fig.~\ref{fig:SingleLines}, the profile of \ion{C}{2}
+$\lambda 1334$ is clearly deeper than \ion{Si}{2} $\lambda 1260$, which
+we had otherwise concluded is optically thick and thus provides a limit
+for the velocity binned covering fractions. We believe the explanation
+is a contribution from \ion{C}{2} $\lambda$ 1335.7 blending with
+$\lambda 1334$. This transition has an oscillator strength of
+$f_{ik} = 0.114$, compared to $f_{ik} = 0.127$ for $\lambda 1334$ (there
+is a third line at 1335 Å, but that is an order of magnitude weaker), so
+given a sufficient population of its ground level, it is strong enough
+to make a non-negligible contribution to the resulting line profile. One
+should however bear in mind that these lines rise from different lower
+fine structure levels; $\lambda 1334$ arises from ²P$_{1/2}$, while the
+other two arise from ²P$_{3/2}$. The population of the latter level
+depends sensitively on physical conditions in its system of origin,
+especially those in photo dissociation regions.
+
+\begin{figure}
+\centering
+\includegraphics[width=3.500in]{../Figs/CIIdoubletmodel.pdf}
+\caption{C \ion{C}{2} 1334, \ion{Si}{2} 1260, along with a \ion{C}{2}
+line synthesized from \ion{Si}{2} (see text for
+details).}\label{fig:CII}
+\end{figure}
+
+Fig.~\ref{fig:CII} shows a quick back-of-the-envelope check of this
+hypothesis. Assuming the ions reside in the same physical regions, we
+used the \ion{Si}{2} and a second contribution created by shifting the
+original profile to the red by the appropriate velocity ($\sim 260$ km
+s⁻¹) and multiplying it by a free parameter, which was chosen by eye to
+give a reasonable replication of the observed \ion{C}{2}; the chosen
+value shown in the figure is 0.7 times the original line. It is clear
+from the figure that the reproduction of the observed \ion{C}{2} line is
+very reasonable, considering that it is generated from a different
+species with a very different ionization potential.
+
+Whether this is a physically reasonable strength is difficult to say
+with precision, but we note that to reproduce the feature observed,
+$\lambda 1334$ must be optically thick and $\lambda 1335$ part
+transparent. This leave open a degeneracy of relative level populations
+and ion abundance, such that the choice of this value only weakly
+constrains these quantities and thus it is compatible with a wide range
+of scenarios.
+
+It is also worth noting that \ion{C}{2} has a significantly higher
+ionization potential than \ion{Si}{2}, such that the former will be more
+abundant in regions of higher ionization, with \ion{C}{2} in effect
+tracing slightly different regions than \ion{Si}{2}. Furthermore, in
+these regions of higher ionization, the relative level populations of
+the Carbon ground state can be significantly altered by shifts in
+e.g.~electron density and radiation field, which can alter the line
+shape further. We make no attempt at mapping these complex conditions
+here, but note only that there exists a range of non-exotic physical
+effects which can generate the deeper and wider $\lambda 1334$ profile
+we observe while still being compatible with the ISM being optically
+thick in $\lambda 1260$.
+
+\section{Discussion and conclusions}\label{discussion-and-conclusions}
+
+\subsection{Lyman-$\alpha$ and ISM absorption
+profiles}\label{sec:LISLya}
+
+In fig.~\ref{fig:HisLisLya}, we show the neutral and ionized absorption
+profile as in fig.~\ref{fig:WithColDens} together with the profile of
+Ly$\alpha$ on a common velocity scale.
 
@@
 \textbf{Lower panel}: Same as middle panel, but for the \ion{Si}{4}
-transitions.}\label{fig:HisLisLya}
+transitions. }\label{fig:HisLisLya}
 \end{figure}
 
-Bla bla bla
+The picture is what we would expect from a Lyman Continuum leaker: weak
+neutral and strong ionized absorption profiles, the latter almost
+everywhere consistent with full coverage, reveal a highly ionized medium
+in front of the central cluster. This is also in good agreement with the
+findings of Pardy et al. (submitted), who conclude that the galaxy has
+about twice as much ionized as neutral gas. In addition to this, it is
+interesting to note the close similarity in shape between the
+\ion{Si}{2} and \ion{Si}{4} line profiles, indicating that they likely
+originate in the same higher density regions. These regions will likely
+be ionized on the side facing the central cluster, being photoionized by
+its hot, massive stars. This also implies that the nebular emission
+outflow found in {[}Rivera-Thorsen et al, submitted{]} at least
+partially traces the same gas as the \ion{Si}{4} absorption here and, by
+extension, also the neutral medium. Looking at
+fig.~\ref{fig:SingleLines}, we see that maximum absorption and thus the
+largest amount of gas in a single velocity bin for both phases is found
+at around $v \approx -50$ km s⁻¹, where also a component is found in
+{[}Rivera-Thorsen et al., submitted{]}. The outflow velocity
+$v_{\text{int}}$ is at 149 ± 7 km s⁻¹, fully consistent with the
+findings of \citet{Heckman2015} and \citet{Alexandroff2015}.
+Interestingly, \citet{Sandberg2013} found from the neutral Sodium
+resonance absorption doublet $\lambda \lambda 5889.95,5895.92$ (NaD) an
+overall, weak \emph{redshift} of $v = 32$ km s⁻¹, strongly at odds with
+the blueshift of $v = 149$ km s⁻¹ found in this work. We note that Na
+\textsc{i} has a very low ionization potential of only $\sim 5$ eV,
+meaning that these atoms may well only be present in fractions of the
+gas traced by Si \textsc{ii}. This is in agreement with the finding of
+\citet{Sandberg2013} that NaD, despite being a strong transition, shows
+absorption of only $\sim 95\%$ of continuum level. They also find that
+NaD is mostly found in small, optically thick clouds, further supporting
+this interpretation.
 
-\section{Discussion and conclusions}\label{discussion-and-conclusions}
+Also the absorption feature in the Lyman $\alpha$ profile in the upper
+panel seems to morphologically follow the shape of the metal lines,
+indicating that radiative transfer effects are modest, indicative of a
+fairly low column density of HI. We find a Lyman $\alpha$ peak velocity
+of $v_{\rm peak}^{\mathrm{Ly}\alpha} = 158 \pm 1$ km s⁻¹ w.r.t the
+H$\alpha$-derived systemic velocity found by \citet{Sandberg2013}. This
+velocity, as it is also discussed in \citet{Verhamme2015}, is just
+consistent with their theoretical predictions for a density-bounded,
+low-column density system, albeit on the upper limit of their allowed
+range.
 
-Bla bla bla
+\subsection{Metal and \ion{H}{1} column
+density}\label{metal-and-column-density}
+
+Lyman $\alpha$ escape is mainly governed by gas at or near systemic
+velocity. In the middle panel of fig.~\ref{fig:WithColDens} (a) is shown
+the best-fit column density $N_{\rm Si II}$ for each velocity bin. The
+value at systemic velocity is $\log_{10}(N_{\rm Si II}) = 12.1 \pm 0.2$.
+We adapt the value for local starbursts of log(Si/O) $= -1.59 \pm 0.07$
+from \citet{Garnett1995}, and use this to estimate the column density of
+neutral Hydrogen in front of the light source in the same way is in
+{[}Puschnig et al., submitted to MNRAS{]} as follows. \citet{Guseva2012}
+found a metallicity of Haro 11 C of $12 + \log_{10}(\text{O/H}) = 8.1$.
+With $\log_{10}$ Si/O $= -1.59 \pm 0.07$, this leads to a Si/H ratio in
+the neutral medium of $Si / H = 3.24^{+0.57}_{-0.48} 10^{-6}$, leading
+to a Hydrogen column density of $6.2^{+0.9}_{-1.1} \times 10^{17}$
+cm\textsuperscript{-2}. Since HI gets opaque to ionizing radiation at
+$\log N \sim 17$, this range is not consistent with the low- optical
+depth, density bounded scenario.
+
+However, the pure riddled ionization bounded scenario is easily ruled
+out since the Ly$\alpha$ profile does not have any appreciable component
+at zero velocity. We expect a residual neutral fraction to remain in the
+ionized, inter-clump phase; a fraction which has a column density high
+enough to block Ly$\alpha$ efficiently at line center, but low enough to
+be at least part transparent to LyC radiation. In Puschnig et al.
+(submitted), it was shown for Tololo 1247-232, an object with very
+similar \ion{Si}{2} column densities, that the sensitivity limit for
+\ion{Si}{2} is $\sim 1 \times 10^{11}$ cm\textsuperscript{-2}, which
+with the metallicity for Haro 11 C corresponds to
+$N_{\text{H\textsc{i}}} \sim 3.1 \times 10^{16}$ cm\textsuperscript{-2}.
+This leaves around 2-3 orders of magnitude in $N$, in which the gas has
+no detectable \ion{Si}{2} and is optically thick to Ly$\alpha$ and
+translucent to Lyman Continuum.
+
+This result seems to be consistent with what is found in the Green Pea
+galaxies of \citep{Henry2015} - these galaxies have sometimes very low
+LIS optical depth, which is usually indicative of low covering fractions
+and high porosity of the neytral medium - and yet they find covering
+fractions of near unity of \ion{H}{1} from Lyman $\beta$ absorption,
+indicating column densities of $N \gtrsim 10^{16}$. Like in the case of
+Haro 11, this indicates that a non-negligible neutral component must be
+present in the ionized phase, although it may very well be of such low
+densities and metallicity that metal absorption from this medium is
+undetectable.
+
+The column densities we derive for \ion{Si}{2} in this work are
+generally between $12.0 \lesssim \log N \lesssim 12.5$, column densities
+around which the transitions involved become optically thick: For
+$\lambda \lambda 1260, 1526 \text{and} 1304$, $tau$ becomes 1 at
+$\log N \sim 11.3, 12.2$ and $12.5$, respectively. In the line wings,
+and in particular at $v_0$, only $\lambda 1260$ seems to be optically
+thick, and it seems the column densities arrived at can be trusted. But
+at line center, around $v\sim v_{int}$, the column densities found are
+so close to the limit that they are most likely to be interpreted as
+lower limits. There might also be systematics in the determination of
+the continuum around the lines which may lead to the lines at
+$\lambda \lambda 1304, 1526$ to be falsely seen as shallower than
+$\lambda 1260$, meaning that all computed column densities are really
+lower limits rather than actual values. The confidence intervals in fig.
+\ref{fig:WithColDens} do \emph{not} reflect this possible saturation,
+but only the formal errors from the best approximation to the residual
+intensity, they do not include systematics.
+
+If the computed column densities are in fact lower limits, this means
+the inferred \ion{H}{1} column densities are also lower limits. This
+would rule out the marginal possibility that the clumps themselves are
+partly transparent to Lyman Continuum, and strengthen the riddled,
+ionization-bounded medium scenario that the ISM on the line of sight to
+Haro 11 C consists of dense, neutral clumps with an ionized interclump
+medium containing a dilute neutral component.
+
+\subsection{Neutral gas metallicity}\label{neutral-gas-metallicity}
+
+The exact value of the metallicity is however uncertain. The values
+found from nebular recombination lines by \citet{Guseva2012} are
+measured mainly in the central HII regions around the clusters; and
+differ by 0.2 dex between knot B and C. The neutral, outflowing gas
+could be mixed, or have an unseen LOS distance component larger than the
+knot separation, drawing into question which is the better value to
+assume for this gas. We base our conclusions on the value found for knot
+C, but note that using the metallicity of $12 + \log (O/H) = 8.3$ found
+for knot B by \citet{Guseva2012}, the inferred H \textsc{i} column
+densities are $3.9 \pm 0.6 \times 10^{17}$ cm\textsuperscript{-2}.
+However, the question of the exact metallicity of the outflowing gas is
+complicated. Gas closer to the star forming regions is expected to be
+more strongly enriched than gas further away, which would imply that the
+HI column density is \emph{larger} than inferred from \ion{Si}{2} above.
+To this can be added the further complication stemming from the merger
+event that the galaxy is currently undergoing, which may have mixed gas
+of different metal contents thoroughly. In any case, though, we would
+expect the regions nearest to the starbursts to generally have higher
+metallicity than the surrounding cool gas, such that the HI column
+density inferred above is more likely to be underestimated than
+overestimated.
+
+\subsection{Radiative transfer effects}\label{sec:rt}
+
+The conclusions drawn by the AOD method rest on the assumption that the
+observed lines are close to being pure absorption lines, with
+redistribution of photons due to radiative transfer effects being
+modest. Modelling work by e.g. \citet{Prochaska2011} and
+\citet{Scarlata2015} has shown that in certain conditions, radiative
+transfer can re-fill absorption features in a way that can make an
+isotropic, optically thin mimic the observational fingerprints of a
+system of optically thick clumps. We therefore need to investigate
+whether our conclusions could be generated by such effects.
+
+\begin{figure}
+\centering
+\includegraphics[width=3.500in]{../Figs/1260-fit-fluor.pdf}
+\caption{\ion{Si}{2} $\lambda 1260$ and its fluorescent line at
+$\lambda 1265$, with the observed data shown in blue. The orange curve
+shows a fit to the fluorescent emission, and in gray is shown the
+worst-case absorption profile corrected for radiative transfer effects
+re-filling the absorption trough.}\label{fig:rt}
+\end{figure}
+
+Because the ground level in \ion{Si}{2} is a doublet with a short-lived
+upper level, each of the Silicon lines included in the analysis has a
+fluorescent emission line with practically no absorption component. The
+fluorescent line can be used to constrain the possible effect of
+radiative infilling of the absorption trough. If each photon in the
+fluorescent transition on average has scattered once in the neutral
+medium, the ratio of emission in this line and re-filling of the
+resonant absorption line is simply that of their Einstein coefficients
+$A_{ki}$. For each subsequent scattering, more photons escape directly
+through the fluorescent channel, and the infilling of the absorption
+line further suppressed.
+
+In fig.~\ref{fig:rt}, the observed line profile is shown in blue, along
+with the best fit to \ion{Si}{2}$^*$ shown in orange. Since the
+fluorescent and resonant reemission originate in the same environments,
+the shape of the resonant reemission profile can be completely
+determined from the shape and center of the fluorescent line and the
+assumption of one scattering. It is therefore simple to construct this
+theoretical reemission line, subtract it from the observed absorption
+line and find a lower limit for the depth of the pure absorption line
+without reemission; this model line sis shown in gray in the figure. It
+is readily seen that the difference between theoretical and observed
+line is so small that it cannot affect our conclusions about the
+covering factors and column densities of the neutral gas significantly.
+
+We have not performed similar measurements for the lines at
+$\lambda \lambda 1304, 1526$, but note that if significant refilling is
+present here, this would mean the column densities had actually been
+underestimated in our analysis, which would strengthen the conclusions
+of a clumpy medium optically thick in \ion{Si}{2} $1260$, but part
+transparent in the much weaker other lines.
+
+\subsection{Conclusion}\label{conclusion}
+
+In this work, we have re-analyzed an archival FUV HST-COS spectrum to
+investigate the kinematics and geometry of both the hot, ionized and
+cold, neutral ISM along the LOS to the main star forming knot. We have
+used the Apparent Optical Depth method to compute column densities and
+velocity-binned covering fractions of the gas and compared these results
+to the extreme cases of either an optically thin, density bounded
+neutral medium, or a riddled, optically thick, ionization bounded
+neutral medium. Assuming that the Lyman Continuum emission previously
+observed from this galaxy indeed does originate from knot C, we find
+that the observations are not compatible with the latter case, since the
+characteristic, bright Lyman-$\alpha$ emission spike at line center is
+absent in this spectrum. Furthermore, the observations are not
+consistent with an optically thin, density bounded neutral medium.
+
+We confirm previous authors concluding that the medium is highly ionized
+with clumps of neutral gas of low velocity-binned covering fraction,
+increasing the probability of finding direct sight lines between these.
+The clumps have low HI column densities in the range
+$N_{\rm HI} = 6.2^{+0.9}_{-1.1} \times 10^{17}$ given the metallicity of
+the background HII region, which is likely a slight underestimate of
+$N_{\rm HI}$. There is a possibility that the found column densities are
+in fact lower limits, since the found \ion{Si}{2} column densities are
+close to the limit where this ion becomes optically thick. We therefore
+conclude that the leaked ionizing photons, if originating from this
+cluster, most likely escaped via sight lines through the ionized medium,
+which must thus contain a neutral gas column density
+$5 \times 10^{13} \leq N_{\rm HI}^{\rm HIS} \leq 3 \times 10^{16}$. This
+range is bounded downwards by the value at which HI becomes transparent
+to Lyman-$\alpha$, and upwards by the sensitivity to \ion{Si}{2}.
+
+\section*{Acknowledgements}\label{acknowledgements}
+\addcontentsline{toc}{section}{Acknowledgements}
+
+G.Ö. is a Royal Swedish Academy of Science research fellow (supported by
+a grant from the Knut \& Alice Wallenbergs foundation). M.H.
+acknowledges the support of the Swedish Research Council,
+Vetenskapsrådet, and the Swedish National Space Board (SNSB) and is
+Academy Fellow of the Knut and Alice Wallenberg Foundation. This project
+has made extensive use of the Python-based packages Numpy \citep{Numpy},
+SciPy \citep{SciPy}, Matplotlib \citep{Matplotlib}, Pandas
+\citep{Pandas}, LMfit \citep{lmfit2014}, and Astropy
+\citep{Astropy2013}.
 

### 2016-11-16 Code/COS_Vignetting_Throughput.py

@@ -1,0 +1,9 @@
+#!/usr/bin/env python
+# encoding: utf-8
+
+import numpy as np
+
+tps = np.array([[1., 0.9999, 0.9282, 0.7679, 0.6039, 0.3096],
+                [1., 0.9647, 0.9180, 0.7786, 0.6243, 0.3640],
+                [1., 0.9899, 0.9559, 0.7952, 0.6231, 0.3410],
+                [1., 0.9791, 0.8735, 0.7658, 0.5875, 0.3154]])

### 2016-11-16 Code/DynVel.py

@@ -65,9 +65,6 @@ def vel_bin_size(indict):
         width = velocities[i + 1] - velocities[i]
         velbinlist.append(width)
     velbarr = sp.array(velbinlist)
-   # print velbarr.ptp()
-   # print velbarr.mean()
-   # print vb1
     return velbarr.mean()
 
 
@@ -96,16 +93,10 @@ def dynvel(indict, ranges=None, species='Average LIS',
                      and piece of right continuum, 6 clicks in total''',
                      (.5, .9), xycoords='axes fraction',
                      ha='center')
-        #cid = fig.canvas.mpl_connect('button_press_event', onclick)
-        #plt.show()
         exes = plt.ginput(6)
         plt.close()
-        #import pdb; pdb.set_trace() ### XXX BREAKPOINT
-        #plt.show()
-        #print exes
         leftexes = np.asarray(exes[0:2])[:, 0]
         riteexes = np.asarray(exes[4:6])[:, 0]
-        #print 'riteexes', riteexes
         lineexes = np.asarray(exes[2:4])[:, 0]
         exesarr = np.asarray(exes)
     else:
@@ -117,18 +108,9 @@ def dynvel(indict, ranges=None, species='Average LIS',
         except:
             print('Could not make sense of given ranges, exiting')
             return
-    # print leftexes
-    # print lineexes
-    # print riteexes
-    # print leftexes.min(), leftexes.max(), wl.shape
-    #normalise = np.where(((wl >= leftexes.min()) & (wl <= leftexes.max())) |
-    #                    ((wl >= riteexes.min()) & (wl <= riteexes.max())))
-    #norm = np.mean(spedata[normalise])
     spedata_orig = spedata.copy()
     spedata = spedata[indict.Velocity.between(lineexes[0], lineexes[1])]
 
-    #print spedata
-    #line = spedata[(wl >= lineexes.min()) & (wl <= lineexes.max())]
     line = spedata[indict.Velocity.between(lineexes[0], lineexes[1])]
     lidx = sp.where((wl >= lineexes.min()) & (wl <= lineexes.max()))
     liwl = wl[(wl >= lineexes.min()) & (wl <= lineexes.max())]
@@ -137,12 +119,6 @@ def dynvel(indict, ranges=None, species='Average LIS',
     norm = 1.      # Because that is what I did when finding robust lower limits
[…]

### 2016-11-16 Code/LyaCFfig.py

@@ -17,6 +17,13 @@ cf_color2 = cosp.paircolors[7]
 wdata = pd.read_pickle('../Products/dfdict.pickle')[1]
 vdata = pd.read_pickle('../Products/vflis.pickle')[1]
 hdata = pd.read_pickle('../Products/vfhis.pickle')[1]
+
+## OBS! Because we know the result of the AOD for Haro 11 COS,
+## we set c1260 as proxy for covfrac.
+vdata.MeanProfile = vdata.Si_II_1260_Flam
+vdata.MeanErrors = vdata.Si_II_1260_Stddev
+## End of dirty hardcoding. FIXME
+
 z = 0.020434136
 # print wdata.head()
 # print vdata.head()

### 2016-11-16 Code/Resol.py

@@ -1,0 +1,215 @@
+#!/usr/bin/env python
+
+import numpy as np
+import matplotlib.pyplot as plt
+from COS_Vignetting_Throughput import tps
+import scipy as sp
+import mpl_tricks as mp
+from scipy.ndimage import rotate
+from astropy.io import fits
+import astropy.units as u
+import scipy.interpolate as ipl
+import pyregion as pr
+
+Cuts = {1: None}
+
+UVdata, UVhead = fits.getdata('../ImageData/haro_lyac.fits', header=True)
+centerpix = [876.01019, 983.80147]
+imangle = (np.arctan(1.0523680571667E-7/6.9436464044738E-6) * u.rad).to(u.deg)
+COSangle = 101.39 * u.deg
+totangle = imangle + COSangle
+print imangle, COSangle, totangle
+pixradius = 50.
+
+def circle_mask(image, cent_pix, radius):
+    ''' Given an array, a center and a radius,
+    generates a Bool array of the same dimension as input,
+    which is True inside the radius and False outside.
+
+    Parameters:
+    -----------
+
+    image: numpy.ndarray
+        Two-dimensional numpy array, the entries of which are
+        interpreted as image pixels.
+
+    cent_pix: tuple
+        (y, x) coordinates (in numpy column-major order) of the
+        circle center.
+
+    radius:  float
+        radius in pixels of circle.
+
+    Returns:
+    --------
+
+    circ_mask: numpy.ndarray
+        Numpy array of datatype bool.
+    '''
+    centx, centy = cent_pix[1], cent_pix[0]
+    x, y = np.arange(image.shape[1]), np.arange(image.shape[0])
+    XX, YY = np.meshgrid(x, y)
+    circ_mask = np.zeros_like(XX).astype(bool)
+    circ_mask[np.sqrt((XX - centx) ** 2 + (YY - centy) ** 2) < radius] = True
+    return circ_mask
+
+
+def vignetting(image, cent_pix, radius):
+    '''Emulates vignetting in the COS aperture'''
+    arcsecbase = np.linspace(0, 1.25, 6)
+    centx, centy = cent_pix[1], cent_pix[0]
+    x, y = np.arange(image.shape[1]), np.arange(image.shape[0])
+    XX, YY = np.meshgrid(x, y)
+    vignette = np.zeros_like(image)
[…]

### 2016-11-16 Code/est_resol.py

@@ -1,0 +1,215 @@
+#!/usr/bin/env python
+# encoding: utf-8
+
+import matplotlib.pyplot as plt
+import numpy as np
+import scipy as sp
+import mpl_tricks as mp
+from COS_Vignetting_Throughput import tps
+from scipy.ndimage import rotate
+import scipy.interpolate as ipl
+from astropy.io import fits
+
+plt.rc('text', usetex=True)
+plt.rc('font', **{'family':'serif', 'serif':['Computer Modern Roman'],
+                  'sans-serif':'Helvetica'})
+
+mirrored = [2, 6, 7, 12, 13, 14]
+
+acqfiles = {1:  '../Data/lc3401luq_rawacq.fits',}
+
+Apertures = {
+    1:  [432, 529, 31.25]}
+
+Cuts = {
+   # 1:  [300, 700],
+   # 2:  [150, 550],
+    1:  None,
+   #  4:  None,
+   #  5:  [300, 500],
+   #  6:  [100, 600],
+   #  7:  [400, 600],
+   #  8:  None,
+   #  9:  None,
+   #  10: [80, 600],
+   #  11: None,
+   #  12: [320,  450],
+   #  13: [250,  500],
+   #  14: [350,  430]
+}
+
+
+def find_angle(larsno):
+    ''' Finds the COS y-axis rotation from in degrees E of N.
+    '''
+    filename = '../Data/haro11_stack.coarse.ascii'
+    for line in open(filename):
+        if line.startswith('#ORIENT'):
+            angle = float(line.split()[2])
+            print angle
+    return angle
+
+
+def circle_mask(image, cent_pix, radius):
+    ''' Given an array, a center and a radius,
+    generates a Bool array of the same dimension as input,
+    which is True inside the radius and False outside.
+
+    Parameters:
+    -----------
+
+    image: numpy.ndarray
+        Two-dimensional numpy array, the entries of which are
+        interpreted as image pixels.
+
+    cent_pix: tuple
+        (y, x) coordinates (in numpy column-major order) of the
+        circle center.
+
+    radius:  float
+        radius in pixels of circle.
+
+    Returns:
+    --------
+
+    circ_mask: numpy.ndarray
+        Numpy array of datatype bool.
+    '''
+    centx, centy = cent_pix[1], cent_pix[0]
+    x, y = np.arange(image.shape[1]), np.arange(image.shape[0])
[…]

### 2016-11-22 Paper/Paper.tex
Almost all comments implemented
Also corrected method for inferring effective HI column density for Lyman Continuum; this should be integrated over all velocities for Lyman Continuum but only be taken around line center for Ly$\alpha$

@@
 \begin{abstract}
-Star forming galaxies are believed to be the main source of ionizing
+Star forming galaxies are believed to be a major source of ionizing
 radiation responsible for reionizing the early Universe. Direct
@@
 ionized medium of
-$5 \times 10^{13} \leq N_{\rm HI} \leq 3 \times 10^{16}$; high enough to
+$5 \times 10^{13} \leq N_{\rm HI} \leq 4 \times 10^{15}$; high enough to
 be optically thick to Lyman-$\alpha$, but low enough to be at least
-partly transparent to Lyman-continuum and undetectable in Si\textsc{ii}.
+partly transparent to Lyman-continuum and undetected in Si\textsc{ii}.
 \end{abstract}
@@
 intensity is given as
-
 %
-\begin{equation*}
+\begin{equation}
+\label{eq:II0}
 \frac{I}{I_0} = 1 - f_C (1 - e^{-\tau}),
-\end{equation*}
+\end{equation}
 %
-
  with the optical depth $\tau$ given as:
-
 %
-\begin{equation*}
+\begin{equation}
+\label{eq:tau}
 \tau = f\lambda \frac{\pi e^2}{m_e c} N 
        = f\lambda \frac{N}{3.768 \times 10^{14}}
-\end{equation*}
+\end{equation}
 %
-
-Here, $f$ is the oscillator strength of a given transition, $\lambda$ is
-its rest frame wavelength in Å, $N = N(v)$ is the column density of the
-relevant ion \emph{within the given velocity bin}, and $f_{C}$ is the
-covering fraction of neutral gas \emph{moving at the given velocity}.
-When multiple absorption lines are present which arise from the same
-ground state; the population of this state is the same for all
+ Here, $f$ is the oscillator strength of a given transition, $\lambda$
+is its rest frame wavelength in Å, $N = N(v)$ is the column density of
+the relevant ion \emph{within the given velocity bin}, and $f_{C}$ is
+the covering fraction of neutral gas \emph{moving at the given
+velocity}. When multiple absorption lines are present which arise from
+the same ground state; the population of this state is the same for all
 transitions, and their relative strengths are governed simply by their
@@
 
+\section{Discussion and conclusions}\label{discussion-and-conclusions}
+
+\subsection{Lyman-$\alpha$ and ISM absorption
+profiles}\label{sec:LISLya}
+
+In fig.~\ref{fig:HisLisLya}, we show the neutral and ionized absorption
+profile as in fig.~\ref{fig:WithColDens} together with the profile of
+Ly$\alpha$ on a common velocity scale.
+
+\begin{figure}
+\centering
+\includegraphics[width=3.500in]{../Figs/LyACoverfracs.pdf}
+\caption{\textbf{Upper panel}: Ly$\alpha$ profile of Haro 11 C, in
+approximate units of the surrounding continuum level. Full line is the
+measured values smoothed by a 5 px. flat kernel; surrounding shading
+encloses the $\pm 1 \sigma$ error band (mostly comparable in width to
+the line width). \textbf{Middle panel}: Black steps show the averaged,
+LIS line profile, smoothed by a 5px kernel. Surrounding gray shading
+denotes the $\pm 1 \sigma$ confidence band. \textbf{Lower panel}: Same
+as middle panel, but for the \ion{Si}{4} transitions.
+}\label{fig:HisLisLya}
+\end{figure}
+
+The picture is what we would expect from a Lyman Continuum leaker: weak
+neutral and strong ionized absorption profiles, the latter almost
+everywhere consistent with full coverage, reveal a highly ionized medium
+in front of the central cluster. This is also in good agreement with the
+findings of \citet{Pardy2016arXiv}, who conclude that the galaxy has
+about twice as much ionized as neutral gas. In addition to this, it is
+interesting to note the close similarity in shape between the
+\ion{Si}{2} and \ion{Si}{4} line profiles, indicating that they likely
+represent two different phases in the same higher density regions. These
+regions will likely be ionized on the side facing the central cluster,
+being photoionized by its hot, massive stars. This also implies that the
+nebular emission outflow found in {[}Rivera-Thorsen et al, submitted{]}
+at least partially traces the same gas as the \ion{Si}{4} absorption
+here and, by extension, also the neutral medium. Looking at
+fig.~\ref{fig:SingleLines}, we see that maximum absorption and thus the
+largest amount of gas in a single velocity bin for both phases is found
+at around $v \approx -50$ km s⁻¹, where also a component is found in
+{[}Rivera-Thorsen et al., submitted{]}. The outflow velocity
+$v_{\text{int}}$ is at 149 ± 7 km s⁻¹, fully consistent with the
+findings of \citet{Heckman2015} and \citet{Alexandroff2015}.
+Interestingly, \citet{Sandberg2013} found from the neutral Sodium
+resonance absorption doublet $\lambda \lambda 5889.95,5895.92$ (NaD) an
+overall, weak \emph{redshift} of $v = 32$ km s⁻¹. From
+e.g.~fig.~\ref{fig:HisLisLya}, it is evident that while neutral gas
+\emph{is} present at these velocities, the velocity is at odds with the
+integrated velocity of $v = -149$ km s⁻¹ found in this work. We note
+that Na \textsc{i} has a very low ionization potential of only $\sim 5$
+eV, meaning that these atoms may well only be present in the densest
+and/or dustiest regions, in which Sodium is shielded from ionization.
+This is in agreement with the finding of \citet{Sandberg2013} that NaD,
+despite being a strong transition, shows absorption of only $\sim 95\%$
+of continuum level and is mostly found in small, optically thick clouds.
+This suggests that the NaD is tracing only the densest and/or dustiest
+regions which are more slowly accelerated by star formation feedback
+than the surrounding, more dilute medium. In fig.~\ref{fig:apert}, dusty
+regions in the aperture are apparent E and W of knot C, and in the
+better resolution of fig. 1 in \citet{Adamo2010}, these regions seem
+like they might be connected by a narrow dust lane partially covering
+the background source. We speculate that the NaD absorption of
+\citet{Sandberg2013} might be associated with this.
+
+Also the absorption feature in the Lyman $\alpha$ profile in the upper
+panel seems to morphologically follow the shape of the metal lines,
+indicating that radiative transfer effects are modest, indicative of a
+fairly low column density of HI around line center. We find a Lyman
+$\alpha$ peak velocity of $v_{\rm peak}^{\mathrm{Ly}\alpha} = 158 \pm 1$
+km s⁻¹ w.r.t the systemic velocity found by \citet{Sandberg2013},
+derived from nebular emission lines in the region around knot C. This
+velocity, as it is also discussed in \citet{Verhamme2015}, is just
+consistent with their theoretical predictions for a density-bounded,
+low-column density system, albeit on the upper limit of their allowed
+range.
+
+\subsection{Metal and \ion{H}{1} column
+density}\label{metal-and-column-density}
+
+Lyman $\alpha$ escape is mainly governed by gas at or near systemic
+velocity. In the middle panel of fig.~\ref{fig:WithColDens} (a) is shown
+the best-fit column density $N_{\rm Si II}$ for each velocity bin. The
+value at systemic velocity is $\log_{10}(N_{\rm Si II}) = 12.1 \pm 0.2$.
+We adapt the value for local starbursts of log(Si/O) $= -1.59 \pm 0.07$
+from \citet{Garnett1995}, and use this to estimate the column density of
+neutral Hydrogen in front of the light source in the same way is in
+{[}Puschnig et al., submitted to MNRAS{]} as follows. \citet{Guseva2012}
+found a metallicity of Haro 11 C of $12 + \log_{10}(\text{O/H}) = 8.1$.
+With $\log_{10}$ Si/O $= -1.59 \pm 0.07$, this leads to a Si/H ratio in
+the neutral medium of Si / H $= 3.24^{+0.57}_{-0.48} 10^{-6}$, leading
+to a Hydrogen column density of $6.2^{+0.9}_{-1.1} \times 10^{17}$
+cm\textsuperscript{-2}. Since HI gets opaque to ionizing radiation at
+$\log N \sim 17.2$ \citep{Verhamme2015}, this range is not consistent
+with the low- optical depth, density bounded scenario. Furthermore;
+while Ly$\alpha$ radiative transfer is dominated by gas of $v \sim v_0$,
+Lyman continuum is sensitive to \ion{H}{1} at \emph{all} velocities.
+Integrating the computed column densities over $-450$ km s⁻¹ $< v < 150$
+km s⁻¹, the velocity range over which the column densities can be
+reasonably well determined (and removing the unphysically high value in
+the bin at $v \approx 222$ km s⁻¹), yields a conservative estimate of
+$\log N_{\rm Si II} \approx 19.4$, corresponding to more than 150
+optical depths in Lyman Continuum, strongly incompatible with an
+optically thin, density-bounded scenario.
+
+However, the pure riddled ionization bounded scenario is easily ruled
+out since the Ly$\alpha$ profile does not have any appreciable emission
+component at zero velocity. We therefore expect a residual neutral
+fraction to remain in the ionized phase; a fraction which has a column
+density high enough to block Ly$\alpha$ efficiently at line center, but
+low enough to be at least part transparent to Lyman Continuum radiation
+and undetected in \ion{Si}{2}.
+
+We can estimate the lowest detectable $N_{\rm Si II}$ by noting that the
+relative errors for the \ion{Si}{2} lines in our spectrum are
+$\sim 0.05$. Assuming a covering fraction of unity for the dilute
+neutral component, and adopting the oscillator strength of the strongest
+of the \ion{Si}{2} transitions, $f\lambda_{1260 \AA} = 1486.8$, we find
+in the limit that $I/I_0 = e^{-\tau} = 0.95$, and eq.~\ref{eq:tau}
+becomes:
+%
+\begin{equation}
+\label{eq:silim}
+N_{\rm Si II}^{\rm min} = -\log_{e}(0.95) \frac{3.768 \times 10^{14}}{f\lambda} 
+    = 10^{10.1} \text{cm}^{-2},
+\end{equation}
+%
+ which with the adopted metallicity for Haro 11 C corresponds to a
+minimum Hydrogen column density of
+$N_{\rm HI}^{\rm min} \sim 4.0 \times 10^{15}$ cm⁻². This leaves around
+2 orders of magnitude in $N_{\rm H I}$, in which the gas is not detected
+in \ion{Si}{2} and is optically thick to Ly$\alpha$ while translucent to
+Lyman Continuum. If we require the gas to be detected in at least two of
+the lines included in this analysis, the limiting hydrogen column
+density becomes $N_{\rm HI}^{\rm min} \sim 4.9 \times 10^{16}$ cm⁻²,
+adding another order of magnitude to the allowed range, but we adopt the
+lower value as a conservative estimate.
+
+The existence of a diffuse neutral component being present in the
+ionized medium seems consistent with what is found in the Green Pea
+galaxies of \citep{Henry2015} - these galaxies have sometimes very low
+LIS optical depth, which is usually indicative of low covering fractions
+and high porosity of the neytral medium - and yet they find covering
+fractions of near unity of \ion{H}{1} from Lyman $\beta$ absorption,
+indicating column densities of $N \gtrsim 10^{16}$. Like in the case of
+Haro 11, this indicates that a non-negligible neutral component must be
+present in the ionized phase, although it may very well be of such low
+densities and metallicity that metal absorption from this medium is
+undetectable.
+
+The column densities we derive for \ion{Si}{2} in this work are
+generally between $12.0 \lesssim \log N \lesssim 12.5$, column densities
+around which the transitions involved become optically thick: For
+$\lambda \lambda 1260, 1526 \text{ and } 1304$, $\tau$ becomes 1 at
+$\log N \sim 11.3, 12.2$ and $12.5$, respectively. Off the regions of
+strongest absorption, and in particular at $v_0$, only $\lambda 1260$
+seems to be optically thick, and it seems the column densities arrived
+at can be trusted. But at line center, around $v\sim v_{int}$, the
+column densities found are so close to the limit that they are most
+likely to be interpreted as lower limits. There might also be
+systematics in the determination of the continuum around the lines which
+may lead to the lines at $\lambda \lambda 1304, 1526$ to be falsely seen
+as shallower than $\lambda 1260$, meaning that all computed column
+densities are really lower limits rather than actual values. The
+confidence intervals in fig. \ref{fig:WithColDens} do \emph{not} reflect
+this possible saturation, but only the formal errors from the best
+approximation to the residual intensity, they do not include
+systematics.
+
+If the computed column densities are in fact lower limits, this means
+the inferred \ion{H}{1} column densities are also lower limits. This
+would strengthen the modified riddled, ionization-bounded medium
+scenario that the ISM on the line of sight to Haro 11 C consists of
+dense, neutral clumps with an ionized interclump medium containing a
+dilute neutral component.
+
+\subsection{Neutral gas metallicity}\label{neutral-gas-metallicity}
+
+The exact value of the metallicity is however uncertain. The values
+found from nebular recombination lines by \citet{Guseva2012} are
+measured mainly in the central HII regions around the clusters; and
+differ by 0.2 dex between knot B and C. The neutral, outflowing gas
+could be mixed, or have an unseen LOS distance component larger than the
+knot separation, drawing into question which is the better value to
+assume for this gas. We base our conclusions on the value found for knot
+C, but note that using the metallicity of $12 + \log (O/H) = 8.3$ found
+for knot B by \citet{Guseva2012}, the inferred H \textsc{i} column
+densities are $3.9 \pm 0.6 \times 10^{17}$ cm\textsuperscript{-2}.
+However, the question of the exact metallicity of the outflowing gas is
+complicated. Gas closer to the star forming regions is expected to be
+more strongly enriched than gas further away, which would imply that the
+HI column density is \emph{larger} than inferred from \ion{Si}{2} above.
+To this can be added the further complication stemming from the merger
+event that the galaxy is currently undergoing, which may have mixed gas
+of different metal contents. In any case, though, we would expect the
+regions nearest to the starbursts to generally have higher metallicity
+than the surrounding cool gas, such that the HI column density inferred
+above is more likely to be underestimated than overestimated.
+
+\subsection{Radiative transfer effects}\label{sec:rt}
+
+The conclusions drawn by the AOD method rest on the assumption that the
+observed lines are close to being pure absorption lines, with
+redistribution of photons due to radiative transfer effects being
+modest. Modelling work by e.g. \citet{Prochaska2011} and
+\citet{Scarlata2015} has shown that in certain conditions, radiative
+transfer can re-fill absorption features in a way that can make an
+isotropic, optically thin mimic the observational fingerprints of a
+system of optically thick clumps. We therefore need to investigate
+whether our conclusions could be generated by such effects.
+
+\begin{figure}
+\centering
+\includegraphics[width=3.500in]{../Figs/1260-fit-fluor.pdf}
+\caption{\ion{Si}{2} $\lambda 1260$ and its fluorescent line at
+$\lambda 1265$, with the observed data shown in blue. The orange curve
+shows a fit to the fluorescent emission, and in gray is shown the
+worst-case absorption profile corrected for radiative transfer effects
+re-filling the absorption trough.}\label{fig:rt}
+\end{figure}
+
+Because the ground level in \ion{Si}{2} is a doublet with a short-lived
+upper level, each of the Silicon lines included in the analysis has a
+fluorescent emission line with practically no absorption component. The
+fluorescent line can be used to constrain the possible effect of
+radiative infilling of the absorption trough. If each photon in the
+fluorescent transition on average has scattered once in the neutral
+medium, the ratio of emission in this line and re-filling of the
+resonant absorption line is simply that of their Einstein coefficients
+$A_{ki}$. For each subsequent scattering, more photons escape directly
+through the fluorescent channel, and the infilling of the absorption
+line further suppressed.
+
+In fig.~\ref{fig:rt}, the observed line profile is shown in blue, along
+with the best fit to \ion{Si}{2}$^*$ shown in orange. Since the
+fluorescent and resonant reemission originate in the same environments,
+the shape of the resonant reemission profile can be completely
+determined from the shape and center of the fluorescent line and the
+assumption of one scattering. It is therefore simple to construct this
+theoretical reemission line, subtract it from the observed absorption
+line and find a lower limit for the depth of the pure absorption line
+without reemission; this model line sis shown in gray in the figure. It
+is readily seen that the difference between theoretical and observed
+line is so small that it cannot affect our conclusions about the
+covering factors and column densities of the neutral gas significantly.
+
+We have not performed similar measurements for the lines at
+$\lambda \lambda 1304, 1526$, but note that if significant refilling is
+present here, this would mean the column densities had actually been
+underestimated in our analysis, which would strengthen the conclusions
+of a clumpy medium optically thick in \ion{Si}{2} $1260$, but part
+transparent in the much weaker other lines.
+
 \subsection{\ion{C}{2} $\lambda 1334$
@@
 we observe while still being compatible with the ISM being optically
-thick in $\lambda 1260$.
-
-\section{Discussion and conclusions}\label{discussion-and-conclusions}
-
-\subsection{Lyman-$\alpha$ and ISM absorption
-profiles}\label{sec:LISLya}
-
-In fig.~\ref{fig:HisLisLya}, we show the neutral and ionized absorption
-profile as in fig.~\ref{fig:WithColDens} together with the profile of
-Ly$\alpha$ on a common velocity scale.
-
-\begin{figure}
-\centering
-\includegraphics[width=3.500in]{../Figs/LyACoverfracs.pdf}
-\caption{\textbf{Upper panel}: Ly$\alpha$ profile of Haro 11 C, in
-approximate units of the surrounding continuum level. Full line is the
-measured values smoothed by a 5 px. flat kernel; surrounding shading
-encloses the $\pm 1 \sigma$ error band. \textbf{Middle panel}: Black
-steps show the averaged, LIS line profile, smoothed by a 5px kernel.
-Surrounding gray shading denotes the $\pm 1 \sigma$ confidence band.
-\textbf{Lower panel}: Same as middle panel, but for the \ion{Si}{4}
-transitions. }\label{fig:HisLisLya}
-\end{figure}
-
-The picture is what we would expect from a Lyman Continuum leaker: weak
-neutral and strong ionized absorption profiles, the latter almost
-everywhere consistent with full coverage, reveal a highly ionized medium
-in front of the central cluster. This is also in good agreement with the
-findings of Pardy et al. (submitted), who conclude that the galaxy has
-about twice as much ionized as neutral gas. In addition to this, it is
-interesting to note the close similarity in shape between the
-\ion{Si}{2} and \ion{Si}{4} line profiles, indicating that they likely
-originate in the same higher density regions. These regions will likely
-be ionized on the side facing the central cluster, being photoionized by
-its hot, massive stars. This also implies that the nebular emission
-outflow found in {[}Rivera-Thorsen et al, submitted{]} at least
-partially traces the same gas as the \ion{Si}{4} absorption here and, by
-extension, also the neutral medium. Looking at
-fig.~\ref{fig:SingleLines}, we see that maximum absorption and thus the
-largest amount of gas in a single velocity bin for both phases is found
-at around $v \approx -50$ km s⁻¹, where also a component is found in
-{[}Rivera-Thorsen et al., submitted{]}. The outflow velocity
-$v_{\text{int}}$ is at 149 ± 7 km s⁻¹, fully consistent with the
-findings of \citet{Heckman2015} and \citet{Alexandroff2015}.
-Interestingly, \citet{Sandberg2013} found from the neutral Sodium
-resonance absorption doublet $\lambda \lambda 5889.95,5895.92$ (NaD) an
-overall, weak \emph{redshift} of $v = 32$ km s⁻¹, strongly at odds with
-the blueshift of $v = 149$ km s⁻¹ found in this work. We note that Na
-\textsc{i} has a very low ionization potential of only $\sim 5$ eV,
-meaning that these atoms may well only be present in fractions of the
-gas traced by Si \textsc{ii}. This is in agreement with the finding of
-\citet{Sandberg2013} that NaD, despite being a strong transition, shows
-absorption of only $\sim 95\%$ of continuum level. They also find that
-NaD is mostly found in small, optically thick clouds, further supporting
-this interpretation.
-
-Also the absorption feature in the Lyman $\alpha$ profile in the upper
-panel seems to morphologically follow the shape of the metal lines,
-indicating that radiative transfer effects are modest, indicative of a
-fairly low column density of HI. We find a Lyman $\alpha$ peak velocity
-of $v_{\rm peak}^{\mathrm{Ly}\alpha} = 158 \pm 1$ km s⁻¹ w.r.t the
-H$\alpha$-derived systemic velocity found by \citet{Sandberg2013}. This
-velocity, as it is also discussed in \citet{Verhamme2015}, is just
-consistent with their theoretical predictions for a density-bounded,
-low-column density system, albeit on the upper limit of their allowed
-range.
-
-\subsection{Metal and \ion{H}{1} column
-density}\label{metal-and-column-density}
-
-Lyman $\alpha$ escape is mainly governed by gas at or near systemic
-velocity. In the middle panel of fig.~\ref{fig:WithColDens} (a) is shown
-the best-fit column density $N_{\rm Si II}$ for each velocity bin. The
-value at systemic velocity is $\log_{10}(N_{\rm Si II}) = 12.1 \pm 0.2$.
-We adapt the value for local starbursts of log(Si/O) $= -1.59 \pm 0.07$
-from \citet{Garnett1995}, and use this to estimate the column density of
-neutral Hydrogen in front of the light source in the same way is in
-{[}Puschnig et al., submitted to MNRAS{]} as follows. \citet{Guseva2012}
-found a metallicity of Haro 11 C of $12 + \log_{10}(\text{O/H}) = 8.1$.
-With $\log_{10}$ Si/O $= -1.59 \pm 0.07$, this leads to a Si/H ratio in
-the neutral medium of $Si / H = 3.24^{+0.57}_{-0.48} 10^{-6}$, leading
-to a Hydrogen column density of $6.2^{+0.9}_{-1.1} \times 10^{17}$
-cm\textsuperscript{-2}. Since HI gets opaque to ionizing radiation at
-$\log N \sim 17$, this range is not consistent with the low- optical
-depth, density bounded scenario.
-
-However, the pure riddled ionization bounded scenario is easily ruled
-out since the Ly$\alpha$ profile does not have any appreciable component
-at zero velocity. We expect a residual neutral fraction to remain in the
-ionized, inter-clump phase; a fraction which has a column density high
-enough to block Ly$\alpha$ efficiently at line center, but low enough to
-be at least part transparent to LyC radiation. In Puschnig et al.
-(submitted), it was shown for Tololo 1247-232, an object with very
-similar \ion{Si}{2} column densities, that the sensitivity limit for
-\ion{Si}{2} is $\sim 1 \times 10^{11}$ cm\textsuperscript{-2}, which
-with the metallicity for Haro 11 C corresponds to
-$N_{\text{H\textsc{i}}} \sim 3.1 \times 10^{16}$ cm\textsuperscript{-2}.
-This leaves around 2-3 orders of magnitude in $N$, in which the gas has
-no detectable \ion{Si}{2} and is optically thick to Ly$\alpha$ and
-translucent to Lyman Continuum.
-
-This result seems to be consistent with what is found in the Green Pea
-galaxies of \citep{Henry2015} - these galaxies have sometimes very low
-LIS optical depth, which is usually indicative of low covering fractions
-and high porosity of the neytral medium - and yet they find covering
-fractions of near unity of \ion{H}{1} from Lyman $\beta$ absorption,
-indicating column densities of $N \gtrsim 10^{16}$. Like in the case of
-Haro 11, this indicates that a non-negligible neutral component must be
-present in the ionized phase, although it may very well be of such low
-densities and metallicity that metal absorption from this medium is
-undetectable.
-
-The column densities we derive for \ion{Si}{2} in this work are
-generally between $12.0 \lesssim \log N \lesssim 12.5$, column densities
-around which the transitions involved become optically thick: For
-$\lambda \lambda 1260, 1526 \text{and} 1304$, $tau$ becomes 1 at
-$\log N \sim 11.3, 12.2$ and $12.5$, respectively. In the line wings,
-and in particular at $v_0$, only $\lambda 1260$ seems to be optically
-thick, and it seems the column densities arrived at can be trusted. But
-at line center, around $v\sim v_{int}$, the column densities found are
-so close to the limit that they are most likely to be interpreted as
-lower limits. There might also be systematics in the determination of
-the continuum around the lines which may lead to the lines at
-$\lambda \lambda 1304, 1526$ to be falsely seen as shallower than
-$\lambda 1260$, meaning that all computed column densities are really
-lower limits rather than actual values. The confidence intervals in fig.
-\ref{fig:WithColDens} do \emph{not} reflect this possible saturation,
-but only the formal errors from the best approximation to the residual
-intensity, they do not include systematics.
-
-If the computed column densities are in fact lower limits, this means
-the inferred \ion{H}{1} column densities are also lower limits. This
-would rule out the marginal possibility that the clumps themselves are
-partly transparent to Lyman Continuum, and strengthen the riddled,
-ionization-bounded medium scenario that the ISM on the line of sight to
-Haro 11 C consists of dense, neutral clumps with an ionized interclump
-medium containing a dilute neutral component.
-
-\subsection{Neutral gas metallicity}\label{neutral-gas-metallicity}
-
-The exact value of the metallicity is however uncertain. The values
-found from nebular recombination lines by \citet{Guseva2012} are
-measured mainly in the central HII regions around the clusters; and
-differ by 0.2 dex between knot B and C. The neutral, outflowing gas
-could be mixed, or have an unseen LOS distance component larger than the
-knot separation, drawing into question which is the better value to
-assume for this gas. We base our conclusions on the value found for knot
-C, but note that using the metallicity of $12 + \log (O/H) = 8.3$ found
-for knot B by \citet{Guseva2012}, the inferred H \textsc{i} column
-densities are $3.9 \pm 0.6 \times 10^{17}$ cm\textsuperscript{-2}.
-However, the question of the exact metallicity of the outflowing gas is
-complicated. Gas closer to the star forming regions is expected to be
-more strongly enriched than gas further away, which would imply that the
-HI column density is \emph{larger} than inferred from \ion{Si}{2} above.
-To this can be added the further complication stemming from the merger
-event that the galaxy is currently undergoing, which may have mixed gas
-of different metal contents thoroughly. In any case, though, we would
-expect the regions nearest to the starbursts to generally have higher
-metallicity than the surrounding cool gas, such that the HI column
-density inferred above is more likely to be underestimated than
-overestimated.
-
-\subsection{Radiative transfer effects}\label{sec:rt}
-
-The conclusions drawn by the AOD method rest on the assumption that the
-observed lines are close to being pure absorption lines, with
-redistribution of photons due to radiative transfer effects being
-modest. Modelling work by e.g. \citet{Prochaska2011} and
-\citet{Scarlata2015} has shown that in certain conditions, radiative
-transfer can re-fill absorption features in a way that can make an
-isotropic, optically thin mimic the observational fingerprints of a
-system of optically thick clumps. We therefore need to investigate
-whether our conclusions could be generated by such effects.
-
-\begin{figure}
-\centering
-\includegraphics[width=3.500in]{../Figs/1260-fit-fluor.pdf}
-\caption{\ion{Si}{2} $\lambda 1260$ and its fluorescent line at
-$\lambda 1265$, with the observed data shown in blue. The orange curve
-shows a fit to the fluorescent emission, and in gray is shown the
-worst-case absorption profile corrected for radiative transfer effects
-re-filling the absorption trough.}\label{fig:rt}
-\end{figure}
-
-Because the ground level in \ion{Si}{2} is a doublet with a short-lived
-upper level, each of the Silicon lines included in the analysis has a
-fluorescent emission line with practically no absorption component. The
-fluorescent line can be used to constrain the possible effect of
-radiative infilling of the absorption trough. If each photon in the
-fluorescent transition on average has scattered once in the neutral
-medium, the ratio of emission in this line and re-filling of the
-resonant absorption line is simply that of their Einstein coefficients
-$A_{ki}$. For each subsequent scattering, more photons escape directly
-through the fluorescent channel, and the infilling of the absorption
-line further suppressed.
-
-In fig.~\ref{fig:rt}, the observed line profile is shown in blue, along
-with the best fit to \ion{Si}{2}$^*$ shown in orange. Since the
-fluorescent and resonant reemission originate in the same environments,
-the shape of the resonant reemission profile can be completely
-determined from the shape and center of the fluorescent line and the
-assumption of one scattering. It is therefore simple to construct this
-theoretical reemission line, subtract it from the observed absorption
-line and find a lower limit for the depth of the pure absorption line
-without reemission; this model line sis shown in gray in the figure. It
-is readily seen that the difference between theoretical and observed
-line is so small that it cannot affect our conclusions about the
-covering factors and column densities of the neutral gas significantly.
-
-We have not performed similar measurements for the lines at
-$\lambda \lambda 1304, 1526$, but note that if significant refilling is
-present here, this would mean the column densities had actually been
-underestimated in our analysis, which would strengthen the conclusions
-of a clumpy medium optically thick in \ion{Si}{2} $1260$, but part
-transparent in the much weaker other lines.
+thick in \ion{Si}{2} $\lambda 1260$.
 
@@
 with clumps of neutral gas of low velocity-binned covering fraction,
-increasing the probability of finding direct sight lines between these.
-The clumps have low HI column densities in the range
+increasing the probability of finding direct sight lines to the
+background star cluster between these. The clumps have HI column
+densities of gas around $v=0$ in the range
 $N_{\rm HI} = 6.2^{+0.9}_{-1.1} \times 10^{17}$ given the metallicity of
-the background HII region, which is likely a slight underestimate of
-$N_{\rm HI}$. There is a possibility that the found column densities are
-in fact lower limits, since the found \ion{Si}{2} column densities are
-close to the limit where this ion becomes optically thick. We therefore
-conclude that the leaked ionizing photons, if originating from this
-cluster, most likely escaped via sight lines through the ionized medium,
-which must thus contain a neutral gas column density
-$5 \times 10^{13} \leq N_{\rm HI}^{\rm HIS} \leq 3 \times 10^{16}$. This
+the background \ion{H}{2} region, which is likely a slight underestimate
+of $N_{\rm HI}$. A conservative estimate of the \ion{H}{1} column
+density integrated over all velocities is
+$N_{\rm H I}^{\rm tot} \sim 2.5 \times 10^{19}$ cm⁻². There is a
+possibility that the found column densities are in fact lower limits,
+since the found \ion{Si}{2} column densities are close to the limit
+where this ion becomes optically thick. We therefore conclude that the
+leaked ionizing photons, if originating from this cluster, most likely
+escaped via sight lines through the ionized medium, which must thus
+contain a neutral gas column density
+$5 \times 10^{13} \leq N_{\rm HI}^{\rm HIS} \leq 4 \times 10^{15}$. This
 range is bounded downwards by the value at which HI becomes transparent
-to Lyman-$\alpha$, and upwards by the sensitivity to \ion{Si}{2}.
+to Lyman-$\alpha$, and upwards by the sensitivity to \ion{Si}{2} of this
+observation.
 
@@
 
-G.Ö. is a Royal Swedish Academy of Science research fellow (supported by
-a grant from the Knut \& Alice Wallenbergs foundation). M.H.
-acknowledges the support of the Swedish Research Council,
-Vetenskapsrådet, and the Swedish National Space Board (SNSB) and is
-Academy Fellow of the Knut and Alice Wallenberg Foundation. This project
-has made extensive use of the Python-based packages Numpy \citep{Numpy},
-SciPy \citep{SciPy}, Matplotlib \citep{Matplotlib}, Pandas
-\citep{Pandas}, LMfit \citep{lmfit2014}, and Astropy
+GÖ \& MH acknowledge the support of the Swedish Research Council,
+Vetenskapsrådet, and the Swedish National Space Board (SNSB) and M. H.
+is an Academy Fellow of the Knut and Alice Wallenberg Foundation. This
+project has made extensive use of the Python-based packages Numpy
+\citep{Numpy}, SciPy \citep{SciPy}, Matplotlib \citep{Matplotlib},
+Pandas \citep{Pandas}, LMfit \citep{lmfit2014}, and Astropy
 \citep{Astropy2013}.

### 2016-11-22 Paper/makeaastex61.sh

@@ -1,0 +1,9 @@
+scholdoc Paper.md \
+--template=pandoc-aastex61.latex \
+--natbib \
+-t latex -o Paper.tex
+
+pdflatex Paper.tex
+bibtex Paper
+pdflatex Paper.tex
+

### 2016-11-23 ToSubmit/RiveraThorsen.tex
added script to build submission version

--- 2016-11-22 Paper/Paper.tex
@@
 
-\title{Neutral ISM, Lyman-Alpha and Lyman-continuum in nearby starburst Haro 11}
-
 \title{Neutral ISM, Lyman-Alpha and Lyman-continuum in nearby starburst Haro 11
@@
 	            }
-%
+
 \correspondingauthor{T. Emil Rivera-Thorsen}
@@
 \centering
-\includegraphics[width=3.500in]{../Figs/Haroslit.pdf}
+\includegraphics[width=3.500in]{./Haroslit.pdf}
 \caption{Approximate position of the COS aperture, shown on HST imaging
@@
 \centering
-\includegraphics[]{../Figs/FullSpec.pdf}
+\includegraphics[]{./FullSpec.pdf}
 \caption{Overview of the relevant regions of the COS spectrum of Haro 11
@@
 \centering
-\includegraphics[width=1.000\hsize]{../Figs/EffResol.pdf}
+\includegraphics[width=1.000\hsize]{./EffResol.pdf}
 \caption{Effective resolution estimate. \textbf{Upper left}: Haro 11 in
@@
 \centering
-\includegraphics[width=3.500in]{../Figs/HISLISProfiles.pdf}
+\includegraphics[width=3.500in]{./HISLISProfiles.pdf}
 \caption{The \ion{Si}{2} and other LIS (\textbf{upper}) and \ion{Si}{4}
@@
 \centering
-\includegraphics[width=0.800\hsize]{../Figs/AOD-details-example.pdf}
+\includegraphics[width=0.800\hsize]{./AOD-details-example.pdf}
 \caption{Illustration of the AOD computations. \textbf{Upper panel}: the
@@
 \centering
-\subfloat[LIS\label{coldenLIS}]{\includegraphics[width=0.400\hsize]{../Figs/Fc_haro11c_LIS.pdf}}
-\subfloat[\ion{Si}{4}\label{coldenHIS}]{\includegraphics[width=0.400\hsize]{../Figs/Fc_haro11c-SiIV.pdf}}
+\subfloat[LIS\label{coldenLIS}]{\includegraphics[width=0.400\hsize]{./Fc_haro11c_LIS.pdf}}
+\subfloat[\ion{Si}{4}\label{coldenHIS}]{\includegraphics[width=0.400\hsize]{./Fc_haro11c-SiIV.pdf}}
 \caption{\textbf{Upper panels}: Pseudo-reduced $\chi^2$ as described in
@@
 \centering
-\includegraphics[width=3.500in]{../Figs/LyACoverfracs.pdf}
+\includegraphics[width=3.500in]{./LyACoverfracs.pdf}
 \caption{\textbf{Upper panel}: Ly$\alpha$ profile of Haro 11 C, in
@@
 $\log N \sim 17.2$ \citep{Verhamme2015}, this range is not consistent
-with the low- optical depth, density bounded scenario. Furthermore;
-while Ly$\alpha$ radiative transfer is dominated by gas of $v \sim v_0$,
-Lyman continuum is sensitive to \ion{H}{1} at \emph{all} velocities.
-Integrating the computed column densities over $-450$ km s⁻¹ $< v < 150$
-km s⁻¹, the velocity range over which the column densities can be
-reasonably well determined (and removing the unphysically high value in
-the bin at $v \approx 222$ km s⁻¹), yields a conservative estimate of
-$\log N_{\rm Si II} \approx 19.4$, corresponding to more than 150
-optical depths in Lyman Continuum, strongly incompatible with an
-optically thin, density-bounded scenario.
+with the low- optical depth, density bounded scenario.
 
-However, the pure riddled ionization bounded scenario is easily ruled
-out since the Ly$\alpha$ profile does not have any appreciable emission
-component at zero velocity. We therefore expect a residual neutral
-fraction to remain in the ionized phase; a fraction which has a column
-density high enough to block Ly$\alpha$ efficiently at line center, but
-low enough to be at least part transparent to Lyman Continuum radiation
-and undetected in \ion{Si}{2}.
+Furthermore; while Ly$\alpha$ radiative transfer is dominated by gas of
+$v \sim v_0$, Lyman continuum is sensitive to \ion{H}{1} at \emph{all}
+velocities. The total column density of \ion{Si}{2} depends on the
+configuration of the neutral clouds. Assuming that the area covered by
+gas in each velocity bin is completely randomly located, a lower limit
+to the total column density is:
+%
+\begin{equation}
+\label{NHImean}
+N_{\rm Si II}^{\rm mean} = \sum_i N_{\text{HI}, i} f_{C, i}
+\end{equation}
+%
+ Summing this over $-450$ km s⁻¹ $< v < 150$ km s⁻¹, the velocity range
+over which the column densities can be reasonably well determined (and
+removing the unphysically high value in the bin at $v \approx 222$ km
+s⁻¹), yields a lower limit of $\log N_{\rm Si II} = 13.52 \pm 0.15$ and
+$\log N_{\rm H I} 19.01 \pm 0.17$, corresponding to $\approx 64$ optical
+depths in Lyman Continuum, strongly incompatible with an optically thin,
+density-bounded scenario.
+
+However, the \emph{pure} riddled ionization bounded scenario is easily
+ruled out since the Ly$\alpha$ profile does not have any appreciable
+emission component at zero velocity. We therefore expect a residual
+neutral fraction to remain in the ionized phase; a fraction which has a
+column density high enough to block Ly$\alpha$ efficiently at line
+center, but low enough to be at least part transparent to Lyman
+Continuum radiation and undetected in \ion{Si}{2}.
 
@@
 \centering
-\includegraphics[width=3.500in]{../Figs/1260-fit-fluor.pdf}
+\includegraphics[width=3.500in]{./1260-fit-fluor.pdf}
 \caption{\ion{Si}{2} $\lambda 1260$ and its fluorescent line at
@@
 \centering
-\includegraphics[width=3.500in]{../Figs/CIIdoubletmodel.pdf}
+\includegraphics[width=3.500in]{./CIIdoubletmodel.pdf}
 \caption{C \ion{C}{2} 1334, \ion{Si}{2} 1260, along with a \ion{C}{2}

### 2016-11-23 prepare_submission.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+# Copy text files
+# cp Paper/Paper.tex ToSubmit/RiveraThorsen.tex
+cp Paper/main.bib ToSubmit/
+cp Paper/table1.tex ToSubmit/
+# Copy figures
+cp Figs/Haroslit.pdf ToSubmit/
+cp Figs/FullSpec.pdf ToSubmit/
+cp Figs/EffResol.pdf ToSubmit/
+cp Figs/HISLISProfiles.pdf ToSubmit/
+cp Figs/AOD-details-example.pdf ToSubmit/
+cp Figs/Fc_haro11c_LIS.pdf ToSubmit/
+cp Figs/Fc_haro11c-SiIV.pdf ToSubmit/
+cp Figs/LyACoverfracs.pdf ToSubmit/
+cp Figs/1260-fit-fluor.pdf ToSubmit/
+cp Figs/CIIdoubletmodel.pdf ToSubmit/
+# Correct figure paths
+sed s,../Figs/,./, Paper/Paper.tex > ToSubmit/RiveraThorsen.tex
+# Build document
+cd ToSubmit
+pdflatex RiveraThorsen.tex
+pdflatex RiveraThorsen.tex
+bibtex RiveraThorsen
+pdflatex RiveraThorsen.tex
+cd ..
+

### 2017-01-16 Paper/Paper.tex
submitted version

@@
 ionized medium of
-$5 \times 10^{13} \leq N_{\rm HI} \leq 4 \times 10^{15}$; high enough to
-be optically thick to Lyman-$\alpha$, but low enough to be at least
-partly transparent to Lyman-continuum and undetected in Si\textsc{ii}.
+$5 \times 10^{13} \leq N_{\rm HI} \leq 4 \times 10^{15}$ cm⁻²; high
+enough to be optically thick to Lyman-$\alpha$, but low enough to be at
+least partly transparent to Lyman-continuum and undetected in
+\ion{Si}{2}.
 \end{abstract}
@@
 leakers have been detected so far
-\citetext{\citealp{Bergvall2006}; \citealp{Leitet2011}; \citealp{Leitet2013}; \citealp{Borthakur2014}; \citealp[Izotov2016Nat;][]{Izotov2016MNRAS}; \citealp{Leitherer2016}},
+\citep{Bergvall2006, Leitet2011, Leitet2013, Borthakur2014, Izotov2016Nat, Izotov2016MNRAS, Leitherer2016},
 at escape fractions ranging typically between 1-8\%, with one as high as
@@
 neutral medium surrounding the central Strömgren sphere not completely
-covering all lines of sight to the background source. This is what is
-called the \emph{picket fence model} by \citet{Heckman2011}, or the
-\emph{riddled ionization bounded medium} by \citet{Verhamme2015}. The
-latter paper presents modeling of the imprints of these two extreme
-scenarios on the observed spectral signature of Lyman-$\alpha$ emission
-lines, and suggest how these can help point to candidate LyC leakers.
-The authors compare their theoretical predictions to sample of
-Lyman-$\alpha$ profiles, including a section of the spectrum treated in
-this work.
-
-The present HST-COS observation is part of the sample in
-\citet{Heckman2015} and \citet{Alexandroff2015}, in which details about
-observation and data reduction are described in depth; we point the
-reader there for further information about these. The Ly$\alpha$ profile
-in this spectrum is discussed in \citet{JaskotOey}.
+covering all lines of sight to the background source \citep[see
+e.g.][]{Zackrisson2013}. This is what is called the \emph{picket fence
+model} by \citet{Heckman2011}, or the \emph{riddled ionization bounded
+medium} by \citet{Verhamme2015}. The latter paper presents modeling of
+the imprints of these two extreme scenarios on the observed spectral
+signature of Lyman-$\alpha$ emission lines, and suggest how these can
+help point to candidate LyC leakers. The authors compare their
+theoretical predictions to sample of Lyman-$\alpha$ profiles, including
+a section of the spectrum treated in this work.
 
@@
 
-Recently, the galaxy has been observed in 21 cm H\textsc{i} emission
-with the 100 m. Robert C. Byrd Green Bank Telescope
-\citep{Pardy2016arXiv}. The authors find that Haro 11 has a low gas mass
-and a very low neutral gas to stellar mass fraction, and that it
-contains around twice as much ionized as neutral Hydrogen.
-Interestingly, the authors also find that the bulk of the neutral gas is
-redshifted wrt. the systemic velocity defined from nebular emission from
-the H\textsc{ii} regions surrounding the main starbursts, signifying
-that the majority of the neutral gas reserves are detached from the star
-formation activity, possibly a tidal arm being flung outwards as a part
-of the ongoing merger event.
+Recently, the galaxy has been observed in 21 cm \ion{H}{1} emission with
+the 100 m. Robert C. Byrd Green Bank Telescope \citep{Pardy2016arXiv}.
+The authors find that Haro 11 has a low gas mass and a very low neutral
+gas to stellar mass fraction, and that it contains around twice as much
+ionized as neutral Hydrogen. Interestingly, the authors also find that
+the bulk of the neutral gas is redshifted wrt. the systemic velocity
+defined from nebular emission from the \ion{H}{2} regions surrounding
+the main starbursts, signifying that the majority of the neutral gas
+reserves are detached from the star formation activity, possibly a tidal
+arm being flung outwards as a part of the ongoing merger event.
 
@@
 as part of HST program GO 13017, PI Timothy Heckman. It was first
-published in \citet{Alexandroff2015} as part of a sample of 22 Lyman
-Break Analog (LBA) galaxies analyzed individually and as a stack. These
-authors mainly focus on three indirect indicators of LyC leakage
-\citep{Overzier2009, Heckman2011}: Residual flux in the trough of
-saturated ISM absorption lines, blueshifted emission in Lyman-$\alpha$,
-and weak optical {[}\ion{S}{2}{]} emission lines.
+published in \citet{Alexandroff2015} and \citet{Heckman2015} as part of
+a sample of 22 Lyman Break Analog (LBA) galaxies analyzed individually
+and as a stack. These authors mainly focus on three indirect indicators
+of LyC leakage \citep{Overzier2009, Heckman2011}: Residual flux in the
+trough of saturated ISM absorption lines, blueshifted emission in
+Lyman-$\alpha$, and weak optical {[}\ion{S}{2}{]} emission lines.
+Details about observation and data reduction are described in depth in
+\citet{Alexandroff2015}; we point the reader there for further
+information about these. The Ly$\alpha$ profile in this spectrum is
+discussed in \citet{Verhamme2015}.
 
@@
 treated here have resolution determined by the properties of their
-surrounding continuum. We the extracted a circular image at the same
+surrounding continuum. We then extracted a circular image at the same
 position and radius as the COS aperture, which was rotated to match the
-orientation of the COS as given in the spectrum headers. We then
-modelled vignetting in the COS aperture by multiplying each pixel in the
-circular UV-continuum image with an interpolation of the values given in
-the throughput grid in Fig. 7 in \citet{CosImaging}. Finally, the
-aperture cutouts were collapsed along the cross-dispersion direction,
-and the FWHM of the flux distribution along the dispersion direction is
-reported as the effective seeing of this observation. This is converted
-from arc seconds to COS resolution elements by the factor 0.171
-arcsec/resel reported in the COS instrument handbook \citep{CosHandbook}
+orientation of the COS as given in the spectrum headers. We modelled
+vignetting in the COS aperture by multiplying each pixel in the circular
+UV-continuum image with an interpolation of the values given in the
+throughput grid in Fig. 7 in \citet{CosImaging}. Finally, the aperture
+cutouts were collapsed along the cross-dispersion direction, and the
+FWHM of the flux distribution along the dispersion direction is reported
+as the effective resolution of this observation. This is converted from
+arc seconds to COS resolution elements by the factor 0.171 arcsec/resel
+reported in the COS instrument handbook \citep{CosHandbook}
 
@@
 The stronger absorption in \ion{Si}{4} reveals a high level of
-ionization of the medium covering the central cluster.
+ionization of the medium covering the background source.
 
@@
 
-In any given velocity bin, the line intensity in terms of the continuum
-intensity is given as
+In any given velocity bin, the residual line intensity in terms of the
+continuum intensity is given as
 %
@@
 the relevant ion \emph{within the given velocity bin}, and $f_{C}$ is
-the covering fraction of neutral gas \emph{moving at the given
-velocity}. When multiple absorption lines are present which arise from
-the same ground state; the population of this state is the same for all
-transitions, and their relative strengths are governed simply by their
-oscillator strengths, and with two or more such transitions, $f_{C}$ and
-$N$ can be inferred from knowledge of $f \lambda$ and measured values of
-$I/I_0$.
+the covering fraction of neutral gas in same velocity bin. When multiple
+absorption lines are present which arise from the same ground state; the
+population of this state is the same for all transitions, and their
+relative strengths are governed simply by their oscillator strengths,
+and with two or more such transitions, $f_{C}$ and $N$ can be inferred
+from knowledge of $f \lambda$ and measured values of $I/I_0$.
 
@@
 integrated velocity of $v = -149$ km s⁻¹ found in this work. We note
-that Na \textsc{i} has a very low ionization potential of only $\sim 5$
+that \ion{Na}{1} has a very low ionization potential of only $\sim 5$
 eV, meaning that these atoms may well only be present in the densest
@@
 indicating that radiative transfer effects are modest, indicative of a
-fairly low column density of HI around line center. We find a Lyman
-$\alpha$ peak velocity of $v_{\rm peak}^{\mathrm{Ly}\alpha} = 158 \pm 1$
-km s⁻¹ w.r.t the systemic velocity found by \citet{Sandberg2013},
-derived from nebular emission lines in the region around knot C. This
-velocity, as it is also discussed in \citet{Verhamme2015}, is just
-consistent with their theoretical predictions for a density-bounded,
-low-column density system, albeit on the upper limit of their allowed
-range.
+fairly low column density of \ion{H}{1} around line center. We find a
+Lyman $\alpha$ peak velocity of
+$v_{\rm peak}^{\mathrm{Ly}\alpha} = 158 \pm 1$ km s⁻¹ w.r.t the systemic
+velocity found by \citet{Sandberg2013}, derived from nebular emission
+lines in the region around knot C. This velocity, as it is also
+discussed in \citet{Verhamme2015}, is just consistent with their
+theoretical predictions for a density-bounded, low-column density
+system, albeit on the upper limit of their allowed range.
 
@@
 the neutral medium of Si / H $= 3.24^{+0.57}_{-0.48} 10^{-6}$, leading
-to a Hydrogen column density of $6.2^{+0.9}_{-1.1} \times 10^{17}$
-cm\textsuperscript{-2}. Since HI gets opaque to ionizing radiation at
+to a Hydrogen column density of $6.2^{+0.9}_{-1.1} \times 10^{17}$ cm⁻²
+for just one velocity bin. Since HI gets opaque to ionizing radiation at
 $\log N \sim 17.2$ \citep{Verhamme2015}, this range is not consistent
-with the low- optical depth, density bounded scenario. Furthermore;
-while Ly$\alpha$ radiative transfer is dominated by gas of $v \sim v_0$,
-Lyman continuum is sensitive to \ion{H}{1} at \emph{all} velocities.
-Integrating the computed column densities over $-450$ km s⁻¹ $< v < 150$
-km s⁻¹, the velocity range over which the column densities can be
-reasonably well determined (and removing the unphysically high value in
-the bin at $v \approx 222$ km s⁻¹), yields a conservative estimate of
-$\log N_{\rm Si II} \approx 19.4$, corresponding to more than 150
-optical depths in Lyman Continuum, strongly incompatible with an
-optically thin, density-bounded scenario.
+with the low- optical depth, density bounded scenario.
 
-However, the pure riddled ionization bounded scenario is easily ruled
-out since the Ly$\alpha$ profile does not have any appreciable emission
-component at zero velocity. We therefore expect a residual neutral
-fraction to remain in the ionized phase; a fraction which has a column
-density high enough to block Ly$\alpha$ efficiently at line center, but
-low enough to be at least part transparent to Lyman Continuum radiation
-and undetected in \ion{Si}{2}.
+Furthermore; while Ly$\alpha$ radiative transfer is dominated by gas of
+$v \sim v_0$, Lyman continuum is sensitive to \ion{H}{1} at \emph{all}
+velocities. The total column density of \ion{Si}{2} depends on the
+configuration of the neutral clouds. Assuming that the area covered by
+gas in each velocity bin is completely randomly located, a lower limit
+to the total column density is:
+%
+\begin{equation}
+\label{NHImean}
+N_{\rm Si II}^{\rm mean} = \sum_i N_{\text{HI}, i} f_{C, i}
+\end{equation}
+%
+ Summing this over $-450$ km s⁻¹ $< v < 150$ km s⁻¹, the velocity range
+over which the column densities can be reasonably well determined (and
+removing the unphysically high value in the bin at $v \approx 222$ km
+s⁻¹), yields a lower limit of $\log N_{\rm Si II} = 13.52 \pm 0.15$ and
+$\log N_{\rm H I} 19.01 \pm 0.17$, corresponding to $\approx 64$ optical
+depths in Lyman Continuum, strongly incompatible with an optically thin,
+density-bounded scenario.
+
+However, the \emph{pure} riddled ionization bounded scenario is easily
+ruled out since the Ly$\alpha$ profile does not have any appreciable
+emission component at zero velocity. We therefore expect a residual
+neutral fraction to remain in the ionized phase; a fraction which has a
+column density high enough to block Ly$\alpha$ efficiently at line
+center, but low enough to be at least part transparent to Lyman
+Continuum radiation and undetected in \ion{Si}{2}.
 
@@
 galaxies of \citep{Henry2015} - these galaxies have sometimes very low
-LIS optical depth, which is usually indicative of low covering fractions
-and high porosity of the neytral medium - and yet they find covering
-fractions of near unity of \ion{H}{1} from Lyman $\beta$ absorption,
-indicating column densities of $N \gtrsim 10^{16}$. Like in the case of
-Haro 11, this indicates that a non-negligible neutral component must be
-present in the ionized phase, although it may very well be of such low
-densities and metallicity that metal absorption from this medium is
-undetectable.
+LIS absorption depths, which is usually indicative of low covering
+fractions and high porosity of the neutral medium - and yet they find
+covering fractions of near unity of \ion{H}{1} from Lyman $\beta$
+absorption, indicating column densities of $N \gtrsim 10^{16}$. Like in
+the case of Haro 11, this indicates that a non-negligible neutral
+component must be present in the ionized phase, although it may very
+well be of such low densities and metallicity that metal absorption from
+this medium is undetectable.
 
@@
 found from nebular recombination lines by \citet{Guseva2012} are
-measured mainly in the central HII regions around the clusters; and
-differ by 0.2 dex between knot B and C. The neutral, outflowing gas
+measured mainly in the central \ion{H}{2} regions around the clusters;
+and differ by 0.2 dex between knot B and C. The neutral, outflowing gas
 could be mixed, or have an unseen LOS distance component larger than the
@@
 C, but note that using the metallicity of $12 + \log (O/H) = 8.3$ found
-for knot B by \citet{Guseva2012}, the inferred H \textsc{i} column
+for knot B by \citet{Guseva2012}, the inferred \ion{H}{1} column
 densities are $3.9 \pm 0.6 \times 10^{17}$ cm\textsuperscript{-2}.
@@
 more strongly enriched than gas further away, which would imply that the
-HI column density is \emph{larger} than inferred from \ion{Si}{2} above.
-To this can be added the further complication stemming from the merger
-event that the galaxy is currently undergoing, which may have mixed gas
-of different metal contents. In any case, though, we would expect the
-regions nearest to the starbursts to generally have higher metallicity
-than the surrounding cool gas, such that the HI column density inferred
-above is more likely to be underestimated than overestimated.
+\ion{H}{1} column density is \emph{larger} than inferred from
+\ion{Si}{2} above. To this can be added the further complication
+stemming from the merger event that the galaxy is currently undergoing,
+which may have mixed gas of different metal contents. In any case,
+though, we would expect the regions nearest to the starbursts to
+generally have higher metallicity than the surrounding cool gas, such
+that the HI column density inferred above is more likely to be
+underestimated than overestimated.
 
@@
 transfer can re-fill absorption features in a way that can make an
-isotropic, optically thin mimic the observational fingerprints of a
-system of optically thick clumps. We therefore need to investigate
+isotropic, optically thin medium mimic the observational fingerprints of
+a system of optically thick clumps. We therefore need to investigate
 whether our conclusions could be generated by such effects.
@@
 upper level, each of the Silicon lines included in the analysis has a
-fluorescent emission line with practically no absorption component. The
-fluorescent line can be used to constrain the possible effect of
+fluorescent emission companion with practically no absorption component.
+The fluorescent line can be used to constrain the possible effect of
 radiative infilling of the absorption trough. If each photon in the
@@
 through the fluorescent channel, and the infilling of the absorption
-line further suppressed.
+line is further suppressed.
 
@@
 theoretical reemission line, subtract it from the observed absorption
-line and find a lower limit for the depth of the pure absorption line
-without reemission; this model line sis shown in gray in the figure. It
-is readily seen that the difference between theoretical and observed
-line is so small that it cannot affect our conclusions about the
-covering factors and column densities of the neutral gas significantly.
+line and find the limiting depth of the pure absorption line without
+reemission; this modeled line is shown in gray in the figure. It is
+readily seen that the difference between worst-case intrinsic and
+observed line is so small that it cannot affect our conclusions about
+the covering factors and column densities of the neutral gas
+significantly.
 
@@
 $\lambda \lambda 1304, 1526$, but note that if significant refilling is
-present here, this would mean the column densities had actually been
+present here, this would mean the column densities had been
 underestimated in our analysis, which would strengthen the conclusions
@@
 $\lambda 1334$ must be optically thick and $\lambda 1335$ part
-transparent. This leave open a degeneracy of relative level populations
+transparent. This leaves open a degeneracy of relative level populations
 and ion abundance, such that the choice of this value only weakly
@@
 density integrated over all velocities is
-$N_{\rm H I}^{\rm tot} \sim 2.5 \times 10^{19}$ cm⁻². There is a
-possibility that the found column densities are in fact lower limits,
-since the found \ion{Si}{2} column densities are close to the limit
-where this ion becomes optically thick. We therefore conclude that the
-leaked ionizing photons, if originating from this cluster, most likely
-escaped via sight lines through the ionized medium, which must thus
+$\log N_{\rm H I}^{\rm tot} = 19.01 \pm 0.17$. There is a possibility
+that the found column densities are in fact lower limits, since the
+found \ion{Si}{2} column densities are close to the limit where this ion
+becomes optically thick. We therefore conclude that the leaked ionizing
+photons, if originating from this cluster, most likely escaped via sight
+lines between the neutral clumps, through an ionized medium which must
 contain a neutral gas column density
-$5 \times 10^{13} \leq N_{\rm HI}^{\rm HIS} \leq 4 \times 10^{15}$. This
-range is bounded downwards by the value at which HI becomes transparent
-to Lyman-$\alpha$, and upwards by the sensitivity to \ion{Si}{2} of this
-observation.
+$5 \times 10^{13} \lesssim N_{\rm HI}^{\rm HIS} \lesssim 4 \times 10^{15}$.
+This range is bounded downwards by the value at which HI becomes
+transparent to Lyman-$\alpha$, and upwards by the detectability of
+\ion{Si}{2} in this observation.
 
@@
 GÖ \& MH acknowledge the support of the Swedish Research Council,
-Vetenskapsrådet, and the Swedish National Space Board (SNSB) and M. H.
-is an Academy Fellow of the Knut and Alice Wallenberg Foundation. This
-project has made extensive use of the Python-based packages Numpy
-\citep{Numpy}, SciPy \citep{SciPy}, Matplotlib \citep{Matplotlib},
-Pandas \citep{Pandas}, LMfit \citep{lmfit2014}, and Astropy
+Vetenskapsrådet, and the Swedish National Space Board (SNSB). MH is an
+Academy Fellow of the Knut and Alice Wallenberg Foundation. This project
+has made extensive use of the Python-based packages Numpy \citep{Numpy},
+SciPy \citep{SciPy}, Matplotlib \citep{Matplotlib}, Pandas
+\citep{Pandas}, LMfit \citep{lmfit2014}, and Astropy
 \citep{Astropy2013}.

### 2017-01-16 ToSubmit/RiveraThorsen.tex
submitted version

@@
 the neutral medium of Si / H $= 3.24^{+0.57}_{-0.48} 10^{-6}$, leading
-to a Hydrogen column density of $6.2^{+0.9}_{-1.1} \times 10^{17}$
-cm\textsuperscript{-2}. Since HI gets opaque to ionizing radiation at
+to a Hydrogen column density of $6.2^{+0.9}_{-1.1} \times 10^{17}$ cm⁻²
+for just one velocity bin. Since HI gets opaque to ionizing radiation at
 $\log N \sim 17.2$ \citep{Verhamme2015}, this range is not consistent

### 2017-01-16 prepare_submission.sh

@@ -5,7 +5,7 @@ cp Paper/main.bib ToSubmit/
 cp Paper/table1.tex ToSubmit/
 # Copy figures
 cp Figs/Haroslit.pdf ToSubmit/
-cp Figs/FullSpec.pdf ToSubmit/
+cp Figs/FullSpec.pdf ToSubmit
 cp Figs/EffResol.pdf ToSubmit/
 cp Figs/HISLISProfiles.pdf ToSubmit/
 cp Figs/AOD-details-example.pdf ToSubmit/

### 2017-01-23 Paper/Paper.tex
First revision submitted
Incorporated comments from Göran and Matthew plus referee report, see
details in the newly added coverletter.* files.

@@
-%%%============================================================================
-%
-%   Pandoc template to convert to latex using emulateapj.
-%   
-%
-%   Usage:
-%   ------
-%
-%   pandoc --template=[/Path/To/File/]pandoc-apj.latex
-%
-%
-%
-%   Caveats (mostly limitations in pandoc):
-%   ---------------------------------------
-%
-%   + Doesn't do figure* and table* environments, these must be tweaked 
-%     manually from standard figure and table environments or inserted as raw
-%     LaTeX rather than Markdown figure invironments.
-%     UPDATE: This can be accomplished by using Scholdoc rather than Pandoc.
-%   + Same goes for equations: pandoc (at the time of writing) only does
-%     displaymath, equations must be declared in raw LaTeX
-%   + Graphics are not scaled, because the autoscale function provided in the
-%     template is using the raw TeX \def function, which is not supported in
-%     ApJ. UPDATE: This has been fixed in Pandoc, and Scholdoc even better.
-%     Use Scholdoc! 
-%
-%   Copyright 2014-2016 T. E. Rivera-Thorsen.
-%
-%%%============================================================================
-\documentclass[twocolumn]{aastex61}
+\documentclass[twocolumn, trackchanges]{aastex61}
 % \usepackage{lmodern}
@@
 
+\submitjournal{\apj}
+\received{November 24, 2016}
+\revised{\today}
+% \watermark{Revision draft}
+% \setwatermarkfontsize{1.4in} 
+%\accepted{\today}
 %%%-----------------------------------------------------------------------
@@
 
-\title{Neutral ISM, Lyman-Alpha and Lyman-continuum in nearby starburst Haro 11
-		                    \footnote{Based on observations with HST-COS, program GO 13017, PI Heckman}
-	            }
+\title{Neutral ISM, Lyman-Alpha and Lyman-continuum in the nearby starburst Haro
+11 \footnote{Based on observations with HST-COS, program GO 13017, obtained from
+the Mikulski Archive for Space Telescopes (MAST). STScI is operated by the
+Association of Universities for Research in Astronomy, Inc., under NASA contract
+NAS5-26555. Support for MAST for non-HST data is provided by the NASA Office of
+Space Science via grant NNX09AF08G and by other grants and contracts.} }
 
@@
 
-\begin{abstract}
-Star forming galaxies are believed to be a major source of ionizing
-radiation responsible for reionizing the early Universe. Direct
-observations of escaping ionizing radiation have however been few and
-with escape fractions far below what would be necessary to account for
-the ionization history of the Universe. In the local Universe, only a
-few handfuls of emitters have been observed with typical escape
-fractions of a few percent. It seems the mechanisms regulating this
-escape need to be strongly evolving with redshift, if galaxies are to be
-held responsible for reionization. Gas mass, star formation feedback and
-thus star formation activity are among the main suspect parameters,
-known to both regulate neutral gas coverage and evolve with cosmic time.
-In this paper, we present a reanalysis of far-UV HST-COS spectra of the
-first detected Lyman-continuum leaker in the local Universe, Haro 11, in
-which we examine the connections between Lyman-continuum leakage and
-Lyman-$\alpha$ line shape and feedback-influenced neutral ISM properties
-like kinematics, geometry and column density. We discuss the two
-extremes of an optically thin, density bounded ISM and a riddled,
-optically thick, ionization bounded ISM and how Haro 11 fits into the
-theoretical predictions made from these models. We find that the most
-likely ISM model for Haro 11 knot C is one of clumpy neutral medium
-embedded in a highly ionized inter-clump medium with a combined covering
-fraction of unity and a residual neutral gas column density in the
-ionized medium of
-$5 \times 10^{13} \leq N_{\rm HI} \leq 4 \times 10^{15}$ cm⁻²; high
-enough to be optically thick to Lyman-$\alpha$, but low enough to be at
-least partly transparent to Lyman-continuum and undetected in
-\ion{Si}{2}.
-\end{abstract}
+\begin{abstract} \textbf{
+
+Star forming galaxies are believed to be a major source of Lyman Continuum (LyC)
+radiation responsible for reionizing the early Universe. Direct observations of
+escaping ionizing radiation have however been few and with low escape fractions.
+In the local Universe, only ~10 emitters have been observed, with typical escape
+fractions of a few percent. The mechanisms regulating this escape need to be
+strongly evolving with redshift in order to account for the Epoch of
+Reionization. Gas content and star formation feedback are among the main
+suspects, known to both regulate neutral gas coverage and evolve with cosmic
+time. In this paper, we reanalyze HST-COS spectrocopy of the first detected
+local LyC leaker, Haro 11. We examine the connection between LyC leakage and
+Lyman-$\alpha$ line shape, and feedback-influenced neutral ISM properties like
+kinematics and gas distribution. We discuss the two extremes of an optically
+thin, density bounded ISM and a riddled, optically thick, ionization bounded
+ISM, and how Haro 11 fits into their theoretical predictions.  We find that the
+most likely ISM model is a clumpy neutral medium embedded in a highly ionized
+medium with a combined covering fraction of unity and a residual neutral gas
+column density in the ionized medium high enough to be optically thick to
+Lyman-$\alpha$, but low enough to be at least partly transparent to Lyman
+continuum and undetected in Si II. This suggests that SF feedback and
+galaxy-scale interaction events play a major role in opening passageways for
+ionizing radiation through the neutral medium.} \end{abstract}
+
+%%% SUBMITTED ORIGINAL VERSION
+% Star forming galaxies are believed to be a major source of ionizing
+% radiation responsible for reionizing the early Universe. Direct
+% observations of escaping ionizing radiation have however been few and
+% with escape fractions far below what would be necessary to account for
+% the ionization history of the Universe. In the local Universe, only a
+% few handfuls of emitters have been observed with typical escape
+% fractions of a few percent. It seems the mechanisms regulating this
+% escape need to be strongly evolving with redshift, if galaxies are to be
+% held responsible for reionization. Gas mass, star formation feedback and
+% thus star formation activity are among the main suspect parameters,
+% known to both regulate neutral gas coverage and evolve with cosmic time.
+% In this paper, we present a reanalysis of far-UV HST-COS spectra of the
+% first detected Lyman continuum leaker in the local Universe, Haro 11, in
+% which we examine the connections between Lyman continuum leakage and
+% Lyman-$\alpha$ line shape and feedback-influenced neutral ISM properties
+% like kinematics, geometry and column density. We discuss the two
+% extremes of an optically thin, density bounded ISM and a riddled,
+% optically thick, ionization bounded ISM and how Haro 11 fits into the
+% theoretical predictions made from these models. We find that the most
+% likely ISM model for Haro 11 knot C is one of clumpy neutral medium
+% embedded in a highly ionized inter-clump medium with a combined covering
+% fraction of unity and a residual neutral gas column density in the
+% ionized medium of
+% $5 \times 10^{13} \leq N_{\rm HI} \leq 4 \times 10^{15}$ cm⁻²; high
+% enough to be optically thick to Lyman-$\alpha$, but low enough to be at
+% least partly transparent to Lyman continuum and undetected in
+% \ion{Si}{2}.
 
@@
 
-Even though star forming galaxies are believed to give rise to the
-majority of radiation reionizing the Universe at early times, it remains
-unknown which physical conditions can facilitate the escape of the
-necessary amounts of radiation from these galaxies, which contain large
-amounts of neutral gas opaque to this radiation at higher column
-densities. Searches for leaking galaxies at redshifts $z \gtrsim 1$ have
-yielded few detections
-\citep[e.g.][]{Iwata2009, Vanzella2010, Vanzella2012, Nestor2013, Cowie2009, Siana2010},
-at escape fractions well below the $\sim 20\%$ needed to account for
+% \replaced{Even though star forming galaxies are believed to give rise to the
+% majority of radiation reionizing the Universe at early times, it remains
+% unknown which physical conditions can facilitate the escape of the
+% necessary amounts of radiation from these galaxies, which contain large
+% amounts of neutral gas opaque to this radiation at higher column
+% densities}{Star forming galaxies are believed to give rise to the
+% majority of radiation reionizing the Universe at early times it remains
+% unknown which physical conditions can facilitate the escape of the
+% necessary amounts of radiation from these galaxies, which contain large
+% amounts of neutral gas opaque to this radiation at higher column
+% densities}.
+\textbf{Young, star-forming galaxies are believed to be the source of a major
+part of the radiation which reionized the early Universe. It is however
+unclear which physical conditions can facilitate the escape of the
+necessary amount of radiation, given that these galaxies contain large
+amounts of neutral gas which is opaque to this ionizing radiation at
+column densities above $\log N \sim 17.2$ \citep{Verhamme2015}.}
+Searches for leaking galaxies at redshifts $z \gtrsim 1$ have yielded few 
+detections
+\citep[e.g.][]{Iwata2009, Vanzella2010, Vanzella2012, Nestor2013, Cowie2009, 
+Siana2010},
+\textbf{with} escape fractions well below the $\sim 20\%$ needed to account for
 cosmic reionization \citep{Bouwens2011, Robertson2013}. A population of
 lower mass and lower luminosity, star forming galaxies are expected to
-contribute to reionization, too, but high star formation is usually
-coincident with higher neutral gas mass, which would cause a higher
-probability of blocking the ionizing photons
-\citep[e.g.][]{Erb2016, Robertson2013}. In the local Universe, only 9
+contribute to reionization, but high star formation is usually
+coincident with higher neutral gas \textbf{(surface)
+density}, which would cause a higher probability of blocking the ionizing 
+photons \citep[e.g.][]{Erb2016, Robertson2013}. In the local Universe, only 9
 leakers have been detected so far
-\citep{Bergvall2006, Leitet2011, Leitet2013, Borthakur2014, Izotov2016Nat, Izotov2016MNRAS, Leitherer2016},
-at escape fractions ranging typically between 1-8\%, with one as high as
+\citep{Bergvall2006, Leitet2011, Leitet2013, Borthakur2014, Izotov2016Nat, 
+Izotov2016MNRAS, Leitherer2016},
+\textbf{with} escape fractions ranging typically between 1-8\%, with one as high as
 $f_{\mathrm{esc}} \approx 13\%$ \citep{Izotov2016MNRAS}.
@@
 Models of ISM surrounding a central source and allowing escape of Lyman
-continuum (LyC), span the range of two extremes: In one regime, the
-surrounding gas is optically thin, highly ionized and density-bounded
-\citep[see e.g.][]{Jaskot2013}, allowing unblocked escape for at least a
-fraction of ionizing photons. In the other regime, the central source is
-surrounded by an optically thick, ionization bounded medium with the
-neutral medium surrounding the central Strömgren sphere not completely
-covering all lines of sight to the background source \citep[see
-e.g.][]{Zackrisson2013}. This is what is called the \emph{picket fence
-model} by \citet{Heckman2011}, or the \emph{riddled ionization bounded
-medium} by \citet{Verhamme2015}. The latter paper presents modeling of
+continuum (LyC), span the range of two extremes: In one regime, the surrounding
+gas is optically thin, highly ionized and density-bounded \citep[see
+e.g.][]{Jaskot2013}, allowing escape for at least a fraction of
+ionizing photons. In the other regime, the central source is surrounded by an
+optically thick, ionization bounded medium with the neutral medium surrounding
+the central Strömgren sphere not completely covering all lines of sight to the
+background source \textbf{in what is called the \emph{picket fence model}
+\citep{Conselice2000, Bergvall2006, Heckman2011, Zackrisson2013} or the
+\emph{riddled ionization bounded medium} by \cite{Verhamme2015}}.
+
+% \citep[see
+% e.g.][]{Zackrisson2013}. This is what is called the \emph{picket fence
+% model} by \citet{Heckman2011}, or the \emph{riddled ionization bounded
+% medium} by \citet{Verhamme2015}.
+
+The latter paper presents modeling of
 the imprints of these two extreme scenarios on the observed spectral
-signature of Lyman-$\alpha$ emission lines, and suggest how these can
-help point to candidate LyC leakers. The authors compare their
+signature of Lyman-$\alpha$ emission lines, and \textbf{suggests}
+how these can help point to candidate LyC leakers. The authors compare their
 theoretical predictions to sample of Lyman-$\alpha$ profiles, including
@@
 
-In (Rivera-Thorsen et al., submitted to \apj), we analyzed optical and
+\textbf{The galaxy treated in this study is Haro 11, a well-studied Blue Compact
+Galaxy at low redshift ($z = 0.021$). Morphologically, it is dominated by three
+major star-forming knots, called knot A, B and C respectively, following the
+terminology of \citet{Vader1993} \citep[see also][
+and fig.~\ref{fig:apert}]{Kunth1998, Hayes2007}. 
+Knots B and C are both very strong in H$\alpha$, revealing that they also are
+producing strong Ly$\alpha$ and LyC. are also
+strong in intrinsic Ly $\alpha$, but while knot C is a strong Ly$\alpha$
+emitter, knot B is a strong absorber, indicating that the neutral ISM 
+properties along the line of sight to the two knots are quite different
+\citep{Hayes2009,Ostlin2009}.  Its complex kinematics indicates that
+it is undergoing a merger or major interaction event 
+\citep{Ostlin2001, Ostlin2015, James2014}. It is the first galaxy in the local
+Universe shown to leak LyC \citep{Bergvall2006}. Since Ly$\alpha$ escape
+is favored by some of the same conditions which also allow LyC escape
+\citep[see e.g. ][]{Hayes2015, DijkstraRev}, the
+leaking photons are assumed to originate from knot C, an assumption adopted in
+this work.}
+
+In Rivera-Thorsen et al., submitted to \apj, we analyzed optical and
 NUV nebular emission lines in slit spectra from ESO VLT/X-Shooter
@@
 both knot B and knot C are associated to a component blueshifted by
-$\sim 50 - 100$ km s\textsuperscript{-1} wrt. the mean nebular velocity.
-This component reaches as far as $\sim 200$ pc. SE of knot B, and
-$\sim 1.5$ kpc S of the midpoint between the two knots. Given the dense
+$\sim 50 - 100$ km s$^{-1}$ \textbf{relative to} the mean 
+nebular velocity.  This component \textbf{extends} as far as $\sim 200$ pc. SE 
+of knot B, 
+and $\sim 1.5$ kpc S of the midpoint between the two knots. Given the dense
 cloud coverage of knot B and the strong star formation activity in both
@@
 ionized as neutral Hydrogen. Interestingly, the authors also find that
-the bulk of the neutral gas is redshifted wrt. the systemic velocity
-defined from nebular emission from the \ion{H}{2} regions surrounding
+the bulk of the neutral gas is redshifted \textbf{relative to} the systemic 
+velocity defined from nebular emission from the \ion{H}{2} regions surrounding
 the main starbursts, signifying that the majority of the neutral gas
@@
 \citet{Alexandroff2015}; we point the reader there for further
-information about these. The Ly$\alpha$ profile in this spectrum is
-discussed in \citet{Verhamme2015}.
+information about these. The Ly$\alpha$ profile in this spectrum is, \textbf{in
+addition to \citet{Heckman2011}, also discussed in \citet{Verhamme2015}.}
 
@@
 
-We measure a number of kinematic parameters for both the neutral (LIS)
-and high-ionized (HIS) phase, and apply the apparent optical depth
-method \citep{Savage1991, Pettini2002, Quider2009, Jones2013}, with the
-implementation being as described in \citet{RiveraThorsen2015} (RT15),
-to infer geometric properties of the neutral medium and constrain the
-column density of neutral hydrogen covering the background source under
-the assumption that the LyC photons detected from this galaxy do indeed
-escape from knot C.
+\textbf{We measure a number of kinematic properties for both the neutral 
+(Low-Ionized State, LIS) and ionized (High-Ionized State, HIS) phase. We apply 
+the apparent optical depth method \citep[AOD, ][]{Savage1991, Pettini2002, Quider2009, Jones2013},
+with the implementation being as described in \citet{RiveraThorsen2015} (RT15)
+to infer geometric properties of the neutral medium. Under the assumtion that
+the LyC photons do indeed escape from knot C, we constrain the 
+column density of neutral hydrogen covering the background source.  
+}
 
@@
 To estimate the effective resolution for this target, we proceeded as
-follows. We used archival imaging data of Haro 11 in the UV-continuum
-from \citet{Ostlin2009}; \citet{Hayes2009}; since the absorption lines
-treated here have resolution determined by the properties of their
-surrounding continuum. We then extracted a circular image at the same
+follows. We used imaging data of Haro 11 in the UV-continuum
+from \citet{Ostlin2009, Hayes2009}, \textbf{since the resolution of absorption
+lines is determined by the resolution of the background continuum source}. We 
+then extracted a circular image at the same
 position and radius as the COS aperture, which was rotated to match the
@@
 \caption{Effective resolution estimate. \textbf{Upper left}: Haro 11 in
-UV-continuum, data from \citet{Ostlin2009}; \citet{Hayes2009}. Data is
+UV-continuum, data from \citet{Ostlin2009, Hayes2009}. Data is
 shown on a square root scale and cut levels set for best detail. Inset
-in blue tinting is the COS aperture covering the region surrounding knot
+in blue is the COS aperture covering the region surrounding knot
 B in the terminology of \citet{Vader1993}. N is up, E is left.
@@
 
-The procedure is illustrated in Fig.~\ref{fig:resol}. Here, the upper
-left panel shows Haro 11 in UV-continuum using HST imaging data from
-\citet{Ostlin2009}; \citet{Hayes2009}, with the COS aperture coverage
-from this observation overlaid in blue tinting. The upper right panel
-shows the galaxy as the COS saw it, with the region covered by the
-aperture cut out, rotated and vignetting-corrected as described above.
-Finally, the lower panel shows the flux profile in the aperture,
-collapsed along the cross dispersion direction. The FWHM of this
-distribution has been adopted as the effective resolution for this
-observation. We find $R_{\text{eff}} = 0.3 \arcsec = 1.75$ resolution
-elements, which at the wavelength of observed Ly$\alpha$ corresponds to
-31 km s⁻¹.
+The procedure is illustrated in Fig.~\ref{fig:resol}. Here, the upper left panel
+shows Haro 11 in UV-continuum using HST imaging data from \citet{Ostlin2009};
+\citet{Hayes2009}, with the COS aperture coverage from this observation overlaid
+in blue. The upper right panel shows the galaxy as the COS saw it, with the
+region covered by the aperture cut out, rotated and vignetting-corrected as
+described above.  Finally, the lower panel shows the flux profile in the
+aperture, collapsed along the cross dispersion direction. The FWHM of this
+distribution has been adopted as the effective resolution for this observation.
+We find $R_{\text{eff}} = 0.3 \arcsec = 1.75$ spectral resolution elements as
+defined in the COS instrument handbook \cite{CosHandbook}, which at the
+wavelength of observed Ly$\alpha$ corresponds to 31 km s⁻¹. \textbf{This value
+might however be slightly underestimated, since the flux profile is not well 
+described by a Gaussian profile, but has stronger wings due to the morphology of 
+the target in the aperture, meaning that a larger fraction of the total flux is 
+outside the FWHM.}
 
@@
 (\textbf{lower}) profiles included in this study. Dashes denote data
-points masked out due to foreground contamination. Note the
+points masked out due to foreground contamination. \textbf{Data in this figure has
+been smoothed to better show the line shapes, but all computations have been
+carried out on the unsmoothed data.} Note the
 high-velocity component in both \ion{Si}{4} lines, extending out to
-$\sim 850$ km s⁻¹.}\label{fig:SingleLines}
+$\sim 850$~km~s$^{-1}$.}\label{fig:SingleLines}
 \end{figure}
@@
 \includegraphics[width=0.800\hsize]{../Figs/AOD-details-example.pdf}
-\caption{Illustration of the AOD computations. \textbf{Upper panel}: the
-three \ion{Si}{2} lines in this analysis shown together, with the
-zero-velocity bin marked with a vertical red line. \textbf{Lower panel}:
-From this bin, the three measured relative intensities are plotted
-against $f\lambda$ as black dots, with vertical error bars showing the
-error spectrum from the COS pipeline. Also shown is the best-fit
-function $I/I0 (f \lambda)$ as defined above. Also shown for
-illustration are the two extreme examples of a very high column density
+\caption{Illustration of the Apparent Optical Depth computations. 
+\textbf{Upper panel}: the three \ion{Si}{2} lines in this analysis shown 
+together, with the zero-velocity bin marked with a vertical red line. 
+\textbf{Lower panel}: From this bin, the three measured relative intensities are 
+plotted against $f\lambda$ as black dots, with vertical error bars showing the
+error spectrum from the COS pipeline. The best-fit
+function $I/I_0 (f \lambda)$ as defined above is drawn in magenta. Also shown 
+for illustration are the two extreme examples of a very high column density
 and unchanged covering fraction, and of a very high covering fraction
@@
 \caption{\textbf{Upper panel}: Ly$\alpha$ profile of Haro 11 C, in
-approximate units of the surrounding continuum level. Full line is the
-measured values smoothed by a 5 px. flat kernel; surrounding shading
+approximate units of the surrounding continuum level. \textbf{The full line
+indicates the measured values smoothed by a 5 px. flat kernel}; surrounding shading
 encloses the $\pm 1 \sigma$ error band (mostly comparable in width to
-the line width). \textbf{Middle panel}: Black steps show the averaged,
+the line width). \textbf{Middle panel}: Black steps show the averaged
 LIS line profile, smoothed by a 5px kernel. Surrounding gray shading
@@
 
-The picture is what we would expect from a Lyman Continuum leaker: weak
-neutral and strong ionized absorption profiles, the latter almost
-everywhere consistent with full coverage, reveal a highly ionized medium
-in front of the central cluster. This is also in good agreement with the
+The picture is what we would expect from a LyC leaker: \textbf{The
+neutral absorption features are weak, and the ionized features are
+strong, revealing a   highly ionized medium
+in front of the central cluster} . This is also in good agreement with the
 findings of \citet{Pardy2016arXiv}, who conclude that the galaxy has
@@
 being photoionized by its hot, massive stars. This also implies that the
-nebular emission outflow found in {[}Rivera-Thorsen et al, submitted{]}
+nebular emission outflow found in Rivera-Thorsen et al, submitted,
 at least partially traces the same gas as the \ion{Si}{4} absorption
@@
 largest amount of gas in a single velocity bin for both phases is found
-at around $v \approx -50$ km s⁻¹, where also a component is found in
-{[}Rivera-Thorsen et al., submitted{]}. The outflow velocity
+at around $v \approx -50$ km s⁻¹\textbf{. Interestingly, a component was also
+found in nebular emission at this velocity in the observations of 
+Rivera-Thorsen et al., submitted}. The outflow velocity
 $v_{\text{int}}$ is at 149 ± 7 km s⁻¹, fully consistent with the
@@
 than the surrounding, more dilute medium. In fig.~\ref{fig:apert}, dusty
-regions in the aperture are apparent E and W of knot C, and in the
+regions in the aperture are apparent E and W of knot C. \textbf{Seen in the
 better resolution of fig. 1 in \citet{Adamo2010}, these regions seem
@@
 the background source. We speculate that the NaD absorption of
-\citet{Sandberg2013} might be associated with this.
+\citet{Sandberg2013} might be associated with this.}
 
@@
 Lyman $\alpha$ peak velocity of
-$v_{\rm peak}^{\mathrm{Ly}\alpha} = 158 \pm 1$ km s⁻¹ w.r.t the systemic
-velocity found by \citet{Sandberg2013}, derived from nebular emission
+$v_{\rm peak}^{\mathrm{Ly}\alpha} = 158 \pm 1$ km s⁻¹ \textbf{relative to} the 
+systemic velocity found by \citet{Sandberg2013}, derived from nebular emission
 lines in the region around knot C. This velocity, as it is also
@@
 from \citet{Garnett1995}, and use this to estimate the column density of
-neutral Hydrogen in front of the light source in the same way is in
-{[}Puschnig et al., submitted to MNRAS{]} as follows. \citet{Guseva2012}
+neutral Hydrogen in front of the light source in \textbf{the same way as in
+Puschnig et al. (submitted to MNRAS) as follows}. \citet{Guseva2012}
 found a metallicity of Haro 11 C of $12 + \log_{10}(\text{O/H}) = 8.1$.
@@
 to a Hydrogen column density of $6.2^{+0.9}_{-1.1} \times 10^{17}$ cm⁻²
-for just one velocity bin. Since HI gets opaque to ionizing radiation at
+for just one velocity bin. Since \ion{H}{1} gets opaque to ionizing radiation at
 $\log N \sim 17.2$ \citep{Verhamme2015}, this range is not consistent
@@
 
-Furthermore; while Ly$\alpha$ radiative transfer is dominated by gas of
-$v \sim v_0$, Lyman continuum is sensitive to \ion{H}{1} at \emph{all}
+Furthermore, while Ly$\alpha$ radiative transfer is dominated by gas of
+$v \sim v_0$, LyC is sensitive to \ion{H}{1} at \emph{all}
 velocities. The total column density of \ion{Si}{2} depends on the
@@
 $\log N_{\rm H I} 19.01 \pm 0.17$, corresponding to $\approx 64$ optical
-depths in Lyman Continuum, strongly incompatible with an optically thin,
+depths in LyC, strongly incompatible with an optically thin,
 density-bounded scenario.
 
-However, the \emph{pure} riddled ionization bounded scenario is easily
+However, the \textbf{strong} riddled ionization bounded scenario 
+\textbf{-- i.e. consisting of only a fully neutral and a fully ionized phase --} 
+is easily
 ruled out since the Ly$\alpha$ profile does not have any appreciable
@@
 column density high enough to block Ly$\alpha$ efficiently at line
-center, but low enough to be at least part transparent to Lyman
-Continuum radiation and undetected in \ion{Si}{2}.
+center, but low enough to be at least part transparent to LyC
+radiation and undetected in \ion{Si}{2}.
 
@@
 in \ion{Si}{2} and is optically thick to Ly$\alpha$ while translucent to
-Lyman Continuum. If we require the gas to be detected in at least two of
+LyC. If we require the gas to be detected in at least two of
 the lines included in this analysis, the limiting hydrogen column
@@
 The existence of a diffuse neutral component being present in the
-ionized medium seems consistent with what is found in the Green Pea
-galaxies of \citep{Henry2015} - these galaxies have sometimes very low
+ionized medium seems consistent with what is found in \textbf{Lyman Break
+Analogs and Green Pea galaxies \citep{Heckman2011, Henry2015}}. 
+These galaxies have sometimes very low
 LIS absorption depths, which is usually indicative of low covering
@@
 covering fractions of near unity of \ion{H}{1} from Lyman $\beta$
-absorption, indicating column densities of $N \gtrsim 10^{16}$. Like in
+absorption, indicating column densities of $N \gtrsim 10^{16}$ cm$^{-2}$. Like in
 the case of Haro 11, this indicates that a non-negligible neutral
@@
 seems to be optically thick, and it seems the column densities arrived
-at can be trusted. But at line center, around $v\sim v_{int}$, the
+at can be trusted. But at line center, around $v\sim v_{\mathrm{int}}$, the
 column densities found are so close to the limit that they are most
@@
 for knot B by \citet{Guseva2012}, the inferred \ion{H}{1} column
-densities are $3.9 \pm 0.6 \times 10^{17}$ cm\textsuperscript{-2}.
+densities are $3.9 \pm 0.6 \times 10^{17}$ cm$^{-2}$.
 However, the question of the exact metallicity of the outflowing gas is
@@
 to make a non-negligible contribution to the resulting line profile. One
-should however bear in mind that these lines rise from different lower
+should however bear in mind that these lines arise from different lower
 fine structure levels; $\lambda 1334$ arises from ²P$_{1/2}$, while the
@@
 \includegraphics[width=3.500in]{../Figs/CIIdoubletmodel.pdf}
-\caption{C \ion{C}{2} 1334, \ion{Si}{2} 1260, along with a \ion{C}{2}
+\caption{\ion{C}{2} 1334, \ion{Si}{2} 1260, along with a \ion{C}{2}
 line synthesized from \ion{Si}{2} (see text for
@@
 investigate the kinematics and geometry of both the hot, ionized and
-cold, neutral ISM along the LOS to the main star forming knot. We have
-used the Apparent Optical Depth method to compute column densities and
-velocity-binned covering fractions of the gas and compared these results
-to the extreme cases of either an optically thin, density bounded
+cold, neutral ISM along the \textbf{line of sight to a strongly star forming
+knot suspected of being the source of the observed LyC leakege from
+the galaxy}. We have used the Apparent Optical Depth method to compute column 
+densities and velocity-binned covering fractions of the gas and compared these 
+results to the extreme cases of either an optically thin, density bounded
 neutral medium, or a riddled, optically thick, ionization bounded
-neutral medium. Assuming that the Lyman Continuum emission previously
+neutral medium. Assuming that the LyC emission previously
 observed from this galaxy indeed does originate from knot C, we find
@@
 densities of gas around $v=0$ in the range
-$N_{\rm HI} = 6.2^{+0.9}_{-1.1} \times 10^{17}$ given the metallicity of
-the background \ion{H}{2} region, which is likely a slight underestimate
-of $N_{\rm HI}$. A conservative estimate of the \ion{H}{1} column
+$N_{\rm HI} = 6.2^{+0.9}_{-1.1} \times 10^{17}$ cm$^{-2}$ given the 
+metallicity of the background \ion{H}{2} region, which is likely a slight 
+underestimate of $N_{\rm HI}$. A conservative estimate of the \ion{H}{1} column
 density integrated over all velocities is
-$\log N_{\rm H I}^{\rm tot} = 19.01 \pm 0.17$. There is a possibility
+$\log N_{\rm H I}^{\rm tot} = 19.01 \pm 0.17$ cm$^{-2}$. There is a possibility
 that the found column densities are in fact lower limits, since the
@@
 contain a neutral gas column density
-$5 \times 10^{13} \lesssim N_{\rm HI}^{\rm HIS} \lesssim 4 \times 10^{15}$.
-This range is bounded downwards by the value at which HI becomes
+$5 \times 10^{13} \lesssim N_{\rm HI}^{\rm HIS} \lesssim 4 \times 10^{15}$
+cm$^{-2}$. This range is bounded downwards by the value at which HI becomes
 transparent to Lyman-$\alpha$, and upwards by the detectability of
@@
 
+\textbf{It is interesting to note that Haro 11 is relatively on neutral 
+gas poor, and has a very strong ongoing starburst episode. If we were to see a 
+case in which neutral gas depletion and/or ionization provided a 
+density-bounded scenario, this would be a likely place to find it. 
+Still, it seems that dynamical effects of feedback and galaxy-scale 
+interaction plays the greater part in peeling away the neutral gas from the 
+central starbursts and opening passages for Ly$\alpha$ and LyC to 
+escape. Given that star formation and merger activity is significantly stronger 
+at $z\gtrsim 1$ than in the local Universe, and that Dark Matter potential wells
+were shallower, these mechanisms could be even more important in that era. 
+one could speculate that this could provide a piece of the puzzle of which
+sources have driven the epoch of reionization.}
+
+% \textbf{While it should be kept in mind that Haro 11 is fairly poor on neutral
+% gas, it is interesting to note that this paints a scenario in which large
+% scale gas motion in e.g. a merger or interaction event, paired with strong star
+% formation feedback, can clear up paths of escape for Ly$\alpha$ and ionizing
+% radiation through an otherwise relatively abundant neutral medium. Rather than
+% requiring a Strömgren radius larger than the scale of the surrounding medium, it
+% might suffice to have the neutral medium stripped off by strong feedback and
+% interaction events. Given that the typical young, high-redshift galaxy is rich
+% in neutral gas, and given the expected high frequency of interactions in this
+% era, it would seem that the }
+
 \section*{Acknowledgements}\label{acknowledgements}
 \addcontentsline{toc}{section}{Acknowledgements}
+
+\textbf{The authors thank the anonymous referee for constructive and insightful 
+comments, which have helped improve the quality of this paper significantly.}
 
@@
 
+% \listofchanges
 \end{document}

### 2017-01-23 ToSubmit/RiveraThorsen.tex
First revision submitted
Incorporated comments from Göran and Matthew plus referee report, see
details in the newly added coverletter.* files.

@@
 
-\begin{abstract}
-Star forming galaxies are believed to be a major source of ionizing
-radiation responsible for reionizing the early Universe. Direct
-observations of escaping ionizing radiation have however been few and
-with escape fractions far below what would be necessary to account for
-the ionization history of the Universe. In the local Universe, only a
-few handfuls of emitters have been observed with typical escape
-fractions of a few percent. It seems the mechanisms regulating this
-escape need to be strongly evolving with redshift, if galaxies are to be
-held responsible for reionization. Gas mass, star formation feedback and
-thus star formation activity are among the main suspect parameters,
-known to both regulate neutral gas coverage and evolve with cosmic time.
-In this paper, we present a reanalysis of far-UV HST-COS spectra of the
-first detected Lyman-continuum leaker in the local Universe, Haro 11, in
-which we examine the connections between Lyman-continuum leakage and
-Lyman-$\alpha$ line shape and feedback-influenced neutral ISM properties
-like kinematics, geometry and column density. We discuss the two
-extremes of an optically thin, density bounded ISM and a riddled,
-optically thick, ionization bounded ISM and how Haro 11 fits into the
-theoretical predictions made from these models. We find that the most
-likely ISM model for Haro 11 knot C is one of clumpy neutral medium
-embedded in a highly ionized inter-clump medium with a combined covering
-fraction of unity and a residual neutral gas column density in the
-ionized medium of
-$5 \times 10^{13} \leq N_{\rm HI} \leq 4 \times 10^{15}$ cm⁻²; high
-enough to be optically thick to Lyman-$\alpha$, but low enough to be at
-least partly transparent to Lyman-continuum and undetected in
-\ion{Si}{2}.
-\end{abstract}
+\begin{abstract} \textbf{ Star forming galaxies are believed to be a major
+		source of Lyman Continuum (LyC) radiation responsible for
+		reionizing the early Universe. Direct observations of escaping
+		ionizing radiation have however been few and with low escape
+		fractions. In the local Universe, only ~10 emitters have been
+		observed, with typical escape fractions of a few percent. The
+		mechanisms regulating this escape need to be strongly evolving
+		with redshift in order to account for the Epoch of Reionization.
+		Gas content and star formation feedback are among the main
+		suspects, known to both regulate neutral gas coverage and evolve
+		with cosmic time. In this paper, we reanalyze HST-COS
+		spectrocopy of the first detected local LyC leaker, Haro 11. We
+		examine the connection between LyC leakage and Lyman-$\alpha$
+		line shape, and feedback-influenced neutral ISM properties like
+		kinematics and gas distribution. We discuss the two extremes of
+		an optically thin, density bounded ISM and a riddled, optically
+		thick, ionization bounded ISM, and how Haro 11 fits into their
+		theoretical predictions.  We find that the most likely ISM model
+		is a clumpy neutral medium embedded in a highly ionized medium
+		with a combined covering fraction of unity and a residual
+		neutral gas column density in the ionized medium high enough to
+		be optically thick to Lyman-$\alpha$, but low enough to be at
+		least partly transparent to Lyman continuum and undetected in Si
+		II. This suggests that SF feedback and galaxy-scale interaction
+		events play a major role in opening passageways for ionizing
+radiation through the neutral medium.} \end{abstract}
+
+%%% SUBMITTED ORIGINAL VERSION
+% Star forming galaxies are believed to be a major source of ionizing
+% radiation responsible for reionizing the early Universe. Direct
+% observations of escaping ionizing radiation have however been few and
+% with escape fractions far below what would be necessary to account for
+% the ionization history of the Universe. In the local Universe, only a
+% few handfuls of emitters have been observed with typical escape
+% fractions of a few percent. It seems the mechanisms regulating this
+% escape need to be strongly evolving with redshift, if galaxies are to be
+% held responsible for reionization. Gas mass, star formation feedback and
+% thus star formation activity are among the main suspect parameters,
+% known to both regulate neutral gas coverage and evolve with cosmic time.
+% In this paper, we present a reanalysis of far-UV HST-COS spectra of the
+% first detected Lyman continuum leaker in the local Universe, Haro 11, in
+% which we examine the connections between Lyman continuum leakage and
+% Lyman-$\alpha$ line shape and feedback-influenced neutral ISM properties
+% like kinematics, geometry and column density. We discuss the two
+% extremes of an optically thin, density bounded ISM and a riddled,
+% optically thick, ionization bounded ISM and how Haro 11 fits into the
+% theoretical predictions made from these models. We find that the most
+% likely ISM model for Haro 11 knot C is one of clumpy neutral medium
+% embedded in a highly ionized inter-clump medium with a combined covering
+% fraction of unity and a residual neutral gas column density in the
+% ionized medium of
+% $5 \times 10^{13} \leq N_{\rm HI} \leq 4 \times 10^{15}$ cm⁻²; high
+% enough to be optically thick to Lyman-$\alpha$, but low enough to be at
+% least partly transparent to Lyman continuum and undetected in
+% \ion{Si}{2}.
 
@@
 \includegraphics[width=0.800\hsize]{./AOD-details-example.pdf}
-\caption{Illustration of the AOD computations. \textbf{Upper panel}: the
-three \ion{Si}{2} lines in this analysis shown together, with the
-zero-velocity bin marked with a vertical red line. \textbf{Lower panel}:
-From this bin, the three measured relative intensities are plotted
-against $f\lambda$ as black dots, with vertical error bars showing the
-error spectrum from the COS pipeline. Also shown is the best-fit
-function $I/I0 (f \lambda)$ as defined above. Also shown for
-illustration are the two extreme examples of a very high column density
+\caption{Illustration of the Apparent Optical Depth computations. 
+\textbf{Upper panel}: the three \ion{Si}{2} lines in this analysis shown 
+together, with the zero-velocity bin marked with a vertical red line. 
+\textbf{Lower panel}: From this bin, the three measured relative intensities are 
+plotted against $f\lambda$ as black dots, with vertical error bars showing the
+error spectrum from the COS pipeline. The best-fit
+function $I/I_0 (f \lambda)$ as defined above is drawn in magenta. Also shown 
+for illustration are the two extreme examples of a very high column density
 and unchanged covering fraction, and of a very high covering fraction
@@
 \includegraphics[width=3.500in]{./CIIdoubletmodel.pdf}
-\caption{C \ion{C}{2} 1334, \ion{Si}{2} 1260, along with a \ion{C}{2}
+\caption{\ion{C}{2} 1334, \ion{Si}{2} 1260, along with a \ion{C}{2}
 line synthesized from \ion{Si}{2} (see text for

### 2017-01-23 Paper/makeaastex6.sh

@@ -1,9 +1,9 @@
-scholdoc Paper.md \
---template=pandoc-aastex6.latex \
---natbib \
--t latex -o Paper.tex
-
-pdflatex Paper.tex
-bibtex Paper
-pdflatex Paper.tex
-
+##  scholdoc Paper.md \
+##  --template=pandoc-aastex6.latex \
+##  --natbib \
+##  -t latex -o Paper.tex
+##  
+##  pdflatex Paper.tex
+##  bibtex Paper
+##  pdflatex Paper.tex
+##  

### 2017-01-23 Paper/makeaastex61.sh

@@ -1,9 +1,9 @@
-scholdoc Paper.md \
---template=pandoc-aastex61.latex \
---natbib \
--t latex -o Paper.tex
-
-pdflatex Paper.tex
-bibtex Paper
-pdflatex Paper.tex
+# scholdoc Paper.md \
+# --template=pandoc-aastex61.latex \
+# --natbib \
+# -t latex -o Paper.tex
+# 
+# pdflatex Paper.tex
+# bibtex Paper
+# pdflatex Paper.tex
 

### 2017-01-26 Paper/Paper.tex
Second revision submitted, hopefully final revision

@@
-\documentclass[twocolumn, trackchanges]{aastex61}
+\documentclass[twocolumn,]{aastex61}
 % \usepackage{lmodern}
@@
            pdfauthor={},
-           pdftitle={Neutral ISM, Lyman-Alpha and Lyman-continuum in nearby starburst Haro 11},
+           pdftitle={Neutral ISM, Lyman-Alpha and Lyman-continuum in the nearby starburst Haro 11},
            colorlinks=true,
@@
 
-\begin{abstract} \textbf{
+\begin{abstract}
 
@@
 galaxy-scale interaction events play a major role in opening passageways for
-ionizing radiation through the neutral medium.} \end{abstract}
+ionizing radiation through the neutral medium.
 
-%%% SUBMITTED ORIGINAL VERSION
-% Star forming galaxies are believed to be a major source of ionizing
-% radiation responsible for reionizing the early Universe. Direct
-% observations of escaping ionizing radiation have however been few and
-% with escape fractions far below what would be necessary to account for
-% the ionization history of the Universe. In the local Universe, only a
-% few handfuls of emitters have been observed with typical escape
-% fractions of a few percent. It seems the mechanisms regulating this
-% escape need to be strongly evolving with redshift, if galaxies are to be
-% held responsible for reionization. Gas mass, star formation feedback and
-% thus star formation activity are among the main suspect parameters,
-% known to both regulate neutral gas coverage and evolve with cosmic time.
-% In this paper, we present a reanalysis of far-UV HST-COS spectra of the
-% first detected Lyman continuum leaker in the local Universe, Haro 11, in
-% which we examine the connections between Lyman continuum leakage and
-% Lyman-$\alpha$ line shape and feedback-influenced neutral ISM properties
-% like kinematics, geometry and column density. We discuss the two
-% extremes of an optically thin, density bounded ISM and a riddled,
-% optically thick, ionization bounded ISM and how Haro 11 fits into the
-% theoretical predictions made from these models. We find that the most
-% likely ISM model for Haro 11 knot C is one of clumpy neutral medium
-% embedded in a highly ionized inter-clump medium with a combined covering
-% fraction of unity and a residual neutral gas column density in the
-% ionized medium of
-% $5 \times 10^{13} \leq N_{\rm HI} \leq 4 \times 10^{15}$ cm⁻²; high
-% enough to be optically thick to Lyman-$\alpha$, but low enough to be at
-% least partly transparent to Lyman continuum and undetected in
-% \ion{Si}{2}.
+\end{abstract}
 
@@
 
-% \replaced{Even though star forming galaxies are believed to give rise to the
-% majority of radiation reionizing the Universe at early times, it remains
-% unknown which physical conditions can facilitate the escape of the
-% necessary amounts of radiation from these galaxies, which contain large
-% amounts of neutral gas opaque to this radiation at higher column
-% densities}{Star forming galaxies are believed to give rise to the
-% majority of radiation reionizing the Universe at early times it remains
-% unknown which physical conditions can facilitate the escape of the
-% necessary amounts of radiation from these galaxies, which contain large
-% amounts of neutral gas opaque to this radiation at higher column
-% densities}.
-\textbf{Young, star-forming galaxies are believed to be the source of a major
-part of the radiation which reionized the early Universe. It is however
-unclear which physical conditions can facilitate the escape of the
-necessary amount of radiation, given that these galaxies contain large
-amounts of neutral gas which is opaque to this ionizing radiation at
-column densities above $\log N \sim 17.2$ \citep{Verhamme2015}.}
-Searches for leaking galaxies at redshifts $z \gtrsim 1$ have yielded few 
-detections
-\citep[e.g.][]{Iwata2009, Vanzella2010, Vanzella2012, Nestor2013, Cowie2009, 
-Siana2010},
-\textbf{with} escape fractions well below the $\sim 20\%$ needed to account for
-cosmic reionization \citep{Bouwens2011, Robertson2013}. A population of
-lower mass and lower luminosity, star forming galaxies are expected to
-contribute to reionization, but high star formation is usually
-coincident with higher neutral gas \textbf{(surface)
-density}, which would cause a higher probability of blocking the ionizing 
-photons \citep[e.g.][]{Erb2016, Robertson2013}. In the local Universe, only 9
-leakers have been detected so far
-\citep{Bergvall2006, Leitet2011, Leitet2013, Borthakur2014, Izotov2016Nat, 
-Izotov2016MNRAS, Leitherer2016},
-\textbf{with} escape fractions ranging typically between 1-8\%, with one as high as
-$f_{\mathrm{esc}} \approx 13\%$ \citep{Izotov2016MNRAS}.
+Young, star-forming galaxies are believed to be the source of a major part of
+the radiation which reionized the early Universe. It is however unclear which
+physical conditions can facilitate the escape of the necessary amount of
+radiation, given that these galaxies contain large amounts of neutral gas which
+is opaque to this ionizing radiation at column densities above $\log N \sim
+17.2$ \citep{Verhamme2015}.  Searches for leaking galaxies at redshifts $z
+\gtrsim 1$ have yielded few detections \citep[e.g.][]{Iwata2009, Vanzella2010,
+Vanzella2012, Nestor2013, Cowie2009, Siana2010}, with escape fractions
+well below the $\sim 20\%$ needed to account for cosmic reionization
+\citep{Bouwens2011, Robertson2013}. A population of lower mass and lower
+luminosity, star forming galaxies are expected to contribute to reionization,
+but high star formation is usually coincident with higher neutral gas
+(surface) density, which would cause a higher probability of blocking
+the ionizing photons \citep[e.g.][]{Erb2016, Robertson2013}. In the local
+Universe, only 9 leakers have been detected so far \citep{Bergvall2006,
+Leitet2011, Leitet2013, Borthakur2014, Izotov2016Nat, Izotov2016MNRAS,
+Leitherer2016}, with escape fractions ranging typically between 1-8\%,
+with one as high as $f_{\mathrm{esc}} \approx 13\%$ \citep{Izotov2016MNRAS}.
 
@@
 the central Strömgren sphere not completely covering all lines of sight to the
-background source \textbf{in what is called the \emph{picket fence model}
+background source in what is called the \emph{picket fence model}
 \citep{Conselice2000, Bergvall2006, Heckman2011, Zackrisson2013} or the
-\emph{riddled ionization bounded medium} by \cite{Verhamme2015}}.
-
-% \citep[see
-% e.g.][]{Zackrisson2013}. This is what is called the \emph{picket fence
-% model} by \citet{Heckman2011}, or the \emph{riddled ionization bounded
-% medium} by \citet{Verhamme2015}.
+\emph{riddled ionization bounded medium} by \cite{Verhamme2015}.
 
@@
 the imprints of these two extreme scenarios on the observed spectral
-signature of Lyman-$\alpha$ emission lines, and \textbf{suggests}
+signature of Lyman-$\alpha$ emission lines, and suggests
 how these can help point to candidate LyC leakers. The authors compare their
@@
 
-\textbf{The galaxy treated in this study is Haro 11, a well-studied Blue Compact
-Galaxy at low redshift ($z = 0.021$). Morphologically, it is dominated by three
-major star-forming knots, called knot A, B and C respectively, following the
-terminology of \citet{Vader1993} \citep[see also][
-and fig.~\ref{fig:apert}]{Kunth1998, Hayes2007}. 
-Knots B and C are both very strong in H$\alpha$, revealing that they also are
-producing strong Ly$\alpha$ and LyC. are also
-strong in intrinsic Ly $\alpha$, but while knot C is a strong Ly$\alpha$
-emitter, knot B is a strong absorber, indicating that the neutral ISM 
+The galaxy treated in this study is Haro 11, a well-studied Blue Compact Galaxy
+at low redshift ($z = 0.021$). Morphologically, it is dominated by three major
+star-forming knots, called knot A, B and C respectively, following the
+terminology of \citet{Vader1993} \citep[see also][ and
+fig.~\ref{fig:apert}]{Kunth1998, Hayes2007}.  Knots B and C are both very strong
+in H$\alpha$, revealing that they also are producing strong Ly$\alpha$ 
+But while knot C is a strong
+Ly$\alpha$ emitter, knot B is a strong absorber, indicating that the neutral ISM
 properties along the line of sight to the two knots are quite different
-\citep{Hayes2009,Ostlin2009}.  Its complex kinematics indicates that
-it is undergoing a merger or major interaction event 
-\citep{Ostlin2001, Ostlin2015, James2014}. It is the first galaxy in the local
-Universe shown to leak LyC \citep{Bergvall2006}. Since Ly$\alpha$ escape
-is favored by some of the same conditions which also allow LyC escape
-\citep[see e.g. ][]{Hayes2015, DijkstraRev}, the
-leaking photons are assumed to originate from knot C, an assumption adopted in
-this work.}
+\citep{Hayes2009,Ostlin2009}.  Its complex kinematics indicates that it is
+undergoing a merger or major interaction event \citep{Ostlin2001, Ostlin2015,
+James2014}. It is the first galaxy in the local Universe \textbf{reported} to leak LyC
+\citep{Bergvall2006}. \textbf{The same dataset has since been re-analyzed by
+\cite{Grimes2007} who concluded that there was no convincing evidence for LyC
+escape; and since by \cite{Leitet2011} who report an escape fraction of $3.3 \pm
+0.7 \%$ based on a newbackground modeling. In this work, we assume that some
+radiation does escape, but it should be kept in mind that this result has been
+disputed.} Since Ly$\alpha$ escape is favored 
+by some of the same conditions which also allow LyC escape 
+\citep[see e.g. ][]{Hayes2015, DijkstraRev, Leitet2011}, the leaking photons 
+are assumed to originate from knot C, an assumption adopted in this work.
 
-In Rivera-Thorsen et al., submitted to \apj, we analyzed optical and
-NUV nebular emission lines in slit spectra from ESO VLT/X-Shooter
-\citep[see also][]{Guseva2012}. We find from kinematics modelling that
-both knot B and knot C are associated to a component blueshifted by
-$\sim 50 - 100$ km s$^{-1}$ \textbf{relative to} the mean 
-nebular velocity.  This component \textbf{extends} as far as $\sim 200$ pc. SE 
-of knot B, 
-and $\sim 1.5$ kpc S of the midpoint between the two knots. Given the dense
-cloud coverage of knot B and the strong star formation activity in both
-knots, we conclude that this component is not only approaching but also
-found in front of the starburst regions and thus along the LOS to knot
+In Rivera-Thorsen et al., submitted to \apj, we analyzed optical and NUV nebular
+emission lines in slit spectra from ESO VLT/X-Shooter \citep[see
+also][]{Guseva2012}. We find from kinematics modelling that both knot B and knot
+C are associated to a component blueshifted by $\sim 50 - 100$ km s$^{-1}$
+relative to the mean nebular velocity.  This component extends as far as $\sim
+200$ pc. SE of knot B, and $\sim 1.5$ kpc S of the midpoint between the two
+knots. Given the dense cloud coverage of knot B and the strong star formation
+activity in both knots, we conclude that this component is not only approaching
+but also found in front of the starburst regions and thus along the LOS to knot
 C.
@@
 ionized as neutral Hydrogen. Interestingly, the authors also find that
-the bulk of the neutral gas is redshifted \textbf{relative to} the systemic 
+the bulk of the neutral gas is redshifted relative to the systemic 
 velocity defined from nebular emission from the \ion{H}{2} regions surrounding
@@
 \citet{Alexandroff2015}; we point the reader there for further
-information about these. The Ly$\alpha$ profile in this spectrum is, \textbf{in
-addition to \citet{Heckman2011}, also discussed in \citet{Verhamme2015}.}
+information about these. The Ly$\alpha$ profile in this spectrum is, in
+addition to \citet{Heckman2011}, also discussed in \citet{Verhamme2015}.
 
@@
 
-\textbf{We measure a number of kinematic properties for both the neutral 
-(Low-Ionized State, LIS) and ionized (High-Ionized State, HIS) phase. We apply 
-the apparent optical depth method \citep[AOD, ][]{Savage1991, Pettini2002, Quider2009, Jones2013},
-with the implementation being as described in \citet{RiveraThorsen2015} (RT15)
-to infer geometric properties of the neutral medium. Under the assumtion that
-the LyC photons do indeed escape from knot C, we constrain the 
-column density of neutral hydrogen covering the background source.  
-}
+We measure a number of kinematic properties for both the neutral (Low-Ionized
+State, LIS) and ionized (High-Ionized State, HIS) phase. We apply the apparent
+optical depth method \citep[AOD, ][]{Savage1991, Pettini2002, Quider2009,
+Jones2013}, with the implementation being as described in
+\citet{RiveraThorsen2015} (RT15) to infer geometric properties of the neutral
+medium. Under the assumtion that the LyC photons do indeed escape from knot C,
+we constrain the column density of neutral hydrogen covering the background
+source.
 
@@
 follows. We used imaging data of Haro 11 in the UV-continuum
-from \citet{Ostlin2009, Hayes2009}, \textbf{since the resolution of absorption
-lines is determined by the resolution of the background continuum source}. We 
+from \citet{Ostlin2009, Hayes2009}, since the resolution of absorption
+lines is determined by the resolution of the background continuum source. We 
 then extracted a circular image at the same
@@
 defined in the COS instrument handbook \cite{CosHandbook}, which at the
-wavelength of observed Ly$\alpha$ corresponds to 31 km s⁻¹. \textbf{This value
-might however be slightly underestimated, since the flux profile is not well 
-described by a Gaussian profile, but has stronger wings due to the morphology of 
-the target in the aperture, meaning that a larger fraction of the total flux is 
-outside the FWHM.}
+wavelength of observed Ly$\alpha$ corresponds to 31 km s⁻¹. This value might
+however be slightly underestimated, since the flux profile is not well described
+by a Gaussian profile, but has stronger wings due to the morphology of the
+target in the aperture, meaning that a larger fraction of the total flux is
+outside the FWHM.
 
@@
 (\textbf{lower}) profiles included in this study. Dashes denote data
-points masked out due to foreground contamination. \textbf{Data in this figure has
+points masked out due to foreground contamination. Data in this figure has
 been smoothed to better show the line shapes, but all computations have been
-carried out on the unsmoothed data.} Note the
+carried out on the unsmoothed data. Note the
 high-velocity component in both \ion{Si}{4} lines, extending out to
@@
 \caption{\textbf{Upper panel}: Ly$\alpha$ profile of Haro 11 C, in
-approximate units of the surrounding continuum level. \textbf{The full line
-indicates the measured values smoothed by a 5 px. flat kernel}; surrounding shading
+approximate units of the surrounding continuum level. The full line
+indicates the measured values smoothed by a 5 px. flat kernel; surrounding shading
 encloses the $\pm 1 \sigma$ error band (mostly comparable in width to
@@
 
-The picture is what we would expect from a LyC leaker: \textbf{The
-neutral absorption features are weak, and the ionized features are
-strong, revealing a   highly ionized medium
-in front of the central cluster} . This is also in good agreement with the
-findings of \citet{Pardy2016arXiv}, who conclude that the galaxy has
+The picture is what we would expect from a LyC leaker: The neutral absorption
+features are weak, and the ionized features are strong, revealing a   highly
+ionized medium in front of the central cluster . This is also in good agreement
+with the findings of \citet{Pardy2016arXiv}, who conclude that the galaxy has
 about twice as much ionized as neutral gas. In addition to this, it is
-interesting to note the close similarity in shape between the
-\ion{Si}{2} and \ion{Si}{4} line profiles, indicating that they likely
-represent two different phases in the same higher density regions. These
-regions will likely be ionized on the side facing the central cluster,
-being photoionized by its hot, massive stars. This also implies that the
-nebular emission outflow found in Rivera-Thorsen et al, submitted,
-at least partially traces the same gas as the \ion{Si}{4} absorption
-here and, by extension, also the neutral medium. Looking at
-fig.~\ref{fig:SingleLines}, we see that maximum absorption and thus the
-largest amount of gas in a single velocity bin for both phases is found
-at around $v \approx -50$ km s⁻¹\textbf{. Interestingly, a component was also
-found in nebular emission at this velocity in the observations of 
-Rivera-Thorsen et al., submitted}. The outflow velocity
-$v_{\text{int}}$ is at 149 ± 7 km s⁻¹, fully consistent with the
-findings of \citet{Heckman2015} and \citet{Alexandroff2015}.
-Interestingly, \citet{Sandberg2013} found from the neutral Sodium
-resonance absorption doublet $\lambda \lambda 5889.95,5895.92$ (NaD) an
-overall, weak \emph{redshift} of $v = 32$ km s⁻¹. From
-e.g.~fig.~\ref{fig:HisLisLya}, it is evident that while neutral gas
-\emph{is} present at these velocities, the velocity is at odds with the
-integrated velocity of $v = -149$ km s⁻¹ found in this work. We note
-that \ion{Na}{1} has a very low ionization potential of only $\sim 5$
-eV, meaning that these atoms may well only be present in the densest
-and/or dustiest regions, in which Sodium is shielded from ionization.
-This is in agreement with the finding of \citet{Sandberg2013} that NaD,
-despite being a strong transition, shows absorption of only $\sim 95\%$
-of continuum level and is mostly found in small, optically thick clouds.
-This suggests that the NaD is tracing only the densest and/or dustiest
-regions which are more slowly accelerated by star formation feedback
-than the surrounding, more dilute medium. In fig.~\ref{fig:apert}, dusty
-regions in the aperture are apparent E and W of knot C. \textbf{Seen in the
-better resolution of fig. 1 in \citet{Adamo2010}, these regions seem
-like they might be connected by a narrow dust lane partially covering
-the background source. We speculate that the NaD absorption of
-\citet{Sandberg2013} might be associated with this.}
+interesting to note the close similarity in shape between the \ion{Si}{2} and
+\ion{Si}{4} line profiles, indicating that they likely represent two different
+phases in the same higher density regions. These regions will likely be ionized
+on the side facing the central cluster, being photoionized by its hot, massive
+stars. This also implies that the nebular emission outflow found in
+Rivera-Thorsen et al, submitted, at least partially traces the same gas as the
+\ion{Si}{4} absorption here and, by extension, also the neutral medium. Looking
+at fig.~\ref{fig:SingleLines}, we see that maximum absorption and thus the
+largest amount of gas in a single velocity bin for both phases is found at
+around $v \approx -50$ km s⁻¹. Interestingly, a component was also found in
+nebular emission at this velocity in the observations of Rivera-Thorsen et al.,
+submitted. The outflow velocity $v_{\text{int}}$ is at 149 ± 7 km s⁻¹, fully
+consistent with the findings of \citet{Heckman2015} and \citet{Alexandroff2015}.
+Interestingly, \citet{Sandberg2013} found from the neutral Sodium resonance
+absorption doublet $\lambda \lambda 5889.95,5895.92$ (NaD) an overall, weak
+\emph{redshift} of $v = 32$ km s⁻¹. From e.g.~fig.~\ref{fig:HisLisLya}, it is
+evident that while neutral gas \emph{is} present at these velocities, the
+velocity is at odds with the integrated velocity of $v = -149$ km s⁻¹ found in
+this work. We note that \ion{Na}{1} has a very low ionization potential of only
+$\sim 5$ eV, meaning that these atoms may well only be present in the densest
+and/or dustiest regions, in which Sodium is shielded from ionization.  This is
+in agreement with the finding of \citet{Sandberg2013} that NaD, despite being a
+strong transition, shows absorption of only $\sim 95\%$ of continuum level and
+is mostly found in small, optically thick clouds.  This suggests that the NaD is
+tracing only the densest and/or dustiest regions which are more slowly
+accelerated by star formation feedback than the surrounding, more dilute medium.
+In fig.~\ref{fig:apert}, dusty regions in the aperture are apparent E and W of
+knot C. Seen in the better resolution of fig. 1 in \citet{Adamo2010}, these
+regions seem like they might be connected by a narrow dust lane partially
+covering the background source. We speculate that the NaD absorption of
+\citet{Sandberg2013} might be associated with this.
 
@@
 Lyman $\alpha$ peak velocity of
-$v_{\rm peak}^{\mathrm{Ly}\alpha} = 158 \pm 1$ km s⁻¹ \textbf{relative to} the 
+$v_{\rm peak}^{\mathrm{Ly}\alpha} = 158 \pm 1$ km s⁻¹ relative to the 
 systemic velocity found by \citet{Sandberg2013}, derived from nebular emission
@@
 from \citet{Garnett1995}, and use this to estimate the column density of
-neutral Hydrogen in front of the light source in \textbf{the same way as in
-Puschnig et al. (submitted to MNRAS) as follows}. \citet{Guseva2012}
+neutral Hydrogen in front of the light source in the same way as in
+Puschnig et al. (submitted to MNRAS) as follows. \citet{Guseva2012}
 found a metallicity of Haro 11 C of $12 + \log_{10}(\text{O/H}) = 8.1$.
@@
 
-However, the \textbf{strong} riddled ionization bounded scenario 
-\textbf{-- i.e. consisting of only a fully neutral and a fully ionized phase --} 
-is easily
-ruled out since the Ly$\alpha$ profile does not have any appreciable
-emission component at zero velocity. We therefore expect a residual
-neutral fraction to remain in the ionized phase; a fraction which has a
-column density high enough to block Ly$\alpha$ efficiently at line
-center, but low enough to be at least part transparent to LyC
-radiation and undetected in \ion{Si}{2}.
+However, the strong riddled ionization bounded scenario -- i.e.
+consisting of only a fully neutral and a fully ionized phase -- is easily ruled
+out since the Ly$\alpha$ profile does not have any appreciable emission
+component at zero velocity. We therefore expect a residual neutral fraction to
+remain in the ionized phase; a fraction which has a column density high enough
+to block Ly$\alpha$ efficiently at line center, but low enough to be at least
+part transparent to LyC radiation and undetected in \ion{Si}{2}.
 
@@
 
-The existence of a diffuse neutral component being present in the
-ionized medium seems consistent with what is found in \textbf{Lyman Break
-Analogs and Green Pea galaxies \citep{Heckman2011, Henry2015}}. 
-These galaxies have sometimes very low
-LIS absorption depths, which is usually indicative of low covering
-fractions and high porosity of the neutral medium - and yet they find
-covering fractions of near unity of \ion{H}{1} from Lyman $\beta$
-absorption, indicating column densities of $N \gtrsim 10^{16}$ cm$^{-2}$. Like in
-the case of Haro 11, this indicates that a non-negligible neutral
-component must be present in the ionized phase, although it may very
-well be of such low densities and metallicity that metal absorption from
-this medium is undetectable.
+The existence of a diffuse neutral component being present in the ionized medium
+seems consistent with what is found in Lyman Break Analogs and Green Pea
+galaxies \citep{Heckman2011, Henry2015}.  These galaxies have sometimes very low
+LIS absorption depths, which is usually indicative of low covering fractions and
+high porosity of the neutral medium - and yet they find covering fractions of
+near unity of \ion{H}{1} from Lyman $\beta$ absorption, indicating column
+densities of $N \gtrsim 10^{16}$ cm$^{-2}$. Like in the case of Haro 11, this
+indicates that a non-negligible neutral component must be present in the ionized
+phase, although it may very well be of such low densities and metallicity that
+metal absorption from this medium is undetectable.
 
@@
 
-In this work, we have re-analyzed an archival FUV HST-COS spectrum to
-investigate the kinematics and geometry of both the hot, ionized and
-cold, neutral ISM along the \textbf{line of sight to a strongly star forming
-knot suspected of being the source of the observed LyC leakege from
-the galaxy}. We have used the Apparent Optical Depth method to compute column 
-densities and velocity-binned covering fractions of the gas and compared these 
-results to the extreme cases of either an optically thin, density bounded
-neutral medium, or a riddled, optically thick, ionization bounded
-neutral medium. Assuming that the LyC emission previously
-observed from this galaxy indeed does originate from knot C, we find
-that the observations are not compatible with the latter case, since the
-characteristic, bright Lyman-$\alpha$ emission spike at line center is
-absent in this spectrum. Furthermore, the observations are not
-consistent with an optically thin, density bounded neutral medium.
+In this work, we have re-analyzed an archival FUV HST-COS spectrum 
+\textbf{of Haro 11} to
+investigate the kinematics and geometry of both the hot, ionized and cold,
+neutral ISM along the line of sight to a strongly star forming knot suspected of
+being the source of the observed LyC leakege from the galaxy. We have used the
+Apparent Optical Depth method to compute column densities and velocity-binned
+covering fractions of the gas and compared these results to the extreme cases of
+either an optically thin, density bounded neutral medium, or a riddled,
+optically thick, ionization bounded neutral medium. Assuming that the LyC
+emission previously observed from this galaxy indeed does originate from knot C,
+we find that the observations are not compatible with the latter case, since the
+characteristic, bright Lyman-$\alpha$ emission spike at line center is absent in
+this spectrum. Furthermore, the observations are not consistent with an
+optically thin, density bounded neutral medium.
 
@@
 
-\textbf{It is interesting to note that Haro 11 is relatively on neutral 
+It is interesting to note that Haro 11 is relatively on neutral 
 gas poor, and has a very strong ongoing starburst episode. If we were to see a 
@@
 one could speculate that this could provide a piece of the puzzle of which
-sources have driven the epoch of reionization.}
+sources have driven the epoch of reionization.
 
@@
 
-\textbf{The authors thank the anonymous referee for constructive and insightful 
-comments, which have helped improve the quality of this paper significantly.}
+The authors thank the anonymous referee for constructive and insightful 
+comments, which have helped improve the quality of this paper significantly.
 

### 2017-01-26 ToSubmit/RiveraThorsen.tex
Second revision submitted, hopefully final revision

@@
 
-\begin{abstract} \textbf{ Star forming galaxies are believed to be a major
-		source of Lyman Continuum (LyC) radiation responsible for
-		reionizing the early Universe. Direct observations of escaping
-		ionizing radiation have however been few and with low escape
-		fractions. In the local Universe, only ~10 emitters have been
-		observed, with typical escape fractions of a few percent. The
-		mechanisms regulating this escape need to be strongly evolving
-		with redshift in order to account for the Epoch of Reionization.
-		Gas content and star formation feedback are among the main
-		suspects, known to both regulate neutral gas coverage and evolve
-		with cosmic time. In this paper, we reanalyze HST-COS
-		spectrocopy of the first detected local LyC leaker, Haro 11. We
-		examine the connection between LyC leakage and Lyman-$\alpha$
-		line shape, and feedback-influenced neutral ISM properties like
-		kinematics and gas distribution. We discuss the two extremes of
-		an optically thin, density bounded ISM and a riddled, optically
-		thick, ionization bounded ISM, and how Haro 11 fits into their
-		theoretical predictions.  We find that the most likely ISM model
-		is a clumpy neutral medium embedded in a highly ionized medium
-		with a combined covering fraction of unity and a residual
-		neutral gas column density in the ionized medium high enough to
-		be optically thick to Lyman-$\alpha$, but low enough to be at
-		least partly transparent to Lyman continuum and undetected in Si
-		II. This suggests that SF feedback and galaxy-scale interaction
-		events play a major role in opening passageways for ionizing
-radiation through the neutral medium.} \end{abstract}
+\begin{abstract}
 
-%%% SUBMITTED ORIGINAL VERSION
-% Star forming galaxies are believed to be a major source of ionizing
-% radiation responsible for reionizing the early Universe. Direct
-% observations of escaping ionizing radiation have however been few and
-% with escape fractions far below what would be necessary to account for
-% the ionization history of the Universe. In the local Universe, only a
-% few handfuls of emitters have been observed with typical escape
-% fractions of a few percent. It seems the mechanisms regulating this
-% escape need to be strongly evolving with redshift, if galaxies are to be
-% held responsible for reionization. Gas mass, star formation feedback and
-% thus star formation activity are among the main suspect parameters,
-% known to both regulate neutral gas coverage and evolve with cosmic time.
-% In this paper, we present a reanalysis of far-UV HST-COS spectra of the
-% first detected Lyman continuum leaker in the local Universe, Haro 11, in
-% which we examine the connections between Lyman continuum leakage and
-% Lyman-$\alpha$ line shape and feedback-influenced neutral ISM properties
-% like kinematics, geometry and column density. We discuss the two
-% extremes of an optically thin, density bounded ISM and a riddled,
-% optically thick, ionization bounded ISM and how Haro 11 fits into the
-% theoretical predictions made from these models. We find that the most
-% likely ISM model for Haro 11 knot C is one of clumpy neutral medium
-% embedded in a highly ionized inter-clump medium with a combined covering
-% fraction of unity and a residual neutral gas column density in the
-% ionized medium of
-% $5 \times 10^{13} \leq N_{\rm HI} \leq 4 \times 10^{15}$ cm⁻²; high
-% enough to be optically thick to Lyman-$\alpha$, but low enough to be at
-% least partly transparent to Lyman continuum and undetected in
-% \ion{Si}{2}.
+Star forming galaxies are believed to be a major source of Lyman Continuum (LyC)
+radiation responsible for reionizing the early Universe. Direct observations of
+escaping ionizing radiation have however been few and with low escape fractions.
+In the local Universe, only ~10 emitters have been observed, with typical escape
+fractions of a few percent. The mechanisms regulating this escape need to be
+strongly evolving with redshift in order to account for the Epoch of
+Reionization. Gas content and star formation feedback are among the main
+suspects, known to both regulate neutral gas coverage and evolve with cosmic
+time. In this paper, we reanalyze HST-COS spectrocopy of the first detected
+local LyC leaker, Haro 11. We examine the connection between LyC leakage and
+Lyman-$\alpha$ line shape, and feedback-influenced neutral ISM properties like
+kinematics and gas distribution. We discuss the two extremes of an optically
+thin, density bounded ISM and a riddled, optically thick, ionization bounded
+ISM, and how Haro 11 fits into their theoretical predictions.  We find that the
+most likely ISM model is a clumpy neutral medium embedded in a highly ionized
+medium with a combined covering fraction of unity and a residual neutral gas
+column density in the ionized medium high enough to be optically thick to
+Lyman-$\alpha$, but low enough to be at least partly transparent to Lyman
+continuum and undetected in Si II. This suggests that SF feedback and
+galaxy-scale interaction events play a major role in opening passageways for
+ionizing radiation through the neutral medium.
+
+\end{abstract}
 

### 2017-01-27 Paper/Paper.tex
Accepted version

@@
 undergoing a merger or major interaction event \citep{Ostlin2001, Ostlin2015,
-James2014}. It is the first galaxy in the local Universe \textbf{reported} to leak LyC
-\citep{Bergvall2006}. \textbf{The same dataset has since been re-analyzed by
+James2014}. It is the first galaxy in the local Universe reported to leak LyC
+\citep{Bergvall2006}. The same dataset has since been re-analyzed by
 \cite{Grimes2007} who concluded that there was no convincing evidence for LyC
 escape; and since by \cite{Leitet2011} who report an escape fraction of $3.3 \pm
-0.7 \%$ based on a newbackground modeling. In this work, we assume that some
+0.7 \%$ based on a new background modeling. In this work, we assume that some
 radiation does escape, but it should be kept in mind that this result has been
-disputed.} Since Ly$\alpha$ escape is favored 
+disputed. Since Ly$\alpha$ escape is favored 
 by some of the same conditions which also allow LyC escape 
